### 2022-03-16 doc/analysis_writeup.Rmd
Added some utility functions, working on plotting functions for labelled histograms

---
title: "Analysis writeup"
author: "Jay Gillenwater"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmdformats::readthedown
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
## target knits Rmds in their own session, so load libraries here.
source(here::here("packages.R"))
```

```{r load-targets, include=FALSE}
# tar_load(c(target_1, target_2, target_3))

# # If your chunk output is shown in-line, then you'll need to wrap tar_load()
# # like so:
# 
# withr::with_dir(here::here(), {
#   tar_load(c(target_1, target_2, target_3))
# })
# 
# # This is not needed when using tar_make() to render the document.
```

## Introduction
This document is a (relatively) brief overview of the analysis performed by this workflow and my reasoning + thoughts for the techniques I used.

## Overall goals
The main objective of this experiment is to identify soybean lines with yield and agronomic traits comparable to existing high-yielding checks that also have seed protein and oil contents that are superior to the high-yielding checks.

## Population description
### Population development history 
In 2018, oil mapping populations 201 and 202 were grown at the Central Crops Research Station in Clayton, NC. These populations consisted of 273 and 237 recombinant inbred lines (RILs) respectively. Several agronomic traits were scored in the field for each population. These included height, lodging, maturity date, and a composite agronomic score. Lodging was scored on a scale of 1-5 where 5indicates that all plants in a plot are on the ground, and a score of 1 indicates that all plants are erect[Feh87]. The agronomic score aimed to capture other traits of value such as visual estimation of pod load and plot uniformity to provide a general score of a line’s agronomic desirability. Agronomic score was recorded on a scale of 1-5 aswell, with 1 identifying the best lines of a population, and 5 the worst. Maturity was recorded at the R8 maturity date. Height was measured in centimeters from the soil to the top of the plant. Following harvest, yield, seed weight, protein, and oil content were measured after seed was air dried to approximately 7% moisture content in a greenhouse. Protein and oil contents were measured on a dry basis using a Perten DA 7250 NIR®instrument. Yield and seed weight were measured after seed had been sifted and cleaned of debris and cracked seed. To select lines for the 2019 growing season, lines with abnormally low bulk weights or extreme maturity dates from 2018 were first removed from consideration. Two yield trials were then developed for each mapping population. The maturity data of RILs were considered when forming tests such that the lines of each test would have a maturity data range approximately half that of the total mapping population from which it was derived. RILs were selected for each test which were also representative of the distribution of seed protein and seed oil traits for each population. Eighty unique lines were selected from each population which satisfied these criteria, and each yield test was comprised of 40 RILs. Three high-yielding check cultivars and the two parents of the respective population were also included in each test. Yield check cultivars Dunphy, Osage, and Roy were used in tests 1 and 2, while Dunphy, Dilday, and N.C. Raleigh were used for tests 3 and 4. These lines were selected to represent the estimated maturities of the RILs in each test. The parents for tests 1 and 2 were cultivars LMN09-119 and N09-09, and the parents for tests 3 and 4 were LMN09-19 and N13-47.

These four tests were grown in two locations in 2019: the Tidewater Research Station in Plymouth, NC (PLY) and the Caswell Research Farm in Kinston, NC (CAS). The same data was collected for each test in this season that was collected in the previous season. Selections were done using this data by first identifying the lines with a yield within or above a least significant difference (LSD) of the average yield of the checks for each test. Further selection was done using the seed composition traits by identifying the thirty lines with the highest protein + oil content.

These thirty lines were then grouped into two new tests of 15 RILs each which were then grown in both the 2020 and 2021 seasons. Thesew tests were grown in CLA and CAS in 2020 and CAS and PLY in 2021.

## Reproducibility

<details><summary>Reproducibility receipt</summary>

```{r}
## datetime
Sys.time()

## repository
if(requireNamespace('git2r', quietly = TRUE)) {
  git2r::repository()
} else {
  c(
    system2("git", args = c("log", "--name-status", "-1"), stdout = TRUE),
    system2("git", args = c("remote", "-v"), stdout = TRUE)
  )
}

## session info
sessionInfo()
```

</details>

### 2022-03-16 R/make_blup_table.R

@@ -1,11 +1,0 @@
-#' .. content for \description{} (no empty lines) ..
-#'
-#' .. content for \details{} ..
-#'
-#' @title
-#' @param fit_models
-make_blup_table <- function(fit_models = mixed_models_two_year) {
-
-  NULL
-
-}

### 2022-03-16 R/merge_yield_data.R

@@ -11,7 +11,8 @@
 #' @param yield_2021_file
 merge_yield_data <- function(yield_2019_file, cas_maturity_file,
                              cla_maturity_file, nir_2020_file, yield_2020_file,
-                             yield_2021_file) {
+                             yield_2021_file, 
+                             util_tables) {
   
   # Read in the 2019 yield data and rename some of the columns
   yield_2019 <- read_excel(yield_2019_file, col_types = "text") %>%
@@ -23,7 +24,7 @@ merge_yield_data <- function(yield_2019_file, cas_maturity_file,
            ht               = height, 
            lod              = lodging, 
            protein_plus_oil = oil_protein) %>% 
-    mutate(loc = toupper(loc))
+    mutate(loc = toupper(loc)) # Convert from kg/ha to bu/acre
 
   # Read in the 2020 maturity date data
   md_cas <- read_excel(cas_maturity_file, col_types = "text")
@@ -105,9 +106,14 @@ merge_yield_data <- function(yield_2019_file, cas_maturity_file,
     reduce(bind_rows) %>% 
     mutate(across(any_of(num_cols), as.numeric), 
            protein_plus_oil = protein + oil, 
-           yield = ifelse(year %in% c("2019", "2020"), yield*0.033, 
-                          ifelse(loc %in% c("PLY", "SAN"), yield*0.0252, yield*0.0228)), 
+           yield = ifelse(year %in% c("2020"), yield*0.033, 
+                          ifelse(year == "2019", yield/67.2510693716674, 
+                            ifelse(loc %in% c("PLY", "SAN"), yield*0.0252, yield*0.0228))), 
            ENV = paste(loc, year, sep = " - "))
+  
+  # Standardize genotype names so that each genotype is identified with
+  # only name. See the function definition in the utils.R script.
+  all_merged <- convert_from_table(all_merged, "genotype", util_tables$genotype_conversion_table)
   
   # Split this data into two tables: One with all the data
   # and one with just the data from 2020 and 2021, split up by test

### 2022-03-16 R/read_util_tables.R

@@ -1,0 +1,18 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param yield_check_genotypes
+#' @param genotype_conversion
+read_util_tables <- function(yield_check_genotypes, genotype_conversion) {
+
+  # Read in each file and return the dataframes in a list
+  yield_checks        <- read_excel(yield_check_genotypes)
+  genotype_conversion <- read_excel(genotype_conversion)
+  
+  res <- list("check_table"               = yield_checks, 
+              "genotype_conversion_table" = genotype_conversion)
+  
+  return(res)
+}

### 2022-03-16 R/set_test_colors.R

@@ -1,0 +1,14 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param color_ids
+set_test_colors <- function(color_ids = names(all_yield_data$all)) {
+
+  # Use the gg_color_hue function (see utils.R) to assign a 
+  # hexcode color to each test name
+  gg_color_hue(length(color_ids)) %>% 
+    set_names(color_ids)
+
+}

### 2022-03-16 R/utils.R

@@ -1,0 +1,25 @@
+##################################################
+## Project: Jay Yield
+## Script purpose: Utility functions for the yield analysis
+## Date: 2022-03-16
+## Author: Jay Gillenwater
+##################################################
+
+# A function to return the ggplot color palette for a given number of categories
+gg_color_hue <- function(n) {
+  hues = seq(15, 375, length = n + 1)
+  hcl(h = hues, l = 65, c = 100)[1:n]
+}
+
+# A function that takes a conversion table with an "old name" inn the first column
+# and the name that it should be recoded to in the second column, and takes
+# this table to recode a given variable in some dataframe
+convert_from_table <- function(data, var, conversiontable){
+  
+  all_matches   <- match(data[, var], conversiontable[, 1])
+  match_indices <- which(!is.na(all_matches))
+  
+  data[, var][match_indices] <- conversiontable[, 2][all_matches[match_indices]]
+  
+  return(data)
+}

### 2022-03-16 _targets.R

@@ -39,8 +39,23 @@ tar_plan(
              list.files(here("data", "season_2021"), full.names = TRUE), 
              format = "file"), 
   
+  # Check genotypes
+  tar_target(yield_check_genotypes, 
+             here("data", "utils", "check_genotypes.xlsx"), 
+             format = "file"),
+  
+  # A table to convert between genotype names that are coded 
+  # differently between years
+  tar_target(genotype_conversion, 
+             here("data", "utils", "genotype_name_conversion.xlsx"), 
+             format = "file"), 
+  
   ## Section: Data cleaning
   ##################################################
+  
+  # Read in the utility tables
+  tar_target(util_tables, 
+             read_util_tables(yield_check_genotypes, genotype_conversion)),
   
   # Cleaning up and merging the data from the three seasons
   tar_target(all_yield_data, 
@@ -49,7 +64,12 @@ tar_plan(
                               cla_maturity_file, 
                               nir_2020_file,
                               yield_2020_file, 
-                              yield_2021_file)),
+                              yield_2021_file, 
+                              util_tables)),
+  
+  # Assign a color to each test name to use for plotting
+  tar_target(test_name_colors, 
+             set_test_colors(color_ids = names(all_yield_data$all))),
   
   ## Section: Analysis
   ##################################################
@@ -76,7 +96,10 @@ tar_plan(
   
   # Plots of the genotype blues
   tar_target(BLUE_plots_two_years, 
-             make_genotype_blue_plots(fit_models = mixed_models_two_years))
-
+             make_genotype_blue_plots(fit_models = mixed_models_two_years)),
+  
+  ## Section: Writeup documents
+  ##################################################
+  tar_render(analysis_writeup, "doc/analysis_writeup.Rmd")
   
 )

### 2022-03-16 packages.R

@@ -12,7 +12,21 @@ pacman::p_load(conflicted,
                here, 
                readxl, 
                janitor, 
-               metan)
+               metan, 
+               rmdformats, 
+               openxlsx, 
+               ggthemes, 
+               lattice, 
+               ggpubr, 
+               ggcorrplot, 
+               extrafont, 
+               GGally, 
+               agricolae, 
+               lme4, 
+               emmeans, 
+               kableExtra, 
+               pander)
 
 # Function preference
 conflicted::conflict_prefer("filter", "dplyr", "base")
+

### 2022-03-16 sandbox/labelled histogram.R

@@ -1,0 +1,56 @@
+
+
+TraitHist.facet <- function(TraitData, Name = names(YieldData_melt_TestTrait)[[1]], FillCol = TestColours[[1]]){
+  
+  # Get the test and trait name from the name of the list element
+  TraitName <- sub("Yield Test \\d{1}\\.", "", Name)
+  TestName  <- str_extract(Name, "Yield Test \\d{1}")
+  
+  # Get the average of checks for a test, and the LSD
+  CheckAvg <- CheckParentAvgerage_byTest %>% filter(Test == TestName, Genotype %in% Checks)
+  CheckAvg <- mean(CheckAvg$LSMean_Yield)
+  
+  # Get the LSD for yield for the current test
+  CurrentLSD <- AllYieldTests.LSD$Yield[which(AllYieldTests.LSD$Test == TestName)]
+  LSDLine    <- CheckAvg - CurrentLSD
+  
+  # The initial plot (need bin heights)
+  Plot.init <- ggplot(TraitData, aes(x = value)) + 
+    geom_histogram(bins = 9, fill = FillCol, col = 'black') + 
+    theme_bw() + 
+    theme(axis.text = element_text(size = 20, face = 'bold'),
+          axis.title = element_text(size = 30)) + 
+    ylab("Count") + 
+    xlab(TraitName) + 
+    geom_vline(xintercept = CheckAvg, linetype = 'dotted', colour = 'black', size = 1.25) + 
+    geom_vline(xintercept = LSDLine, linetype = 2, colour = 'red', size = 1.25)
+  
+  # Get data for the parents/checks
+  CheckParents <- TraitData %>% filter(Genotype %in% c(Checks, Parents))
+  
+  # Data from the initial plot (I want the bin heights)
+  PlotData <- ggplot_build(Plot.init)$data[[1]]
+  
+  # Using the bin counts from the plot, find the y-value where the labels for each
+  # check/parent genotype shoud start
+  CheckParents$yval <- NA
+  for(i in 1:nrow(CheckParents)){
+    CheckParents$yval[[i]] <- PlotData$count[[max(which(PlotData$xmin < CheckParents$value[[i]]))]]
+  }
+  
+  
+  # Add labels w/arrows for the parents/checks using this new data
+  # c(max(PlotData$count) + max(PlotData$count)/5)
+  Plot.Final <- Plot.init + 
+    ylim(c(0, 20)) + 
+    ggrepel::geom_label_repel(data = CheckParents,
+                              aes(x = value, y = yval, label = Genotype),
[…]

### 2022-04-01 doc/manuscript/manuscript.Rmd
A lot idk

---
title: Identification of high-yielding soybean lines with exceptional seed composition qualities
author:
  - name: Jay Gillenwater
    affil: 1,2,\ddagger,*
    orcid: 0000-0003-3293-2315
  - name: John Doe
    affil: 2, \dagger, \ddagger
affiliation:
  - num: 1
    address: |
      Muenster University of Applied Sciences - 
      Institute for Infrastructure, Water, Resources, Environment
      Correnstr. 25, 48149 Muenster, Germany
    email: leutnant@fh-muenster.de
  - num: 2
    address: |
      Your department
      Street, City, Country
    email: jhgille2@ncsu.edu
# firstnote to eighthnote
firstnote: |
  Current address: Updated affiliation
secondnote: |
  These authors contributed equally to this work.
correspondence: |
  leutnant@fh-muenster.de; Tel.: +XX-000-00-0000.
journal: Agronomy
type: article
status: submit
bibliography: mybibfile.bib
appendix: appendix.tex
simplesummary: |
  A Simple summary goes here.
abstract: |
  A single paragraph of about 200 words maximum. For research articles, 
  abstracts should give a pertinent overview of the work. We strongly encourage
  authors to use the following style of structured abstracts, but without 
  headings: 1) Background: Place the question addressed in a broad context and
  highlight the purpose of the study; 2) Methods: Describe briefly the main
  methods or treatments applied; 3) Results: Summarize the article's main 
  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
  The abstract should be an objective representation of the article, it must not 
  contain results which are not presented and substantiated in the main text and 
  should not exaggerate the main conclusions.
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  For research articles with several authors, a short paragraph specifying their 
  individual contributions must be provided. The following statements should be 
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.
conflictsofinterest: |
  Declare conflicts of interest or state 'The authors declare no conflict of 
  interest.' Authors must identify and declare any personal circumstances or
  interest that may be perceived as inappropriately influencing the
  representation or interpretation of reported research results. Any role of the
  funding sponsors in the design of the study; in the collection, analyses or 
  interpretation of data in the writing of the manuscript, or in the decision to 
  publish the results must be declared in this section. If there is no role, 
  please state 'The founding sponsors had no role in the design of the study; 
  in the collection, analyses, or interpretation of data; in the writing of the 
  manuscript, an in the decision to publish the results'.
sampleavailability: |
  Samples of the compounds ...... are available from the authors.
abbreviations:
  - short: MDPI
    long: Multidisciplinary Digital Publishing Institute
  - short: DOAJ
    long: Directory of open access journals
  - short: TLA
    long: Three letter acronym
  - short: LD 
    long: linear dichroism
output: rticles::mdpi_article
---

```{r setup, warning=FALSE,echo = FALSE, message=FALSE}
library(here)
source(here("packages.R"))
tar_load(c(example_table))
```

# Version

This Rmd-skeleton uses the mdpi Latex template published 2019/02. 
However, the official template gets more frequently updated than the 'rticles'
package. Therefore, please make sure prior to paper submission, that you're 
using the most recent .cls, .tex and .bst files 
(available [here](http://www.mdpi.com/authors/latex)).

# Introduction

The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper [@bertrand-krajewski_distribution_1998; @leutnant_stormwater_2016]. And now citing a book reference @gujer_systems_2008. Please use the command [@leutnant_stormwater_2016] for the following MDPI journals, which use author-date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences.

# Materials and Methods

## Population development
In 2018, oil mapping populations 201 and 202 were grown at the Central Crops Research Station in Clayton, NC. These populations consisted of 273 and 237 recombinant inbred lines (RILs) respectively. Several agronomic traits were scored in the field for each population. These included height, lodging, maturity date, and a composite agronomic score. Lodging was scored on a scale of 1-5 where 5indicates that all plants in a plot are on the ground, and a score of 1 indicates that all plants are erect[Feh87]. The agronomic score aimed to capture other traits of value such as visual estimation of pod load and plot uniformity to provide a general score of a line’s agronomic desirability. Agronomic score was recorded on a scale of 1-5 aswell, with 1 identifying the best lines of a population, and 5 the worst. Maturity was recorded at the R8 maturity date. Height was measured in centimeters from the soil to the top of the plant. Following harvest, yield, seed weight, protein, and oil content were measured after seed was air dried to approximately 7% moisture content in a greenhouse. Protein and oil contents were measured on a dry basis using a Perten DA 7250 NIR®instrument. Yield and seed weight were measured after seed had been sifted and cleaned of debris and cracked seed. To select lines for the 2019 growing season, lines with abnormally low bulk weights or extreme maturity dates from 2018 were first removed from consideration. Two yield trials were then developed for each mapping population. The maturity data of RILs were considered when forming tests such that the lines of each test would have a maturity data range approximately half that of the total mapping population from which it was derived. RILs were selected for each test which were also representative of the distribution of seed protein and seed oil traits for each population. Eighty unique lines were selected from each population which satisfied these criteria, and each yield test was comprised of 40 RILs. Three high-yielding check cultivars and the two parents of the respective population were also included in each test. Yield check cultivars Dunphy, Osage, and Roy were used in tests 1 and 2, while Dunphy, Dilday, and N.C. Raleigh were used for tests 3 and 4. These lines were selected to represent the estimated maturities of the RILs in each test. The parents for tests 1 and 2 were cultivars LMN09-119 and N09-09, and the parents for tests 3 and 4 were LMN09-19 and N13-47.

These four tests were grown in two locations in 2019: the Tidewater Research Station in Plymouth, NC (PLY) and the Caswell Research Farm in Kinston, NC (CAS). The same data was collected for each test in this season that was collected in the previous season. Selections were done using this data by first identifying the lines with a yield within or above a least significant difference (LSD) of the average yield of the checks for each test. Further selection was done using the seed composition traits by identifying the thirty lines with the highest protein + oil content.

These thirty lines were then grouped into two new tests of 15 RILs each which were then grown in both the 2020 and 2021 seasons. Thesew tests were grown in CLA and CAS in 2020 and CAS and PLY in 2021.

Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.

# Results

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.

## Subsection Heading Here

Subsection text here.

### Subsubsection Heading Here

Bulleted lists look like this:

* First bullet
* Second bullet
* Third bullet

Numbered lists can be added as follows:

1. First item
2. Second item
3. Third item

The text continues here.

All figures and tables should be cited in the main text as Figure 1, Table 1, etc.

```{r example_plot, echo = FALSE}
tar_load(example_plot)
```

\begin{figure}[H]
\centering
\includegraphics[width=10 cm]{`r example_plot`}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=3 cm]{logo-mdpi}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}

\begin{table}[H]
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccc}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
entry 1		& data			& data\\
entry 2		& data			& data\\
\bottomrule
\end{tabular}
\end{table}

```{r test_table, results = "asis", echo = FALSE}
print(example_table)
```

This is an example of an equation:

\begin{equation}
\mathbb{S}
\end{equation}
<!-- If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph. -->

<!-- Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows: -->
Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

Example of a proof:
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
\end{proof}
The text continues here.

# Discussion

Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

# Conclusion

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

# Patents

This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.

### 2022-04-01 doc/manuscript/manuscript.tex
A lot idk

%  LaTeX support: latex@mdpi.com
%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).

%=================================================================
\documentclass[Agronomy,article,submit,moreauthors,pdftex]{mdpi}

% If you would like to post an early version of this manuscript as a preprint, you may use preprint as the journal and change 'submit' to 'accept'. The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%% Some pieces required from the pandoc template
\setlist[itemize]{leftmargin=*,labelsep=5.8mm}
\setlist[enumerate]{leftmargin=*,labelsep=4.9mm}

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, aerospace, agriculture, agriengineering, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, asc, asi, atmosphere, atoms, axioms, batteries, bdcc, behavsci , beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci , buildings, cancers, carbon , catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, children, cleantechnol, climate, clockssleep, cmd, coatings, colloids, computation, computers, condensedmatter, cosmetics, cryptography, crystals, dairy, data, dentistry, designs , diagnostics, diseases, diversity, drones, econometrics, economies, education, electrochem, electronics, energies, entropy, environments, epigenomes, est, fermentation, fibers, fire, fishes, fluids, foods, forecasting, forests, fractalfract, futureinternet, futurephys, galaxies, games, gastrointestdisord, gels, genealogy, genes, geohazards, geosciences, geriatrics, hazardousmatters, healthcare, heritage, highthroughput, horticulturae, humanities, hydrology, ijerph, ijfs, ijgi, ijms, ijns, ijtpp, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jcdd, jcm, jcp, jcs, jdb, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmse, jnt, jof, joitmc, jpm, jrfm, jsan, land, languages, laws, life, literature, logistics, lubricants, machines, magnetochemistry, make, marinedrugs, materials, mathematics, mca, medicina, medicines, medsci, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, modelling, molbank, molecules, mps, mti, nanomaterials, ncrna, neuroglia, nitrogen, notspecified, nutrients, ohbm, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, physics, plants, plasma, polymers, polysaccharides, preprints , proceedings, processes, proteomes, psych, publications, quantumrep, quaternary, qubs, reactions, recycling, religions, remotesensing, reports, resources, risks, robotics, safety, sci, scipharm, sensors, separations, sexes, signals, sinusitis, smartcities, sna, societies, socsci, soilsystems, sports, standards, stats, surfaces, surgeries, sustainability, symmetry, systems, technologies, test, toxics, toxins, tropicalmed, universe, urbansci, vaccines, vehicles, vetsci, vibration, viruses, vision, water, wem, wevj

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by:
% abstract, addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, conferenceproceedings, correction, conferencereport, expressionofconcern, extendedabstract, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, meetingreport, newbookreceived, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, supfile, technicalnote, viewpoint
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{xx}
\issuenum{1}
\articlenumber{5}
\pubyear{2019}
\copyrightyear{2019}
%\externaleditor{Academic Editor: name}
\history{Received: date; Accepted: date; Published: date}
\updates{yes} % If there is an update available, un-comment this line

%% MDPI internal command: uncomment if new journal that already uses continuous page numbers
%\continuouspages{yes}

%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Identification of high-yielding soybean lines with exceptional
seed composition qualities}

% Authors, for the paper (add full first names)
\Author{Jay
Gillenwater$^{1,2,\ddagger,*}$\href{https://orcid.org/0000-0003-3293-2315}{\orcidicon}, John
Doe$^{2, \dagger, \ddagger}$}

% Authors, for metadata in PDF
\AuthorNames{Jay Gillenwater, John Doe}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Muenster University of Applied Sciences - Institute for
Infrastructure, Water, Resources, Environment Correnstr. 25, 48149
Muenster,
Germany; \href{mailto:leutnant@fh-muenster.de}{\nolinkurl{leutnant@fh-muenster.de}}\\
$^{2}$ \quad Your department Street, City,
Country; \href{mailto:jhgille2@ncsu.edu}{\nolinkurl{jhgille2@ncsu.edu}}\\
}
% Contact information of the corresponding author
\corres{Correspondence: \href{mailto:leutnant@fh-muenster.de}{\nolinkurl{leutnant@fh-muenster.de}};
Tel.: +XX-000-00-0000.}

% Current address and/or shared authorship
\firstnote{Current address: Updated affiliation}
\secondnote{These authors contributed equally to this work.}

% The commands \thirdnote{} till \eighthnote{} are available for further notes

% Simple summary
\simplesumm{A Simple summary goes here.}

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{A single paragraph of about 200 words maximum. For research
articles, abstracts should give a pertinent overview of the work. We
strongly encourage authors to use the following style of structured
abstracts, but without headings: 1) Background: Place the question
addressed in a broad context and highlight the purpose of the study; 2)
Methods: Describe briefly the main methods or treatments applied; 3)
Results: Summarize the article's main findings; and 4) Conclusion:
Indicate the main conclusions or interpretations. The abstract should be
an objective representation of the article, it must not contain results
which are not presented and substantiated in the main text and should
not exaggerate the main conclusions.}

% Keywords
\keyword{keyword 1; keyword 2; keyword 3 (list three to ten pertinent
keywords specific to the article, yet reasonably common within the
subject discipline.).}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences:
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:
%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately. If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal. In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}

%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%\setcounter{secnumdepth}{4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hypertarget{version}{%
\section{Version}\label{version}}

This Rmd-skeleton uses the mdpi Latex template published 2019/02.
However, the official template gets more frequently updated than the
`rticles' package. Therefore, please make sure prior to paper
submission, that you're using the most recent .cls, .tex and .bst files
(available \href{http://www.mdpi.com/authors/latex}{here}).

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

The introduction should briefly place the study in a broad context and
highlight why it is important. It should define the purpose of the work
and its significance. The current state of the research field should be
reviewed carefully and key publications cited. Please highlight
controversial and diverging hypotheses when necessary. Finally, briefly
mention the main aim of the work and highlight the principal
conclusions. As far as possible, please keep the introduction
comprehensible to scientists outside your particular field of research.
Citing a journal paper
\citep{bertrand-krajewski_distribution_1998, leutnant_stormwater_2016}.
And now citing a book reference \citet{gujer_systems_2008}. Please use
the command \citep{leutnant_stormwater_2016} for the following MDPI
journals, which use author-date citation: Administrative Sciences, Arts,
Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws,
Religions, Risks, Social Sciences.

\hypertarget{materials-and-methods}{%
\section{Materials and Methods}\label{materials-and-methods}}

\hypertarget{population-development}{%
\subsection{Population development}\label{population-development}}

In 2018, oil mapping populations 201 and 202 were grown at the Central
Crops Research Station in Clayton, NC. These populations consisted of
273 and 237 recombinant inbred lines (RILs) respectively. Several
agronomic traits were scored in the field for each population. These
included height, lodging, maturity date, and a composite agronomic
score. Lodging was scored on a scale of 1-5 where 5indicates that all
plants in a plot are on the ground, and a score of 1 indicates that all
plants are erect{[}Feh87{]}. The agronomic score aimed to capture other
traits of value such as visual estimation of pod load and plot
uniformity to provide a general score of a line's agronomic
desirability. Agronomic score was recorded on a scale of 1-5 aswell,
with 1 identifying the best lines of a population, and 5 the worst.
Maturity was recorded at the R8 maturity date. Height was measured in
centimeters from the soil to the top of the plant. Following harvest,
yield, seed weight, protein, and oil content were measured after seed
was air dried to approximately 7\% moisture content in a greenhouse.
Protein and oil contents were measured on a dry basis using a Perten DA
7250 NIR®instrument. Yield and seed weight were measured after seed had
been sifted and cleaned of debris and cracked seed. To select lines for
the 2019 growing season, lines with abnormally low bulk weights or
extreme maturity dates from 2018 were first removed from consideration.
Two yield trials were then developed for each mapping population. The
maturity data of RILs were considered when forming tests such that the
lines of each test would have a maturity data range approximately half
that of the total mapping population from which it was derived. RILs
were selected for each test which were also representative of the
distribution of seed protein and seed oil traits for each population.
Eighty unique lines were selected from each population which satisfied
these criteria, and each yield test was comprised of 40 RILs. Three
high-yielding check cultivars and the two parents of the respective
population were also included in each test. Yield check cultivars
Dunphy, Osage, and Roy were used in tests 1 and 2, while Dunphy, Dilday,
and N.C. Raleigh were used for tests 3 and 4. These lines were selected
to represent the estimated maturities of the RILs in each test. The
parents for tests 1 and 2 were cultivars LMN09-119 and N09-09, and the
parents for tests 3 and 4 were LMN09-19 and N13-47.

These four tests were grown in two locations in 2019: the Tidewater
Research Station in Plymouth, NC (PLY) and the Caswell Research Farm in
Kinston, NC (CAS). The same data was collected for each test in this
season that was collected in the previous season. Selections were done
using this data by first identifying the lines with a yield within or
above a least significant difference (LSD) of the average yield of the
checks for each test. Further selection was done using the seed
composition traits by identifying the thirty lines with the highest
protein + oil content.

These thirty lines were then grouped into two new tests of 15 RILs each
which were then grown in both the 2020 and 2021 seasons. Thesew tests
were grown in CLA and CAS in 2020 and CAS and PLY in 2021.

Materials and Methods should be described with sufficient details to
allow others to replicate and build on published results. Please note
that publication of your manuscript implicates that you must make all
materials, data, computer code, and protocols associated with the
publication available to readers. Please disclose at the submission
stage any restrictions on the availability of materials or information.
New methods and protocols should be described in detail while
well-established methods can be briefly described and appropriately
cited.

Research manuscripts reporting large datasets that are deposited in a
publicly available database should specify where the data have been
deposited and provide the relevant accession numbers. If the accession
numbers have not yet been obtained at the time of submission, please
state that they will be provided during review. They must be provided
prior to publication.

Interventionary studies involving animals or humans, and other studies
require ethical approval must list the authority that provided approval
and the corresponding ethical approval code.

\hypertarget{results}{%
\section{Results}\label{results}}

This section may be divided by subheadings. It should provide a concise
and precise description of the experimental results, their
interpretation as well as the experimental conclusions that can be
drawn.

\hypertarget{subsection-heading-here}{%
\subsection{Subsection Heading Here}\label{subsection-heading-here}}

Subsection text here.

\hypertarget{subsubsection-heading-here}{%
\subsubsection{Subsubsection Heading
Here}\label{subsubsection-heading-here}}

Bulleted lists look like this:

\begin{itemize}
\tightlist
\item
  First bullet
\item
  Second bullet
\item
  Third bullet
\end{itemize}

Numbered lists can be added as follows:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  First item
\item
  Second item
\item
  Third item
\end{enumerate}

The text continues here.

All figures and tables should be cited in the main text as Figure 1,
Table 1, etc.

\begin{figure}[H]
\centering
\includegraphics[width=10 cm]{C:/Users/jhgille2/Documents/R/projects/Jay_yield/exports/plots/example_plot.pdf}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=3 cm]{logo-mdpi}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}

\begin{table}[H]
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccc}
\toprule
\textbf{Title 1}    & \textbf{Title 2}  & \textbf{Title 3}\\
\midrule
entry 1     & data          & data\\
entry 2     & data          & data\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}

\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
\centering
\begin{tabular}[t]{lrrrrrrrrrrr}
\toprule
\textbf{ } & \textbf{mpg} & \textbf{cyl} & \textbf{disp} & \textbf{hp} & \textbf{drat} & \textbf{wt} & \textbf{qsec} & \textbf{vs} & \textbf{am} & \textbf{gear} & \textbf{carb}\\
\midrule
Mazda RX4 & 21.0 & 6 & 160 & 110 & 3.90 & 2.620 & 16.46 & 0 & 1 & 4 & 4\\
Mazda RX4 Wag & 21.0 & 6 & 160 & 110 & 3.90 & 2.875 & 17.02 & 0 & 1 & 4 & 4\\
Datsun 710 & 22.8 & 4 & 108 & 93 & 3.85 & 2.320 & 18.61 & 1 & 1 & 4 & 1\\
Hornet 4 Drive & 21.4 & 6 & 258 & 110 & 3.08 & 3.215 & 19.44 & 1 & 0 & 3 & 1\\
Hornet Sportabout & 18.7 & 8 & 360 & 175 & 3.15 & 3.440 & 17.02 & 0 & 0 & 3 & 2\\
\addlinespace
Valiant & 18.1 & 6 & 225 & 105 & 2.76 & 3.460 & 20.22 & 1 & 0 & 3 & 1\\
\bottomrule
\end{tabular}
\end{table}

This is an example of an equation:

\begin{equation}
\mathbb{S}
\end{equation}

Example of a theorem:

\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

Example of a proof:

\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
\end{proof}

The text continues here.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

Authors should discuss the results and how they can be interpreted in
perspective of previous studies and of the working hypotheses. The
findings and their implications should be discussed in the broadest
context possible. Future research directions may also be highlighted.

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

This section is not mandatory, but can be added to the manuscript if the
discussion is unusually long or complex.

\hypertarget{patents}{%
\section{Patents}\label{patents}}

This section is not mandatory, but may be added if there are patents
resulting from the work reported in this manuscript.

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %% optional
% \supplementary{The following are available online at www.mdpi.com/link, Figure S1: title, Table S1: title, Video S1: title.}
%
% % Only for the journal Methods and Protocols:
% % If you wish to submit a video article, please do so with any other supplementary material.
% % \supplementary{The following are available at www.mdpi.com/link: Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}

\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{All sources of funding of the study should be
disclosed. Please clearly indicate grants that you have received in
support of your research work. Clearly state if you received funds for
covering the costs to publish in open access.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short
paragraph specifying their individual contributions must be provided.
The following statements should be used ``X.X. and Y.Y. conceive and
designed the experiments; X.X. performed the experiments; X.X. and Y.Y.
analyzed the data; W.W. contributed reagents/materials/analysis tools;
Y.Y. wrote the paper.'\,' Authorship must be limited to those who have
contributed substantially to the work reported.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictsofinterest{Declare conflicts of interest or state `The authors
declare no conflict of interest.' Authors must identify and declare any
personal circumstances or interest that may be perceived as
inappropriately influencing the representation or interpretation of
reported research results. Any role of the funding sponsors in the
design of the study; in the collection, analyses or interpretation of
data in the writing of the manuscript, or in the decision to publish the
results must be declared in this section. If there is no role, please
state `The founding sponsors had no role in the design of the study; in
the collection, analyses, or interpretation of data; in the writing of
the manuscript, an in the decision to publish the results'.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\abbreviations{The following abbreviations are used in this manuscript:\\

\noindent
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute \\
DOAJ & Directory of open access journals \\
TLA & Three letter acronym \\
LD & linear dichroism \\
\end{tabular}}

\input{"appendix.tex"}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: internal bibliography
%=====================================
%\reftitle{References}
%\begin{thebibliography}{999}
% Reference 1
%\bibitem[Author1(year)]{ref-journal}
%Author1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
% Reference 2
%\bibitem[Author2(year)]{ref-book}
%Author2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
%\end{thebibliography}

% The following MDPI journals use author-date citation: Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences. For those journals, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%=====================================
% References, variant B: external bibliography
%=====================================
\reftitle{References}
\externalbibliography{yes}
\bibliography{mybibfile.bib}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\sampleavailability{Samples of the compounds \ldots\ldots{} are
available from the authors.}

%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2022-04-01 R/make_example_plot.R

@@ -1,0 +1,27 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param all_yield_data
+#' @param test_name_colors
+#' @param dir
+make_example_plot <- function(all_yield_data, test_name_colors, dir =
+                              here("exports", "plots", "example_plot.pdf")) {
+
+  # Get just the data from 2019
+  data_2019 <- all_yield_data$all %>% 
+    reduce(bind_rows) %>%
+    dplyr::filter(str_detect(test, "Yield Test"))
+  
+  test_colors <- test_name_colors[names(test_name_colors) %in% unique(data_2019$test)]
+  
+ p <-  ggplot(data_2019, aes(y = yield, fill = test)) + 
+   geom_boxplot() + 
+   theme_calc() + 
+   scale_fill_manual(values = test_colors)
+ 
+ ggsave(dir, plot = p, device = "pdf", width = 5, height = 5, units = "in")
+ 
+ return(dir)
+}

### 2022-04-01 R/make_example_table.R

@@ -1,0 +1,16 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+
+make_example_table <- function() {
+
+  data(mtcars)
+  
+  ex_kable <- head(mtcars) %>% 
+    kable(format = "latex", caption = "This is a table caption. Tables should be placed in the main text near to the first time they are cited.", booktabs = TRUE) %>% row_spec(0,bold=TRUE) %>% 
+    kable_styling()
+  
+  return(ex_kable)
+}

### 2022-04-01 R/read_util_tables.R

@@ -5,16 +5,18 @@
 #' @title
 #' @param yield_check_genotypes
 #' @param genotype_conversion
-read_util_tables <- function(yield_check_genotypes, genotype_conversion, trait_conversion) {
+read_util_tables <- function(yield_check_genotypes, genotype_conversion, trait_conversion, trait_shortname_conversion) {
 
   # Read in each file and return the dataframes in a list
   yield_checks        <- read_excel(yield_check_genotypes)
   genotype_conversion <- read_excel(genotype_conversion)
   trait_lookup        <- read_excel(trait_conversion)
+  trait_shortnames    <- read_excel(trait_shortname_conversion)
   
   res <- list("check_table"               = yield_checks, 
               "genotype_conversion_table" = genotype_conversion, 
-              "trait_lookup"              = trait_lookup)
+              "trait_lookup"              = trait_lookup, 
+              "trait_shortnames"          = trait_shortnames)
   
   return(res)
 }

### 2022-04-01 R/utils.R

@@ -38,3 +38,23 @@ match_from_table <- function(old_name, conversiontable){
   return(converted_name)
 }
 
+
+# A function to replace the names of a dataframe by using a lookup table
+rename_with_lookup <- function(df, lookup){
+  
+  index_match <- function(vec, convert_table){
+    matches     <- match(vec, unlist(convert_table[, 1]))
+    matches_ind <- which(!is.na(matches))
+    
+    replacement <- unlist(convert_table[, 2])[matches[matches_ind]]
+    
+    return(list("index" = matches_ind, 
+                "replacement" = replacement))
+  }
+  
+  replacement_names <- index_match(names(df), lookup)
+  
+  names(df)[replacement_names$index] <- replacement_names$replacement
+  
+  return(df)
+}

### 2022-04-01 _targets.R

@@ -55,12 +55,21 @@ tar_plan(
              here("data", "utils", "trait_name_lookup.xlsx"), 
              format = "file"),
   
+  # A table to convert short phenotype names to longer names that don't 
+  # have units included
+  tar_target(trait_shortname_conversion, 
+             here("data", "utils", "trait_shortname_lookup.xlsx"), 
+             format = "file"),
+  
   ## Section: Data cleaning
   ##################################################
   
   # Read in the utility tables
   tar_target(util_tables, 
-             read_util_tables(yield_check_genotypes, genotype_conversion, trait_conversion)),
+             read_util_tables(yield_check_genotypes, 
+                              genotype_conversion, 
+                              trait_conversion, 
+                              trait_shortname_conversion)),
   
   # Cleaning up and merging the data from the three seasons
   tar_target(all_yield_data, 
@@ -103,8 +112,18 @@ tar_plan(
   tar_target(BLUE_plots_two_years, 
              make_genotype_blue_plots(fit_models = mixed_models_two_years)),
   
+  tar_target(example_table, 
+             make_example_table()),
+  
+  # A example plot to use for testing manuscript markdown rendering
+  tar_target(example_plot, 
+             make_example_plot(all_yield_data, test_name_colors, dir = here("exports", "plots", "example_plot.pdf")), 
+             format = "file"),
+  
   ## Section: Writeup documents
   ##################################################
-  tar_render(analysis_writeup, "doc/analysis_writeup.Rmd")
+  tar_render(analysis_writeup, "doc/analysis_writeup.Rmd"), 
+  
+  tar_render(manuscript_document, here("doc", "manuscript", "manuscript.Rmd"))
   
 )

### 2022-04-01 packages.R

@@ -3,7 +3,7 @@ if(!require(pacman)){
   install.packages("pacman")
 }
 
-# Use pacman to load/install packaged
+# Use pacman to load/install packages
 pacman::p_load(conflicted, 
                dotenv, 
                targets, 
@@ -19,13 +19,16 @@ pacman::p_load(conflicted,
                lattice, 
                ggpubr, 
                ggcorrplot, 
+               patchwork,
                extrafont, 
                GGally, 
                agricolae, 
                lme4, 
                emmeans, 
                kableExtra, 
-               pander)
+               pander, 
+               visNetwork,
+               kableExtra)
 
 # Function preference
 conflicted::conflict_prefer("filter", "dplyr", "base")

### 2022-04-01 sandbox/correlation plots.R

@@ -1,0 +1,25 @@
+##################################################
+## Project: Jay Yield
+## Script purpose: descriptive statistics for two year data
+## Date: 2022-04-01
+## Author: Jay Gillenwater
+##################################################
+
+# Load the yield data
+tar_load(all_yield_data)
+tar_load(test_name_colors)
+tar_load(util_tables)
+
+data_twoyear <- all_yield_data$two_year %>% 
+  reduce(bind_rows) %>% 
+  rename_with_lookup(., util_tables$trait_shortnames)
+
+
+desc_stat(data_twoyear, hist = TRUE, by = test)
+
+corr_two_year <- map(all_yield_data$two_year, function(x) rename_with_lookup(x, util_tables$trait_shortnames)) %>% 
+  map(., corr_coef) %>% 
+  map(., plot)
+
+x11()
+arrange_ggplot(corr_two_year, tag_levels = list(names(corr_two_year)))

### 2022-04-01 sandbox/ge plots.R

@@ -1,0 +1,50 @@
+##################################################
+## Project: Jay Yield
+## Script purpose: Development of scatter plots to show pairwise 
+## relationships between traits
+## Date: 2022-04-01
+## Author: Jay Gillenwater
+##################################################
+
+
+# Load in the data to use in the histograms
+tar_load(util_tables)
+tar_load(genotype_BLUEs)
+tar_load(all_yield_data)
+tar_load(test_name_colors)
+
+all_data <- reduce(genotype_BLUEs$BLUEs, bind_rows)
+
+test1 <- ge_plot(all_yield_data$two_year$`Jay Test 1`, 
+                 env = ENV, 
+                 gen = genotype, 
+                 resp = yield) + 
+  theme(axis.text.x = element_text(angle = 75, hjust = 1, vjust = 1))
+
+test2 <- ge_plot(all_yield_data$two_year$`Jay Test 2`, 
+                 env = ENV, 
+                 gen = genotype, 
+                 resp = yield) + 
+  theme(axis.text.x = element_text(angle = 75, hjust = 1, vjust = 1))
+
+x11()
+arrange_ggplot(test1, test2, tag_levels = list("Test 1", "Test 2"))
+
+index_match <- function(vec, convert_table){
+  matches     <- match(vec, unlist(convert_table[, 1]))
+  matches_ind <- which(!is.na(matches))
+  
+  replacement <- unlist(convert_table[, 2])[matches[matches_ind]]
+  
+  return(list("index" = matches_ind, 
+              "replacement" = replacement))
+}
+
+replacement_names <- index_match(names(all_data), util_tables$trait_shortnames)
+
+names(all_data)[replacement_names$index] <- replacement_names$replacement
+
+ggplot(all_data, aes(x = protein, y = yield, fill = test_name)) + 
+  geom_point(color = "black", shape = 21, size = 5) + 
+  geom_smooth(method = "lm") + 
+  theme_few()

### 2022-04-01 sandbox/histogram development.R

@@ -1,13 +1,23 @@
+##################################################
+## Project: Jay Yield
+## Script purpose: Development of function(s) for annotated histograms
+## Date: 2022-04-01
+## Author: Jay Gillenwater
+##################################################
+
+# Load in the data to use in the histograms
 tar_load(util_tables)
 tar_load(genotype_BLUEs)
 tar_load(all_yield_data)
 tar_load(test_name_colors)
 
+# Combine all the yield data into a single data frame
 all_yield <- reduce(all_yield_data$all, bind_rows)
 
-util_tables$genotype_conversion_table$genotype[match(all_yield$genotype, util_tables$genotype_conversion_table$old_genotype)]
-
-
+# A function to replace values in a column with their match from a 
+# conversion table. The current value in the data column should be one of 
+# the values in the first column of the conversion table and the second
+# column should hold what the value should be converted to
 convert_from_table <- function(data, var, conversiontable){
   
   all_matches   <- match(unlist(data[, var]), unlist(conversiontable[, 1]))
@@ -22,12 +32,13 @@ convert_from_table <- function(data, var, conversiontable){
   return(data)
 }
 
+# Use the genotype conversion utility table to standardize the check genotype names
 convert_from_table(all_yield, "genotype", util_tables$genotype_conversion_table)
 
 tar_load(genotype_BLUEs)
 
 # A function to make a labelled histogram
-labelled_histogram <- function(blue_data, test_colors, trait_name, check_genotypes, trait_name_lookup){
+labelled_histogram <- function(blue_data, test_colors, trait_name, check_genotypes, trait_name_lookup, label_genotypes = NULL){
   
   # Use the lookup table to convert the trait name to its fancy counterpart
   fancy_trait_name <- match_from_table(trait_name, trait_name_lookup)
@@ -36,7 +47,7 @@ labelled_histogram <- function(blue_data, test_colors, trait_name, check_genotyp
   # The initial plot (need bin heights)
   Plot.init <- ggplot(blue_data, aes_string(x = trait_name, fill = test_name)) + 
     geom_histogram(bins = 9, col = 'black') + 
-    theme_bw() + 
+    theme_calc() + 
     theme(axis.text = element_text(size = 20, face = 'bold'),
           axis.title = element_text(size = 30)) + 
     ylab("Count") + 
@@ -47,7 +58,7 @@ labelled_histogram <- function(blue_data, test_colors, trait_name, check_genotyp
[…]

### 2022-04-08 doc/manuscript/manuscript.Rmd
Worked on a couple of functions in the sandbox directory to make some nicer looking summary tables. Also rearranged the packages file a little bit to keep categories of packages together.

@@
 
-These thirty lines were then grouped into two new tests of 15 RILs each which were then grown in both the 2020 and 2021 seasons. Thesew tests were grown in CLA and CAS in 2020 and CAS and PLY in 2021.
+These thirty lines were then grouped into two new tests of 15 RILs each which were then grown in both the 2020 and 2021 seasons. These tests were grown in CLA and CAS in 2020 and CAS and PLY in 2021.
+
+## Statistical Analysis
+The data for seed yield, seed oil, and seed protein contents were analyzed using a mixed model with the metan[@r_metan] R package.
+Environment, replication nested with environment, and the interaction of genotype with environment were considered to be random effects while genotype was considered to be a fixed effect.
 

### 2022-04-08 doc/manuscript/manuscript.tex
Worked on a couple of functions in the sandbox directory to make some nicer looking summary tables. Also rearranged the packages file a little bit to keep categories of packages together.

@@
 These thirty lines were then grouped into two new tests of 15 RILs each
-which were then grown in both the 2020 and 2021 seasons. Thesew tests
+which were then grown in both the 2020 and 2021 seasons. These tests
 were grown in CLA and CAS in 2020 and CAS and PLY in 2021.
+
+\hypertarget{statistical-analysis}{%
+\subsection{Statistical Analysis}\label{statistical-analysis}}
+
+The data for seed yield, seed oil, and seed protein contents were
+analyzed using a mixed model with the metan\citep{r_metan} R package.
+Environment, replication nested with environment, and the interaction of
+genotype with environment were considered to be random effects while
+genotype was considered to be a fixed effect.
 

### 2022-04-08 R/fit_mixed_models.R

@@ -14,7 +14,7 @@ fit_mixed_models <- function(df = all_yield_data$two_year) {
                            gen     = genotype, 
                            rep     = rep, 
                            resp    = everything(), 
-                           random  = "gen",
+                           random  = "env",
                            verbose = FALSE)
     
     return(model_fit)

### 2022-04-08 R/get_lsd_values.R

@@ -6,6 +6,88 @@
 #' @param df
 get_lsd_values <- function(df = all_yield_data$two_year) {
 
-  NULL
-
+  # A function to fit a linear model with the yield data for one test
+  fit_lm <- function(test_data){
+    
+    # Phenotypes to fit a model on
+    measure_vars <- c("md", 
+                      "ht", 
+                      "lod", 
+                      "oil", 
+                      "protein", 
+                      "yield", 
+                      "sdwt", 
+                      "sq", 
+                      "protein_plus_oil")
+    
+    # A function to apply to the nested data column to remove any observations
+    # with missing data. Also, remove the parent genotypes from the data 
+    # because the LSD.test function can only return a value for LSD/MSD if
+    # the data is perfectly balanced (as all things should be) and these genotypes
+    # were included multiple times in the tests.
+    clean_data <- function(pheno_data){
+      
+      pheno_data %<>%
+        dplyr::filter(!is.na(value), !genotype %in% c("LMN09-119", "N09-09"))
+      
+      genotype_reps <- pheno_data %>%
+        group_by(genotype) %>% 
+        count(name = "num_reps")
+      
+      rep_counts <- genotype_reps %>% 
+        group_by(num_reps) %>% 
+        count(name = "rep_count")
+      
+      max_rep_count <- rep_counts$num_reps[[which(rep_counts$rep_count == max(rep_counts$rep_count))]]
+      
+      keep_genos <- genotype_reps %>%
+        dplyr::filter(num_reps == max_rep_count)
+      
+      keep_genos <- as.character(keep_genos$genotype)
+      
+      pheno_data %<>% 
+        dplyr::filter(genotype %in% keep_genos)
+      
+      return(pheno_data)
+      
+    }
+    
+    # Pivot the data by these phenotypes and then nest by each phenotype
+    test_data %<>%
+      pivot_longer(cols = all_of(measure_vars), names_to = "trait") %>%
+      group_by(trait) %>% 
+      nest() %>% 
+      ungroup() %>%
+      mutate(data = map(data, clean_data))
+    
+    model_fn <- function(pheno_data) {
+      
+      # Fit a linear model on the data, perform an analysis of variance, 
+      # and then perform a least significant difference test
+      model     <- with(pheno_data, lm(value~ genotype + genotype:ENV + ENV/rep))
+      model_aov <- aov(model)
+      trait_lsd <- agricolae::LSD.test(model_aov, 
+                                       trt   = "genotype", 
[…]

### 2022-04-08 R/make_blue_table.R

@@ -9,7 +9,7 @@ make_blue_table <- function(fit_models = mixed_models_two_year) {
   # A function to extract the BLUEs from the fit models and then add the test name
   # to the summary table
   make_blue_summary <- function(fit_model, test_name){
-    get_model_data(fit_model, "blupg") %>% 
+    get_model_data(fit_model, "blueg") %>% 
       mutate(test_name = test_name) %>% 
       relocate(test_name, 1) %>% 
       rename(genotype = GEN) %>% 
@@ -18,7 +18,7 @@ make_blue_table <- function(fit_models = mixed_models_two_year) {
   
   # A function to get the GxE genotype blues
   make_ge_blue_summary <- function(fit_model, test_name){
-    get_model_data(fit_model, "blupge") %>% 
+    get_model_data(fit_model, "bluege") %>% 
       pivot_wider(names_from = ENV, values_from = c("md", 
                                                     "ht", 
                                                     "lod", 

### 2022-04-08 _targets.R

@@ -104,6 +104,10 @@ tar_plan(
   tar_target(gyt_model_two_years, 
              fit_gyt_model(df = all_yield_data$two_year)),
   
+  # LSD/MSD tests
+  tar_target(least_sig_differences, 
+             get_lsd_values(df = all_yield_data$two_year)),
+  
   
   ## Section: Analysis summaries
   ##################################################

### 2022-04-08 packages.R

@@ -4,34 +4,44 @@ if(!require(pacman)){
 }
 
 # Use pacman to load/install packages
+
+# Workflow/organization
 pacman::p_load(conflicted, 
                dotenv, 
                targets, 
-               tarchetypes, 
-               tidyverse, 
+               tarchetypes)
+
+# Data wrangling
+pacman::p_load(tidyverse, 
                here, 
                readxl, 
                janitor, 
-               metan, 
-               rmdformats, 
-               openxlsx, 
-               ggthemes, 
-               lattice, 
+               magrittr,
+               openxlsx)
+
+# Visualization
+pacman::p_load(ggthemes, 
+               lattice,
+               visNetwork,
                ggpubr, 
                ggcorrplot, 
                patchwork,
                extrafont, 
-               GGally, 
+               GGally)
+
+# Analysis
+pacman::p_load(metan,
                agricolae, 
                lme4, 
-               emmeans, 
+               emmeans,
+               agricolae)
+
+# Writeup
+pacman::p_load(rmdformats, 
                kableExtra, 
                pander, 
-               visNetwork,
-               kableExtra, 
-               agricolae, 
-               magrittr)
+               kableExtra)
 
-# Function preference
+# Function conflict preferences
 conflicted::conflict_prefer("filter", "dplyr", "base")
 

### 2022-04-08 sandbox/yield summary tables.R

@@ -1,0 +1,130 @@
+tar_load(least_sig_differences)
+
+
+# A function to get the minimum significant difference from the lsd results list
+get_msd <- function(fit_model){
+  msd <- fit_model %>% 
+    pluck("lsd") %>% 
+    pluck("statistics") %>% 
+    pluck("MSD")
+  
+  if(is.null(msd)){
+    msd <- NA
+  }
+  
+  msd <- round(msd, 2)
+  
+  return(msd)
+}
+
+
+
+##################################################
+## Project: Jay Yield
+## Script purpose: Testing out functions to make sumamry tables of the 
+## phenotype BLUEs/MSD tables
+## Date: 2022-04-08
+## Author: Jay Gillenwater
+##################################################
+
+# Load in the BLUEs, utility tables, and MSDs
+tar_load(genotype_BLUEs)
+tar_load(util_tables)
+tar_load(least_sig_differences)
+
+# A function that takes the phenotype BLUEs table and calculates some summary
+# information for each phenotype: 
+#
+# 1. The overall test average, 
+# 2. The average for the checks
+# 3. The rank of each genoype
+make_pheno_comparison <- function(test_data){
+  
+  keep_phenos <- c("yield", "protein", "oil", "protein_plus_oil")
+  
+  genotype_ranks <- test_data %>% 
+    pivot_longer(cols = util_tables$trait_shortnames$name, 
+                 names_to = "pheno") %>% 
+    group_by(pheno) %>% 
+    arrange(desc(value)) %>% 
+    mutate(rank = 1:n()) %>% 
+    ungroup() %>%
+    group_by(pheno) %>% 
+    mutate(test_avg = mean(value, na.rm = TRUE)) %>% 
+    dplyr::filter(pheno %in% keep_phenos) %>% 
+    mutate(pheno = ordered(pheno, keep_phenos)) %>%
+    mutate(value = round(value, 2), 
+           test_avg = round(test_avg, 2))
+  
+  check_pheno_avg <- test_data %>% 
+    dplyr::filter(genotype %in% util_tables$check_table$genotype) %>% 
+    pivot_longer(cols = util_tables$trait_shortnames$name, 
+                 names_to = "pheno") %>% 
+    group_by(pheno) %>% 
+    summarise(check_avg_value = mean(value, na.rm = TRUE)) %>% 
+    mutate(check_avg_value = round(check_avg_value, 2))
+  
+  left_join(genotype_ranks, check_pheno_avg, by = "pheno")
+  
+}
+
[…]

### 2022-04-11 doc/manuscript/manuscript.Rmd
small changes to the yield summary table, and utility function file

@@
 ## Statistical Analysis
-The data for seed yield, seed oil, and seed protein contents were analyzed using a mixed model with the metan[@r_metan] R package.
+The data for seed yield, seed oil, and seed protein contents were analyzed using a mixed model with the metan[@olivotoMetanPackageMultienvironment2020] R package.
 Environment, replication nested with environment, and the interaction of genotype with environment were considered to be random effects while genotype was considered to be a fixed effect.

### 2022-04-11 R/utils.R

@@ -42,9 +42,9 @@ match_from_table <- function(old_name, conversiontable){
 # A function to replace the names of a dataframe by using a lookup table
 rename_with_lookup <- function(df, lookup){
   
-  index_match <- function(vec, convert_table){
-    matches     <- match(vec, unlist(convert_table[, 1]))
-    matches_ind <- which(!is.na(matches))
+   index_match <- function(vec, convert_table){
+   matches     <- match(vec, unlist(convert_table[, 1]))
+   matches_ind <- which(!is.na(matches))
     
     replacement <- unlist(convert_table[, 2])[matches[matches_ind]]
     

### 2022-04-11 sandbox/yield summary tables.R

@@ -1,5 +1,16 @@
-tar_load(least_sig_differences)
+##################################################
+## Project: Jay Yield
+## Script purpose: Testing out functions to make summary tables of the 
+## phenotype BLUEs/MSD tables
+## Date: 2022-04-08
+## Author: Jay Gillenwater
+##################################################
 
+
+# Load in the BLUEs, utility tables, and MSDs
+tar_load(genotype_BLUEs)
+tar_load(util_tables)
+tar_load(least_sig_differences)
 
 # A function to get the minimum significant difference from the lsd results list
 get_msd <- function(fit_model){
@@ -17,30 +28,36 @@ get_msd <- function(fit_model){
   return(msd)
 }
 
+# A helper function for identifying the column indices of some phenotype
+# when multiple variables are recorded for multiple phenotypes. The specific
+# issue this function resolves is overlaps in matches for oil/protein with
+# oil_plus_protein
+get_pheno_indices <- function(column_names, pheno_name, name_conversion = util_tables$trait_shortnames){
+  
+  # Get all the string matches and then exclude protein_plus_oil if the pheno_name
+  # is either protein or oil
+  all_matches <- str_detect(column_names, pheno_name)
+  
+  if(pheno_name %in% c("protein", "oil")){
+    p_o_matches <- str_detect(column_names, "protein_plus_oil")
+    final_matches <- (all_matches & !p_o_matches) %>% 
+      which()
+  }else{
+    final_matches <- which(all_matches)
+  }
+  
+  # Get cleaned up names for the column indices
+  return(final_matches)
+}
 
-
-##################################################
-## Project: Jay Yield
-## Script purpose: Testing out functions to make sumamry tables of the 
-## phenotype BLUEs/MSD tables
-## Date: 2022-04-08
-## Author: Jay Gillenwater
-##################################################
-
-# Load in the BLUEs, utility tables, and MSDs
-tar_load(genotype_BLUEs)
-tar_load(util_tables)
-tar_load(least_sig_differences)
 
 # A function that takes the phenotype BLUEs table and calculates some summary
 # information for each phenotype: 
 #
 # 1. The overall test average, 
 # 2. The average for the checks
-# 3. The rank of each genoype
-make_pheno_comparison <- function(test_data){
-  
-  keep_phenos <- c("yield", "protein", "oil", "protein_plus_oil")
+# 3. The rank of each genotype
[…]

### 2022-04-11 doc/manuscript/manuscript.tex
some small changes to the yield summary table function. Added a table to the utility tables list to convert summary table column names to more easily readible column names

@@
 The data for seed yield, seed oil, and seed protein contents were
-analyzed using a mixed model with the metan\citep{r_metan} R package.
+analyzed using a mixed model with the
+metan\citep{olivotoMetanPackageMultienvironment2020} R package.
 Environment, replication nested with environment, and the interaction of
@@
 
+\begin{table}
+\centering
+\begin{tabular}{l|r|r|l|l|l|r|r|l|l|l|r|r|l|l|l|r|r|l|l|l}
+\hline
+\multicolumn{1}{c|}{} & \multicolumn{5}{c|}{Protein + Oil} & \multicolumn{5}{c|}{Protein} & \multicolumn{5}{c|}{Yield} & \multicolumn{5}{c}{Oil} \\
+\cline{2-6} \cline{7-11} \cline{12-16} \cline{17-21}
+genotype & value & rank & test\_avg & check\_avg\_value & msd & value & rank & test\_avg & check\_avg\_value & msd & value & rank & test\_avg & check\_avg\_value & msd & value & rank & test\_avg & check\_avg\_value & msd\\
+\hline
+LMN09-119 & 69.44 & 1 &  &  &  & 51.67 & 1 &  &  &  & 40.82 & 17 &  &  &  & 17.77 & 20 &  &  & \\
+\cline{1-3}
+\cline{7-8}
+\cline{12-13}
+\cline{17-18}
+N18-1855 & 68.07 & 2 &  &  &  & 47.51 & 4 &  &  &  & 43.17 & 10 &  &  &  & 20.57 & 14 &  &  & \\
+\cline{1-3}
+\cline{7-8}
+\cline{12-13}
+\cline{17-18}
+N18-1632-1 & 67.49 & 3 &  &  &  & 46.81 & 5 &  &  &  & 45.73 & 6 &  &  &  & 20.67 & 11 &  &  & \\
+\cline{1-3}
+\cline{7-8}
+\cline{12-13}
+\cline{17-18}
+N18-1763 & 67.46 & 4 &  &  &  & 47.98 & 2 &  &  &  & 39.45 & 18 &  &  &  & 19.48 & 18 &  &  & \\
+\cline{1-3}
+\cline{7-8}
+\cline{12-13}
+\cline{17-18}
+N18-1632-2 & 67.41 & 5 &  &  &  & 46.79 & 6 &  &  &  & 46.34 & 5 &  &  &  & 20.62 & 12 &  &  & \\
+\cline{1-3}
+\cline{7-8}
+\cline{12-13}
+\cline{17-18}
+N18-1595 & 67.04 & 6 &  &  &  & 47.73 & 3 &  &  &  & 43.52 & 9 &  &  &  & 19.30 & 19 &  &  & \\
+\cline{1-3}
+\cline{7-8}
+\cline{12-13}
+\cline{17-18}
+N18-1731 & 66.66 & 7 &  &  &  & 46.27 & 8 &  &  &  & 43.16 & 11 &  &  &  & 20.40 & 15 &  &  & \\
+\cline{1-3}
+\cline{7-8}
+\cline{12-13}
+\cline{17-18}
+N18-1674 & 66.38 & 8 &  &  &  & 45.48 & 9 &  &  &  & 44.26 & 7 &  &  &  & 20.90 & 8 &  &  & \\
+\cline{1-3}
+\cline{7-8}
+\cline{12-13}
+\cline{17-18}
+N18-1572 & 66.26 & 9 &  &  &  & 45.38 & 10 &  &  &  & 38.58 & 19 &  &  &  & 20.88 & 9 &  &  & \\
+\cline{1-3}
+\cline{7-8}
+\cline{12-13}
+\cline{17-18}
+N09-09 & 66.26 & 10 &  &  &  & 46.74 & 7 &  &  &  & 41.63 & 14 &  &  &  & 19.52 & 17 &  &  & \\
+\cline{1-3}
+\cline{7-8}
+\cline{12-13}
+\cline{17-18}
+N18-1956 & 66.13 & 11 &  &  &  & 45.26 & 12 &  &  &  & 34.79 & 20 &  &  &  & 20.87 & 10 &  &  & \\
+\cline{1-3}
+\cline{7-8}
+\cline{12-13}
+\cline{17-18}
+N18-1682 & 65.87 & 12 &  &  &  & 45.27 & 11 &  &  &  & 43.64 & 8 &  &  &  & 20.60 & 13 &  &  & \\
+\cline{1-3}
+\cline{7-8}
+\cline{12-13}
+\cline{17-18}
+N18-1751 & 65.23 & 13 &  &  &  & 44.85 & 13 &  &  &  & 41.59 & 15 &  &  &  & 20.37 & 16 &  &  & \\
+\cline{1-3}
+\cline{7-8}
+\cline{12-13}
+\cline{17-18}
+N18-1635 & 65.22 & 14 &  &  &  & 43.79 & 16 &  &  &  & 46.45 & 4 &  &  &  & 21.42 & 3 &  &  & \\
+\cline{1-3}
+\cline{7-8}
+\cline{12-13}
+\cline{17-18}
+N18-1604 & 65.19 & 15 &  &  &  & 43.99 & 14 &  &  &  & 43.15 & 12 &  &  &  & 21.20 & 5 &  &  & \\
+\cline{1-3}
+\cline{7-8}
+\cline{12-13}
+\cline{17-18}
+N18-1620 & 65.15 & 16 &  &  &  & 43.98 & 15 &  &  &  & 46.54 & 3 &  &  &  & 21.17 & 6 &  &  & \\
+\cline{1-3}
+\cline{7-8}
+\cline{12-13}
+\cline{17-18}
+N18-1641 & 64.83 & 17 &  &  &  & 43.73 & 17 &  &  &  & 41.99 & 13 &  &  &  & 21.10 & 7 &  &  & \\
+\cline{1-3}
+\cline{7-8}
+\cline{12-13}
+\cline{17-18}
+Dilday & 63.54 & 18 &  &  &  & 41.40 & 19 &  &  &  & 46.78 & 2 &  &  &  & 22.15 & 2 &  &  & \\
+\cline{1-3}
+\cline{7-8}
+\cline{12-13}
+\cline{17-18}
+NC-Raleigh & 63.53 & 19 &  &  &  & 40.32 & 20 &  &  &  & 41.04 & 16 &  &  &  & 23.21 & 1 &  &  & \\
+\cline{1-3}
+\cline{7-8}
+\cline{12-13}
+\cline{17-18}
+Dunphy & 63.34 & 20 & \multirow{-20}{*}{\raggedright\arraybackslash 66.02} & \multirow{-20}{*}{\raggedright\arraybackslash 65.22} & \multirow{-20}{*}{\raggedright\arraybackslash 0.73} & 41.94 & 18 & \multirow{-20}{*}{\raggedright\arraybackslash 45.34} & \multirow{-20}{*}{\raggedright\arraybackslash 44.41} & \multirow{-20}{*}{\raggedright\arraybackslash 1.09} & 47.33 & 1 & \multirow{-20}{*}{\raggedright\arraybackslash 43} & \multirow{-20}{*}{\raggedright\arraybackslash 43.52} & \multirow{-20}{*}{\raggedright\arraybackslash 7.08} & 21.41 & 4 & \multirow{-20}{*}{\raggedright\arraybackslash 20.68} & \multirow{-20}{*}{\raggedright\arraybackslash 20.81} & \multirow{-20}{*}{\raggedright\arraybackslash 0.77}\\
+\hline
+\end{tabular}
+\end{table}
+
 % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-04-11 R/read_util_tables.R

@@ -5,18 +5,20 @@
 #' @title
 #' @param yield_check_genotypes
 #' @param genotype_conversion
-read_util_tables <- function(yield_check_genotypes, genotype_conversion, trait_conversion, trait_shortname_conversion) {
+read_util_tables <- function(yield_check_genotypes, genotype_conversion, trait_conversion, trait_shortname_conversion, column_shortname_conversion) {
 
   # Read in each file and return the dataframes in a list
   yield_checks        <- read_excel(yield_check_genotypes)
   genotype_conversion <- read_excel(genotype_conversion)
   trait_lookup        <- read_excel(trait_conversion)
   trait_shortnames    <- read_excel(trait_shortname_conversion)
+  column_shortnames   <- read_excel(column_shortname_conversion)
   
   res <- list("check_table"               = yield_checks, 
               "genotype_conversion_table" = genotype_conversion, 
               "trait_lookup"              = trait_lookup, 
-              "trait_shortnames"          = trait_shortnames)
+              "trait_shortnames"          = trait_shortnames, 
+              "column_shortnames"         = column_shortnames)
   
   return(res)
 }

### 2022-04-11 _targets.R

@@ -61,6 +61,12 @@ tar_plan(
              here("data", "utils", "trait_shortname_lookup.xlsx"), 
              format = "file"),
   
+  # A table to convert short column names in sumamry tables to longer, 
+  # more descriptive names
+  tar_target(column_shortname_conversion, 
+             here("data", "utils", "summary_column_names.xlsx"), 
+             format = "file"),
+  
   ## Section: Data cleaning
   ##################################################
   
@@ -69,7 +75,8 @@ tar_plan(
              read_util_tables(yield_check_genotypes, 
                               genotype_conversion, 
                               trait_conversion, 
-                              trait_shortname_conversion)),
+                              trait_shortname_conversion, 
+                              column_shortname_conversion)),
   
   # Cleaning up and merging the data from the three seasons
   tar_target(all_yield_data, 

### 2022-04-11 sandbox/yield summary tables.R

@@ -197,7 +197,8 @@ make_phenotype_comparison_table <- function(comparison_table_output, pheno_names
   # The indices of these columns
   collapse_indices <- map(collapse_cols, function(x) which(str_detect(colnames(current_table), x))) %>% 
     unlist() %>% 
-    unique()
+    unique() %>% 
+    sort()
   
   # Convert these columns to character variables
   current_table %<>% 
@@ -205,9 +206,11 @@ make_phenotype_comparison_table <- function(comparison_table_output, pheno_names
   
   colnames(current_table) <- remove_phenotype_names(colnames(current_table), pheno_names = pheno_names)
   
+  current_table <- as.data.frame(current_table)
+  
   knitr::kable(current_table, "html") %>% 
     kable_classic() %>% 
-    collapse_rows(columns = 4) %>%
+    collapse_rows(columns = collapse_indices) %>%
     add_header_above(column_groups)
   
 }

### 2022-04-20 doc/manuscript/manuscript.Rmd
some small changes to the yield summary table function. Added a table to the utility tables list to convert summary table column names to more easily readible column names
updated manuscript

--- 2022-04-01 doc/manuscript/manuscript.Rmd
@@
   - name: Jay Gillenwater
-    affil: 1,2,\ddagger,*
-    orcid: 0000-0003-3293-2315
-  - name: John Doe
-    affil: 2, \dagger, \ddagger
+    affil: 1,\ddagger,*
+    orcid: 0000-0002-3477-6291
 affiliation:
@@
     address: |
-      Muenster University of Applied Sciences - 
-      Institute for Infrastructure, Water, Resources, Environment
-      Correnstr. 25, 48149 Muenster, Germany
-    email: leutnant@fh-muenster.de
-  - num: 2
-    address: |
-      Your department
-      Street, City, Country
+      Department of Crop and Soil Sciences, NCSU, Raleigh, NC, USA
     email: jhgille2@ncsu.edu
@@
 keywords: |
-  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
-  to the article, yet reasonably common within the subject discipline.).
+  yield; protein; oil;soybean; protein meal
 acknowledgement: |
@@
 
-The introduction should briefly place the study in a broad context and highlight why it is important.
-It should define the purpose of the work and its significance.
-The current state of the research field should be reviewed carefully and key publications cited.
-Please highlight controversial and diverging hypotheses when necessary.
-Finally, briefly mention the main aim of the work and highlight the principal conclusions.
-As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
-Citing a journal paper [@bertrand-krajewski_distribution_1998; @leutnant_stormwater_2016].
-And now citing a book reference @gujer_systems_2008.
-Please use the command [@leutnant_stormwater_2016] for the following MDPI journals, which use author-date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences.
+Seed yield, oil, and protein are all valuable traits in a soybean variety, however breeding lines which have both high yield and protein has been difficult to develop due to the negative correlation between the two traits[@burton1987quantitative; @ProtOilCorr; @ProtOilCorr_new].
+While considerable efforts have been made to identify loci which control these seed quality traits so that MAS breeding strategies can be utilized for their improvement, to date the applications of such markers have been few.
+This is largely due to the lack of markers which are uniquely associated with one trait, and are also stable across genetic and environmental backgrounds.
+While there is still reason to continue this genetic research, it is important that breeders take every opportunity to identify lines with both high yield, and seed composition traits like oil and protein content so that new varieties can be released.
+
+Soybean lines typically contain about 20\% oil and 40\% protein content on a dry weight basis[@ProteinGenomics].
+The market for soybean meal requires 47.5\% protein content in the meal, which corresponds to approximately 41.5\% protein content on a dry weight basis[@ProteinGenomics].
+Oil and protein content are two of the most important seed composition traits in soybean so if one is decreased, the other should be correspondingly increased to account for the loss in value.
+The inverse correlation between protein and oil contents is well known and is suspected to be due at least partially to the action of pleiotropic genes and competing metabolic pathways which control the expression of each trait[@SeedCompositionGenomics].
+
+Despite the difficulty in simultaneously breeding for all three of these traits, releases of varieties with elevated protein contents and only moderately reduced yield has shown that it is not impossible.
+The high protein germplasm lines R05-1415 and R05-1772 were released recently and contain 46.9\% and 46.1\% protein content with while still producing yields 94\% and 91\% of that of the high yielding 5002T cultivar[@HiProtHiYield02].
+Lines TN03-350 and TN04-5321 contain 43.9\% and 43.1\% protein content while having superior or comparable performance to yield checks[@HiProtHiYield04].
+The Prolina cultivar has a protein content of 46.1\% with a yield only 13\% reduced from the Centennial check[@HiProtHiYield01].
+The Highpro1 cultivar was released in 2016 and has a yield which is greater than or equal to 97\% of that of the highest yielding check cultivar, IA3023 with a protein content of 40.1\%[@HighPro1].
+Cultivars produced through conventional breeding techniques such as these have shown that it is possible to identify lines with both high seed protein and seed yield.
+Efforts to find these lines should be continued to provide growers and breeders with additional high value cultivars, and germplasm which can be further used to improve protein and yield traits.
+
+To meet this goal, two recombinant inbred line (RIL) oil mapping populations were screened for lines which showed promising combinations of yield and seed composition traits.
+Successive rounds of selection were conducted to identify and characterize lines with high values for yield as well as protein and oil composition were performed between 2018 and 2021 to identify soybean lines with elevated yield as well as the valuable seed composition traits when compared with existing check cultivars.
 
@@
 ## Population development
-In 2018, oil mapping populations 201 and 202 were grown at the Central Crops Research Station in Clayton, NC.
+In 2018, oil mapping populations 201 and 202 were grown as plant rows at the Central Crops Research Station in Clayton, NC.
 These populations consisted of 273 and 237 recombinant inbred lines (RILs) respectively.
 Several agronomic traits were scored in the field for each population.
-These included height, lodging, maturity date, and a composite agronomic score.
-Lodging was scored on a scale of 1-5 where 5indicates that all plants in a plot are on the ground, and a score of 1 indicates that all plants are erect[Feh87].
+
+The agronomic traits recorded in the field were height, lodging, maturity date, and a composite agronomic score.
+Lodging was scored on a scale of 1-5 where 5 indicates that all plants in a plot are on the ground, and a score of 1 indicates that all plants are erect[@fehr1987soybeans].
 The agronomic score aimed to capture other traits of value such as visual estimation of pod load and plot uniformity to provide a general score of a line’s agronomic desirability.
-Agronomic score was recorded on a scale of 1-5 aswell, with 1 identifying the best lines of a population, and 5 the worst.
-Maturity was recorded at the R8 maturity date.
-Height was measured in centimeters from the soil to the top of the plant.
+Agronomic score was recorded on a scale of 1-5 as well, with 1 identifying the best lines of a population, and 5 the worst.
+Maturity was recorded at the R8 maturity date and was recorded as the number of days after September 1.
+Height was measured in inches from the soil to the top of the plant.
+
 Following harvest, yield, seed weight, protein, and oil content were measured after seed was air dried to approximately 7% moisture content in a greenhouse.
@@
 Yield and seed weight were measured after seed had been sifted and cleaned of debris and cracked seed.
+
 To select lines for the 2019 growing season, lines with abnormally low bulk weights or extreme maturity dates from 2018 were first removed from consideration.
 Two yield trials were then developed for each mapping population.
-The maturity data of RILs were considered when forming tests such that the lines of each test would have a maturity data range approximately half that of the total mapping population from which it was derived.
+The maturity dates of RILs were considered when forming tests such that the lines of each test would have a maturity date range approximately half that of the total mapping population from which it was derived.
 RILs were selected for each test which were also representative of the distribution of seed protein and seed oil traits for each population.
+
 Eighty unique lines were selected from each population which satisfied these criteria, and each yield test was comprised of 40 RILs.
 Three high-yielding check cultivars and the two parents of the respective population were also included in each test.
-Yield check cultivars Dunphy, Osage, and Roy were used in tests 1 and 2, while Dunphy, Dilday, and N.C.
-Raleigh were used for tests 3 and 4.
+Yield check cultivars Dunphy, Osage[@Osage], and Roy were used in tests 1 and 2, while Dunphy, Dilday, and NC-Raleigh[@NCRaleighregistration] were used for tests 3 and 4.
 These lines were selected to represent the estimated maturities of the RILs in each test.
@@
 The same data was collected for each test in this season that was collected in the previous season.
-Selections were done using this data by first identifying the lines with a yield within or above a least significant difference (LSD) of the average yield of the checks for each test.
-Further selection was done using the seed composition traits by identifying the thirty lines with the highest protein + oil content.
 
-These thirty lines were then grouped into two new tests of 15 RILs each which were then grown in both the 2020 and 2021 seasons. Thesew tests were grown in CLA and CAS in 2020 and CAS and PLY in 2021.
+Using the data collected from the 2019 season season, further selections were done to identify high-yielding lines from the four tests.
+This was done by identifying the RILs with a yield within or above a least significant difference (LSD) of the average yield of the checks for each test.
+Further selection was done using the seed composition traits by identifying the thirty RILs with the highest protein + oil content on a dry basis from among the RILs which had passed the yield selection threshold.
+
+These thirty lines were then grouped into two new tests of 15 RILs each based on maturity date.
+These two new tests are named Test 1 and Test 2.
+Yield check cultivars were again assigned to each test to match the maturity dates of the RILs that were in each test.
+Cultivars Dunphy, DIlday, and NC-Raleigh were used as checks in Test 1 and Dunphy, Ellis, N10-697, and Osage were used as checks in Test 2.
+
+These two tests were grown in both the 2020 and 2021 seasons.
+These tests were grown in CLA and CAS in 2020 and CAS and PLY in 2021.
+The same phenotypes were evaluated for each genotype in the 2020 and 2021 seasons using the same methodology that was employed in the 2019 season.
+
+## Statistical Analysis
+Phenotypic traits were analysed with a linear model with the form:
+
+$$y_{ijk} = \mu + L_i + B(L_i) + G_k + GL_{ik} + \epsilon_{ijk}$$
+
+Where $y_{ijk}$ is the phenotypic measurement for rep$j$ of genotype $k$ in environment $i$, $L_i$ is the effect of location $i$, $G_k$ is the effect of genotype $G$, $GL_{ik}$ is the interaction effect of location $L$ and genotype $G$, and $\epsilon_{ijk}$ is the measurement error.
+
+Models were fit using the lm function in R[@rcoreteamLanguageEnvironmentStatistical2022], and analysis of variance (ANOVA) performed using the anova function.
+Least-square means (LS Means) for each genotype and trait were calculated using the above model using the emmeans package[@lenthEmmeansEstimatedMarginal2022] in R.
+Least-significant difference values for each trait were calculated using the LSD.test function from the agricolae[@de2014agricolae] package.
+Pearson correlation coefficients between each phenotype were calculated with the cor function in R.
+
+Pearson correlation is calculated for each pair of traits as:
+
+$$r = \frac{\sum{(x-m_x)(y-m_y)}}{\sqrt{\sum{(x-m_x)^2}\sum{(y-m_y)^2}}}$$
+
+Where $x$ and $y$ are measurements of the two phenotypes, $m_x$ and $m_y$ are the means of each phenotype, and $r$ is the correlation coefficient.
 

### 2022-04-20 doc/manuscript/manuscript.tex
updated manuscript

--- 2022-04-01 doc/manuscript/manuscript.tex
@@
 \Author{Jay
-Gillenwater$^{1,2,\ddagger,*}$\href{https://orcid.org/0000-0003-3293-2315}{\orcidicon}, John
-Doe$^{2, \dagger, \ddagger}$}
+Gillenwater$^{1,\ddagger,*}$\href{https://orcid.org/0000-0002-3477-6291}{\orcidicon}}
 
 % Authors, for metadata in PDF
-\AuthorNames{Jay Gillenwater, John Doe}
+\AuthorNames{Jay Gillenwater}
 
@@
 \address{%
-$^{1}$ \quad Muenster University of Applied Sciences - Institute for
-Infrastructure, Water, Resources, Environment Correnstr. 25, 48149
-Muenster,
-Germany; \href{mailto:leutnant@fh-muenster.de}{\nolinkurl{leutnant@fh-muenster.de}}\\
-$^{2}$ \quad Your department Street, City,
-Country; \href{mailto:jhgille2@ncsu.edu}{\nolinkurl{jhgille2@ncsu.edu}}\\
+$^{1}$ \quad Department of Crop and Soil Sciences, NCSU, Raleigh, NC,
+USA; \href{mailto:jhgille2@ncsu.edu}{\nolinkurl{jhgille2@ncsu.edu}}\\
 }
@@
 % Keywords
-\keyword{keyword 1; keyword 2; keyword 3 (list three to ten pertinent
-keywords specific to the article, yet reasonably common within the
-subject discipline.).}
+\keyword{yield; protein; oil;soybean; protein meal}
 
@@
 
-The introduction should briefly place the study in a broad context and
-highlight why it is important. It should define the purpose of the work
-and its significance. The current state of the research field should be
-reviewed carefully and key publications cited. Please highlight
-controversial and diverging hypotheses when necessary. Finally, briefly
-mention the main aim of the work and highlight the principal
-conclusions. As far as possible, please keep the introduction
-comprehensible to scientists outside your particular field of research.
-Citing a journal paper
-\citep{bertrand-krajewski_distribution_1998, leutnant_stormwater_2016}.
-And now citing a book reference \citet{gujer_systems_2008}. Please use
-the command \citep{leutnant_stormwater_2016} for the following MDPI
-journals, which use author-date citation: Administrative Sciences, Arts,
-Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws,
-Religions, Risks, Social Sciences.
+Seed yield, oil, and protein are all valuable traits in a soybean
+variety, however breeding lines which have both high yield and protein
+has been difficult to develop due to the negative correlation between
+the two
+traits\citep{burton1987quantitative, ProtOilCorr, ProtOilCorr_new}.
+While considerable efforts have been made to identify loci which control
+these seed quality traits so that MAS breeding strategies can be
+utilized for their improvement, to date the applications of such markers
+have been few. This is largely due to the lack of markers which are
+uniquely associated with one trait, and are also stable across genetic
+and environmental backgrounds. While there is still reason to continue
+this genetic research, it is important that breeders take every
+opportunity to identify lines with both high yield, and seed composition
+traits like oil and protein content so that new varieties can be
+released.
+
+Soybean lines typically contain about 20\% oil and 40\% protein content
+on a dry weight basis\citep{ProteinGenomics}. The market for soybean
+meal requires 47.5\% protein content in the meal, which corresponds to
+approximately 41.5\% protein content on a dry weight
+basis\citep{ProteinGenomics}. Oil and protein content are two of the
+most important seed composition traits in soybean so if one is
+decreased, the other should be correspondingly increased to account for
+the loss in value. The inverse correlation between protein and oil
+contents is well known and is suspected to be due at least partially to
+the action of pleiotropic genes and competing metabolic pathways which
+control the expression of each trait\citep{SeedCompositionGenomics}.
+
+Despite the difficulty in simultaneously breeding for all three of these
+traits, releases of varieties with elevated protein contents and only
+moderately reduced yield has shown that it is not impossible. The high
+protein germplasm lines R05-1415 and R05-1772 were released recently and
+contain 46.9\% and 46.1\% protein content with while still producing
+yields 94\% and 91\% of that of the high yielding 5002T
+cultivar\citep{HiProtHiYield02}. Lines TN03-350 and TN04-5321 contain
+43.9\% and 43.1\% protein content while having superior or comparable
+performance to yield checks\citep{HiProtHiYield04}. The Prolina cultivar
+has a protein content of 46.1\% with a yield only 13\% reduced from the
+Centennial check\citep{HiProtHiYield01}. The Highpro1 cultivar was
+released in 2016 and has a yield which is greater than or equal to 97\%
+of that of the highest yielding check cultivar, IA3023 with a protein
+content of 40.1\%\citep{HighPro1}. Cultivars produced through
+conventional breeding techniques such as these have shown that it is
+possible to identify lines with both high seed protein and seed yield.
+Efforts to find these lines should be continued to provide growers and
+breeders with additional high value cultivars, and germplasm which can
+be further used to improve protein and yield traits.
+
+To meet this goal, two recombinant inbred line (RIL) oil mapping
+populations were screened for lines which showed promising combinations
+of yield and seed composition traits. Successive rounds of selection
+were conducted to identify and characterize lines with high values for
+yield as well as protein and oil composition were performed between 2018
+and 2021 to identify soybean lines with elevated yield as well as the
+valuable seed composition traits when compared with existing check
+cultivars.
 
@@
 
-In 2018, oil mapping populations 201 and 202 were grown at the Central
-Crops Research Station in Clayton, NC. These populations consisted of
-273 and 237 recombinant inbred lines (RILs) respectively. Several
-agronomic traits were scored in the field for each population. These
-included height, lodging, maturity date, and a composite agronomic
-score. Lodging was scored on a scale of 1-5 where 5indicates that all
-plants in a plot are on the ground, and a score of 1 indicates that all
-plants are erect{[}Feh87{]}. The agronomic score aimed to capture other
-traits of value such as visual estimation of pod load and plot
+In 2018, oil mapping populations 201 and 202 were grown as plant rows at
+the Central Crops Research Station in Clayton, NC. These populations
+consisted of 273 and 237 recombinant inbred lines (RILs) respectively.
+Several agronomic traits were scored in the field for each population.
+
+The agronomic traits recorded in the field were height, lodging,
+maturity date, and a composite agronomic score. Lodging was scored on a
+scale of 1-5 where 5 indicates that all plants in a plot are on the
+ground, and a score of 1 indicates that all plants are
+erect\citep{fehr1987soybeans}. The agronomic score aimed to capture
+other traits of value such as visual estimation of pod load and plot
 uniformity to provide a general score of a line's agronomic
-desirability. Agronomic score was recorded on a scale of 1-5 aswell,
+desirability. Agronomic score was recorded on a scale of 1-5 as well,
 with 1 identifying the best lines of a population, and 5 the worst.
-Maturity was recorded at the R8 maturity date. Height was measured in
-centimeters from the soil to the top of the plant. Following harvest,
-yield, seed weight, protein, and oil content were measured after seed
-was air dried to approximately 7\% moisture content in a greenhouse.
-Protein and oil contents were measured on a dry basis using a Perten DA
-7250 NIR®instrument. Yield and seed weight were measured after seed had
-been sifted and cleaned of debris and cracked seed. To select lines for
-the 2019 growing season, lines with abnormally low bulk weights or
-extreme maturity dates from 2018 were first removed from consideration.
-Two yield trials were then developed for each mapping population. The
-maturity data of RILs were considered when forming tests such that the
-lines of each test would have a maturity data range approximately half
-that of the total mapping population from which it was derived. RILs
-were selected for each test which were also representative of the
-distribution of seed protein and seed oil traits for each population.
+Maturity was recorded at the R8 maturity date and was recorded as the
+number of days after September 1. Height was measured in inches from the
+soil to the top of the plant.
+
+Following harvest, yield, seed weight, protein, and oil content were
+measured after seed was air dried to approximately 7\% moisture content
+in a greenhouse. Protein and oil contents were measured on a dry basis
+using a Perten DA 7250 NIR®instrument. Yield and seed weight were
+measured after seed had been sifted and cleaned of debris and cracked
+seed.
+
+To select lines for the 2019 growing season, lines with abnormally low
+bulk weights or extreme maturity dates from 2018 were first removed from
+consideration. Two yield trials were then developed for each mapping
+population. The maturity dates of RILs were considered when forming
+tests such that the lines of each test would have a maturity date range
+approximately half that of the total mapping population from which it
+was derived. RILs were selected for each test which were also
+representative of the distribution of seed protein and seed oil traits
+for each population.
+
 Eighty unique lines were selected from each population which satisfied
@@
 population were also included in each test. Yield check cultivars
-Dunphy, Osage, and Roy were used in tests 1 and 2, while Dunphy, Dilday,
-and N.C. Raleigh were used for tests 3 and 4. These lines were selected
-to represent the estimated maturities of the RILs in each test. The
-parents for tests 1 and 2 were cultivars LMN09-119 and N09-09, and the
-parents for tests 3 and 4 were LMN09-19 and N13-47.
+Dunphy, Osage\citep{Osage}, and Roy were used in tests 1 and 2, while
+Dunphy, Dilday, and N.C. Raleigh were used for tests 3 and 4. These
+lines were selected to represent the estimated maturities of the RILs in
+each test. The parents for tests 1 and 2 were cultivars LMN09-119 and
+N09-09, and the parents for tests 3 and 4 were LMN09-19 and N13-47.
 
@@
 Kinston, NC (CAS). The same data was collected for each test in this
-season that was collected in the previous season. Selections were done
-using this data by first identifying the lines with a yield within or
-above a least significant difference (LSD) of the average yield of the
-checks for each test. Further selection was done using the seed
-composition traits by identifying the thirty lines with the highest
-protein + oil content.
+season that was collected in the previous season.
+
+Using the data follected from this season, further selections were done
+to identify high-yielding lines from the four tests. This was done by
+identifying the RILs with a yield within or above a least significant
+difference (LSD) of the average yield of the checks for each test.
+Further selection was done using the seed composition traits by
+identifying the thirty RILs with the highest protein + oil content on a
+dry basis from among the RILs which had passed the yield selection
+threshold.
 
 These thirty lines were then grouped into two new tests of 15 RILs each
-which were then grown in both the 2020 and 2021 seasons. Thesew tests
-were grown in CLA and CAS in 2020 and CAS and PLY in 2021.
+on the basis of maturity date. These two new tests are named Test 1 and
+Test 2. Yield check cultivars were again assigned to each test to match
+the maturity dates of the RILs that were in each test. Cultivars Dunphy,
+DIlday, and NC-Raleigh were used as checks in Test 1 and Dunphy, Ellis,
+N10-697, and Osage were used as checks in Test 2.
+
+These two tests were grown in both the 2020 and 2021 seasons. These
+tests were grown in CLA and CAS in 2020 and CAS and PLY in 2021. The
+same phenotypes were evaluated for each genotype in the 2020 and 2021
+seasons using the same methodology that was employed in the 2019 season.
+
+\hypertarget{statistical-analysis}{%
+\subsection{Statistical Analysis}\label{statistical-analysis}}
+
+Phenotypic traits were analysed with a linear model with the form:
+
+\[y_{ijk} = \mu + L_i + B(L_i) + G_k + GL_{ik} + \epsilon_{ijk}\]
+
+Where \(y_{ijk}\) is the phenotypic measurement for rep\(j\) of genotype
+\(k\) in environment \(i\), \(L_i\) is the effect of location \(i\),
+\(G_k\) is the effect of genotype \(G\), \(GL_{ik}\) is the interaction
+effect of location \(L\) and genotype \(G\), and \(\epsilon_{ijk}\) is
+the measurement error.
+
+Models were fit using the lm function in
+R\citep{rcoreteamLanguageEnvironmentStatistical2022}, and analysis of
+variance (ANOVA) performed using the anova function. Least-square means
+(LS Means) for each genotype and trait were calculated using the above
+model using the emmeans package\citep{lenthEmmeansEstimatedMarginal2022}
+in R. Least-significant difference values for each trait were calculated
+using the LSD.test function from the agricolae\citep{de2014agricolae}
+package. Pearson correlation coefficients between each phenotype were
+calculated with the cor function in R.
+
+Pearson correlation is calculated for each pair of traits as:
+
+\[r = \frac{\sum{(x-m_x)(y-m_y)}}{\sqrt{\sum{(x-m_x)^2}\sum{(y-m_y)^2}}}\]
+
+Where \(x\) and \(y\) are measurements of the two phenotypes, \(m_x\)
+and \(m_y\) are the means of each phenotype, and \(r\) is the
+correlation coefficient.
 

### 2022-04-20 R/get_lsd_values.R
stuff

@@ -26,30 +26,30 @@ get_lsd_values <- function(df = all_yield_data$two_year) {
     # the data is perfectly balanced (as all things should be) and these genotypes
     # were included multiple times in the tests.
     clean_data <- function(pheno_data){
-      
+
       pheno_data %<>%
         dplyr::filter(!is.na(value), !genotype %in% c("LMN09-119", "N09-09"))
-      
+
       genotype_reps <- pheno_data %>%
-        group_by(genotype) %>% 
+        group_by(genotype) %>%
         count(name = "num_reps")
-      
-      rep_counts <- genotype_reps %>% 
-        group_by(num_reps) %>% 
+
+      rep_counts <- genotype_reps %>%
+        group_by(num_reps) %>%
         count(name = "rep_count")
-      
+
       max_rep_count <- rep_counts$num_reps[[which(rep_counts$rep_count == max(rep_counts$rep_count))]]
-      
+
       keep_genos <- genotype_reps %>%
         dplyr::filter(num_reps == max_rep_count)
-      
+
       keep_genos <- as.character(keep_genos$genotype)
-      
-      pheno_data %<>% 
+
+      pheno_data %<>%
         dplyr::filter(genotype %in% keep_genos)
-      
+
       return(pheno_data)
-      
+
     }
     
     # Pivot the data by these phenotypes and then nest by each phenotype
@@ -57,8 +57,12 @@ get_lsd_values <- function(df = all_yield_data$two_year) {
       pivot_longer(cols = all_of(measure_vars), names_to = "trait") %>%
       group_by(trait) %>% 
       nest() %>% 
-      ungroup() %>%
+      ungroup()  %>%
       mutate(data = map(data, clean_data))
+    
+    # I took this part out to test using the HSD test function with the unbalanced
+    # data
+    #
     
     model_fn <- function(pheno_data) {
       
@@ -68,12 +72,22 @@ get_lsd_values <- function(df = all_yield_data$two_year) {
       model_aov <- aov(model)
       trait_lsd <- agricolae::LSD.test(model_aov, 
                                        trt   = "genotype", 
-                                       p.adj = "bonferroni")
+                                       p.adj = "none")
+      
+      trait_hsd <- agricolae::HSD.test(model_aov, 
+                                       trt = "genotype")
+      
+      trait_hsd_metan <- metan::tukey_hsd(model_aov, 
+                                          which = "genotype")
+      
+      trait_hsd_stats <- TukeyHSD(model_aov, 
[…]

### 2022-04-20 R/make_emmean_table.R

@@ -1,0 +1,32 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param test_anova_list
+#' @param test_name
+make_emmean_table <- function(test_anova_list, test_name) {
+  
+  # Pull just the joint anova results
+  test_anova_list <- pluck(test_anova_list, "joint")
+  
+  # Each element if both_anova is a list of phenotype ANOVAs
+  # I want a function to extract the marginal means from the 
+  # phenotype
+  extract_emmeans <- function(pheno_anova, pheno_name){
+    pheno_anova %>% 
+      pluck("model") %>% 
+      emmeans("GEN") %>%
+      as_tibble() %>%
+      select(GEN, emmean) %>% 
+      set_names(c("genotype", pheno_name))
+  }
+  
+  all_emmeans <- map2(test_anova_list, names(test_anova_list), extract_emmeans) %>% 
+    reduce(left_join) %>% 
+    mutate(test_name = test_name) %>% 
+    relocate(test_name, 1) %>% 
+    arrange(desc(yield))
+  
+  return(all_emmeans)
+}

### 2022-04-20 R/make_genotype_blue_plots.R

@@ -4,8 +4,30 @@
 #'
 #' @title
 #' @param fit_models
-make_genotype_blue_plots <- function(fit_models = mixed_models_two_years) {
+make_genotype_blue_plots <- function(fit_models = mixed_models_two_years, all_data = all_yield_data$two_year) {
 
-  NULL
-
+  
+  # A function to relevel the environment factor variable in the yield data
+  # so that it is ordered by year and so that 
+  reorder_environment <- function(yield_df){
+    yield_df %>% 
+      mutate(ENV = fct_relevel(ENV, 'CLA - 2020', 'CAS - 2020', 'CAS - 2021', 'PLY - 2021'), 
+             genotype = fct_reorder(genotype, yield, .fun = mean, na.rm = TRUE)) %>% 
+      rename(Genotype = genotype, 
+             Environment = ENV, 
+             Yield = yield)
+  }
+  
+  all_data <- map(all_data, reorder_environment)
+  
+  # A genotype by environment plot for yield
+  test_1_yield <- ge_plot(pluck(all_data, "Jay Test 1"), env = Environment, gen = Genotype, resp = Yield)
+  test_2_yield <- ge_plot(pluck(all_data, "Jay Test 2"), env = Environment, gen = Genotype, resp = Yield)
+  
+  both_test_plots <- arrange_ggplot(test_1_yield, test_2_yield, 
+                                    tag_levels = list(c("Test 1", "Test 2")))
+  
+  res <- list("ge_plot" = both_test_plots)
+  
+  return(res)
 }

### 2022-04-20 _targets.R

@@ -119,13 +119,17 @@ tar_plan(
   ## Section: Analysis summaries
   ##################################################
   
+  # Marginal means derived from linear models
+  tar_target(linear_means, 
+             map2(anova_two_years, names(anova_two_years), make_emmean_table)),
+  
   # A table of genotype BLUPs for each trait/test
   tar_target(genotype_BLUEs, 
              make_blue_table(fit_models = mixed_models_two_years)),
   
   # Plots of the genotype blues
   tar_target(BLUE_plots_two_years, 
-             make_genotype_blue_plots(fit_models = mixed_models_two_years)),
+             make_genotype_blue_plots(fit_models = mixed_models_two_years, all_data = all_yield_data$two_year)),
   
 # A example latex table to use for testing targets with the manuscript template
   tar_target(example_table, 

### 2022-04-20 packages.R

@@ -19,7 +19,7 @@ pacman::p_load(tidyverse,
                magrittr,
                openxlsx)
 
-# Visualization
+# VC:\Users\jhgille2\Documents\SAS\field trial analysis macros\04142022HIF6CASPLYPRG.sasisualization
 pacman::p_load(ggthemes, 
                lattice,
                visNetwork,
@@ -27,7 +27,8 @@ pacman::p_load(ggthemes,
                ggcorrplot, 
                patchwork,
                extrafont, 
-               GGally)
+               GGally, 
+               scales)
 
 # Analysis
 pacman::p_load(metan,

### 2022-04-20 sandbox/histogram development.R

@@ -38,33 +38,33 @@ convert_from_table(all_yield, "genotype", util_tables$genotype_conversion_table)
 tar_load(genotype_BLUEs)
 
 # A function to make a labelled histogram
-<<<<<<< HEAD
 labelled_histogram <- function(blue_data, test_colors, trait_name, check_genotypes, trait_name_lookup, label_genotypes = NULL){
-=======
-labelled_histogram <- function(blue_data, test_colors, trait_name, check_genotypes, trait_name_lookup, label_genotypes){
->>>>>>> b2ac9991b18b7dda610fba75c40b9e8b3e7fd0ff
   
   # Use the lookup table to convert the trait name to its fancy counterpart
   fancy_trait_name <- match_from_table(trait_name, trait_name_lookup)
-  test_name <- "test_name"
-  
-  # The initial plot (need bin heights)
-  Plot.init <- ggplot(blue_data, aes_string(x = trait_name, fill = test_name)) + 
-    geom_histogram(bins = 9, col = 'black') + 
-    theme_calc() + 
-    theme(axis.text = element_text(size = 20, face = 'bold'),
-          axis.title = element_text(size = 30)) + 
-    ylab("Count") + 
-    xlab(fancy_trait_name)
-  
-  # + 
-  #   geom_vline(xintercept = CheckAvg, linetype = 'dotted', colour = 'black', size = 1.25) + 
-  #   geom_vline(xintercept = LSDLine, linetype = 2, colour = 'red', size = 1.25)
+  test_name        <- "test_name"
   
   # Get data for the parents/checks
   CheckParents <- blue_data %>% dplyr::filter(genotype %in% c(check_genotypes$genotype, label_genotypes))
   CheckParents <- CheckParents[, c("genotype", trait_name)]
   colnames(CheckParents) <- c("genotype", "value")  
+  
+  CheckAvg <- mean(CheckParents$value, na.rm = TRUE)
+  TestAvg  <- mean(unlist(blue_data[, trait_name]), na.rm = TRUE)
+  
+  # The initial plot (need bin heights).
+  # Add a black dotted line for check average, a red dashed line for the test average
+  Plot.init <- ggplot(blue_data, aes_string(x = trait_name, fill = test_name)) + 
+    geom_histogram(bins = 9, col = 'black') + 
+    theme_calc() + 
+    theme(axis.text  = element_text(size = 20, face = 'bold'),
[…]

### 2022-04-20 sandbox/yield summary tables.R

@@ -11,11 +11,12 @@
 tar_load(genotype_BLUEs)
 tar_load(util_tables)
 tar_load(least_sig_differences)
+tar_load(linear_means)
 
 # A function to get the minimum significant difference from the lsd results list
 get_msd <- function(fit_model){
   msd <- fit_model %>% 
-    pluck("lsd") %>% 
+    pluck("hsd") %>% 
     pluck("statistics") %>% 
     pluck("MSD")
   
@@ -99,7 +100,7 @@ full_comparison_table <- function(blue_data, lsd_data, keep_phenos = c("yield", 
   # a summary table for each test
   test_comparisons <- map(blue_data, make_pheno_comparison, keep_phenos = keep_phenos)
   
-  # Now join each summary table to the correspnding MSD table for each test
+  # Now join each summary table to the corresponding MSD table for each test
   # and then pivot to a wide format using the phenotypes to name columns
   # and all the columns that have been added to fill the values
   full_comparisons <- map2(test_comparisons, just_msd, function(x, y) left_join(x, y, by = c("pheno" = "trait")) %>% 
@@ -117,8 +118,29 @@ full_comparison_table <- function(blue_data, lsd_data, keep_phenos = c("yield", 
   return(res)
 }
 
+# The same function from above, but keep the dat ain a long format
+# that is more helpful for plotting and other data management
+full_comparison_long <- function(blue_data, lsd_data, keep_phenos = c("yield", "protein", "oil", "protein_plus_oil")){
+  
+  # Get just the MSD from the msd dataframe
+  just_msd <- lsd_data %>% 
+    map(., function(x) mutate(x, msd = map_dbl(fit_model, get_msd)) %>%
+          select(trait, msd))
+  
+  # Apply the phenotype comparison function to the BLUE data to make 
+  # a summary table for each test
+  test_comparisons <- map(blue_data, make_pheno_comparison, keep_phenos = keep_phenos)
+  
+  # Now join each summary table to the corresponding MSD table for each test
+  # and then pivot to a wide format using the phenotypes to name columns
+  # and all the columns that have been added to fill the values
+  full_comparisons <- map2(test_comparisons, just_msd, function(x, y) left_join(x, y, by = c("pheno" = "trait")))
+  
+  return(full_comparisons)
+}
+
 # Testing the functions together
-comparison_tables <- full_comparison_table(blue_data = genotype_BLUEs$BLUEs, least_sig_differences)
[…]

### 2022-04-25 doc/manuscript/manuscript.tex
Added a short summary document and a flochart for use in the summary document

@@
 Dunphy, Osage\citep{Osage}, and Roy were used in tests 1 and 2, while
-Dunphy, Dilday, and N.C. Raleigh were used for tests 3 and 4. These
-lines were selected to represent the estimated maturities of the RILs in
-each test. The parents for tests 1 and 2 were cultivars LMN09-119 and
-N09-09, and the parents for tests 3 and 4 were LMN09-19 and N13-47.
+Dunphy, Dilday, and NC-Raleigh\citep{NCRaleighregistration} were used
+for tests 3 and 4. These lines were selected to represent the estimated
+maturities of the RILs in each test. The parents for tests 1 and 2 were
+cultivars LMN09-119 and N09-09, and the parents for tests 3 and 4 were
+LMN09-19 and N13-47.
 
@@
 
-Using the data follected from this season, further selections were done
-to identify high-yielding lines from the four tests. This was done by
-identifying the RILs with a yield within or above a least significant
-difference (LSD) of the average yield of the checks for each test.
-Further selection was done using the seed composition traits by
+Using the data collected from the 2019 season season, further selections
+were done to identify high-yielding lines from the four tests. This was
+done by identifying the RILs with a yield within or above a least
+significant difference (LSD) of the average yield of the checks for each
+test. Further selection was done using the seed composition traits by
 identifying the thirty RILs with the highest protein + oil content on a
@@
 These thirty lines were then grouped into two new tests of 15 RILs each
-on the basis of maturity date. These two new tests are named Test 1 and
-Test 2. Yield check cultivars were again assigned to each test to match
-the maturity dates of the RILs that were in each test. Cultivars Dunphy,
+based on maturity date. These two new tests are named Test 1 and Test 2.
+Yield check cultivars were again assigned to each test to match the
+maturity dates of the RILs that were in each test. Cultivars Dunphy,
 DIlday, and NC-Raleigh were used as checks in Test 1 and Dunphy, Ellis,

### 2022-04-25 doc/overview_document.Rmd
Added a short summary document and a flochart for use in the summary document

---
title: "Untitled Draft"
author: "Report Author"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
## target knits Rmds in their own session, so load libraries here.
## source("here::here(packages.R"))
```

```{r load-targets, include=FALSE}
# tar_load(c(target_1, target_2, target_3))

# # If your chunk output is shown in-line, then you'll need to wrap tar_load()
# # like so:
# 
# withr::with_dir(here::here(), {
#   tar_load(c(target_1, target_2, target_3))
# })
# 
# # This is not needed when using tar_make() to render the document.
```
## Introduction
This document is a high-level overview of the experimental design and objectives of the "Jay" yield tests.

## Objectives
The overall objective of this experiment is to identify recombinant inbred lines (RILs) that have yield and agronomic qualities comparable to existing check cultivars, and have a protein + oil content that is greater than the check cultivars.

## Experimental design
The experiment consists of two tests, names test 1 and test 2, that are comprised of 15 RILs, and 5 check cultivars. These two tests were grown in a RCBD in 2020 and 2021, in two locations for each year. In 2020, each test was grown at the Clayton (CLA) and Caswell (CAS) research stations, while in 2021 each test was grown at the Plymouth (PLY) research station and CAS. Each test was grown in four replications within each location for both years.

## Population development
The RILs used in these two tests come from two mapping populations that were initially grown as plant rows in 2018 at CLA. We noticed some of the lines in these two populations had some good combinations of agronomic qualities, and seed composition traits and this is how we first got the idea to more rigorously evaluate the yield performance potential of a selection of the lines from these two populations. These two populations were too large to test every line so we first made some selections to identify 80 lines from each population that would be tested for yield performance. Briefly, this selection scheme first removed any lines from consideration that had poor lodging, seed load, or bulk weight, and any lines with extreme maturity dates. Lines were then selected so that the entire distribution of protein and oil content of the starting mapping populations would be represented in the selection. The 80 lines for each population were then split into two tests of 40 RILs based on maturity date. Three check cultivars and the mapping population parents were then included in the tests as well for a final set of four tests with 45 lines each.

These four tests were grown in PLY and CAS in 2019. Agronomic notes including lodging, height, maturity date, and an agronomic score based on overall appearance were taken in the field and yield, seed weight, protein, and oil content were measured after harvesting.

After this data was collected, another round of selection was done that focused on the observed yield performance of the lines. Only lines that were within, or above a least significant difference of the average of the checks for each test were considered for advancement. Then, the thirty lines with the highest protein + oil content across all four tests were identified from among

## Analysis

## Reproducibility

<details><summary>Reproducibility receipt</summary>

```{r}
## datetime
Sys.time()

## repository
if(requireNamespace('git2r', quietly = TRUE)) {
  git2r::repository()
} else {
  c(
    system2("git", args = c("log", "--name-status", "-1"), stdout = TRUE),
    system2("git", args = c("remote", "-v"), stdout = TRUE)
  )
}

## session info
sessionInfo()
```

</details>

### 2022-04-25 R/read_plant_row_data.R

@@ -1,0 +1,20 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param plant_rows_2019_file
+read_plant_row_data <- function(plant_rows_2019_file) {
+
+  # Read in the data from each population
+  pop_201 <- read_excel(plant_rows_2019_file, sheet = "Pop201")
+  pop_202 <- read_excel(plant_rows_2019_file, sheet = "Pop202")
+  
+  # Combine the two data sets into one, clean up them names, 
+  # and rename a clumsy column name
+  both_pops <- bind_rows(pop_201, pop_202) %>% 
+    clean_names() %>% 
+    rename(sdwt = x100_seed_weight)
+  
+  return(both_pops)
+}

### 2022-04-25 _targets.R

@@ -10,6 +10,11 @@ tar_plan(
   ## Section: Input files
   ##################################################
   
+  # All plant row data collected from the  2018 MPs
+  tar_target(plant_rows_2019_file, 
+             here("data", "season_2019", "OilMPYieldSelections2019.xlsx"), 
+             format = "file"),
+  
   # Yield data from 2019
   tar_target(yield_2019_file, 
              here("data", "season_2019", "YieldData_2019.xlsx"), 
@@ -77,6 +82,10 @@ tar_plan(
                               trait_conversion, 
                               trait_shortname_conversion, 
                               column_shortname_conversion)),
+  
+  # Read in and clean up the plant row data from 2019
+  tar_target(plant_row_data, 
+             read_plant_row_data(plant_rows_2019_file)),
   
   # Cleaning up and merging the data from the three seasons
   tar_target(all_yield_data, 
@@ -148,6 +157,8 @@ tar_plan(
   ## Section: Writeup documents
   ##################################################
   tar_render(analysis_writeup, "doc/analysis_writeup.Rmd"), 
+
+  tar_render(overview_document, "doc/overview_document.Rmd")
   
   tar_render(manuscript_document, here("doc", "manuscript", "manuscript.Rmd"))
   

### 2022-04-25 packages.R

@@ -46,3 +46,4 @@ pacman::p_load(rmdformats,
 # Function conflict preferences
 conflicted::conflict_prefer("filter", "dplyr", "base")
 
+library(rmarkdown)

### 2022-04-25 sandbox/plant row data cleaning.R

@@ -1,0 +1,20 @@
+##################################################
+## Project: Jay Yield
+## Script purpose: Development of the function to clean up the plant
+## row data from 2018
+## Date: 2022-04-25
+## Author: Jay Gillenwater
+##################################################
+
+tar_load(plant_rows_2019_file)
+
+excel_sheets(plant_rows_2019_file)
+
+
+# Read in the data from each population
+pop_201 <- read_excel(plant_rows_2019_file, sheet = "Pop201")
+pop_202 <- read_excel(plant_rows_2019_file, sheet = "Pop202")
+
+both_pops <- bind_rows(pop_201, pop_202) %>% 
+  clean_names() %>% 
+  rename(sdwt = x100_seed_weight)

### 2022-04-25 sandbox/selection plots development.R

@@ -1,0 +1,56 @@
+##################################################
+## Project: Jay Yield
+## Script purpose: Making boxplots to show how maturity date was used to assign 
+## genotypes to tests
+## Date: 2022-04-25
+## Author: Jay Gillenwater
+##################################################
+
+# Load in the required data
+tar_load(c(plant_row_data, all_yield_data))
+
+plant_row_data %<>%
+  rename(genotype = row) %>% 
+  mutate(test = population)
+
+# Merge the data from 2019 into one dataframe and then just get the 
+# table of genotypes that were in each test
+selected_genotypes_2019 <- all_yield_data %>%
+  pluck("all") %>% 
+  reduce(bind_rows) %>% 
+  dplyr::filter(year == "2019") %>% 
+  select(test, genotype) %>% 
+  distinct() %>% 
+  split_factors(test, keep_factors = TRUE) %>% 
+  map(., function(x) left_join(x, plant_row_data, by = "genotype")) %>% 
+  reduce(bind_rows) %>% 
+  select(-test.y) %>% 
+  rename(test = test.x) %>%
+  dplyr::filter(!is.na(md)) %>% 
+  bind_rows(plant_row_data) %>%
+  mutate(p_o = protein_dry_basis + oil_dry_basis) %>%
+  select(test, genotype, population, md, ht, sdwt, bulk_weight, oil_dry_basis, protein_dry_basis, p_o) %>%
+  split_factors(population, keep_factors = TRUE)
+
+# The data for one of the population to test plotting functions
+pop_201_data <- selected_genotypes_2019$`Oil Mapping Pop 201`
+
+md_plot <- ggplot(pop_201_data, aes(x = test, y = md, fill = test)) + 
+  geom_boxplot(color = "black") + 
+  coord_flip() + 
+  theme_few() + 
+  theme(legend.position = "none")
+
+p_o_plot <- ggplot(pop_201_data, aes(x = p_o, fill = test)) + 
+  geom_histogram(color = "black") + 
+  theme_few()
+
+bulk_weight_plot <- ggplot(pop_201_data, aes(x = bulk_weight, fill = test)) + 
+  geom_histogram(color = "black") + 
+  theme_few()
+
+x11()
+(bulk_weight_plot+ p_o_plot) / md_plot + plot_layout(guides = "collect")
+
+
+

### 2022-04-25 _targets.R
update targets file (added a comma)

@@ -158,7 +158,7 @@ tar_plan(
   ##################################################
   tar_render(analysis_writeup, "doc/analysis_writeup.Rmd"), 
 
-  tar_render(overview_document, "doc/overview_document.Rmd")
+  tar_render(overview_document, "doc/overview_document.Rmd"),
   
   tar_render(manuscript_document, here("doc", "manuscript", "manuscript.Rmd"))
   

### 2022-04-26 doc/overview_document.Rmd
Added a high-level overview document to describe the overall experiment objectives and design

@@
 ---
-title: "Untitled Draft"
-author: "Report Author"
+title: "Project Overview"
+author: "Jay Gillenwater"
 date: "`r format(Sys.time(), '%d %B, %Y')`"
-output: html_document
+output: pdf_document
 ---
@@
 ## target knits Rmds in their own session, so load libraries here.
-## source("here::here(packages.R"))
+source(here::here("packages.R"))
 ```
@@
 ```{r load-targets, include=FALSE}
-# tar_load(c(target_1, target_2, target_3))
+tar_load(c(pop_development_pdf))
+```
 
-# # If your chunk output is shown in-line, then you'll need to wrap tar_load()
-# # like so:
-# 
-# withr::with_dir(here::here(), {
-#   tar_load(c(target_1, target_2, target_3))
-# })
-# 
-# # This is not needed when using tar_make() to render the document.
-```
 ## Introduction
+
 This document is a high-level overview of the experimental design and objectives of the "Jay" yield tests.
@@
 ## Objectives
-The overall objective of this experiment is to identify recombinant inbred lines (RILs) that have yield and agronomic qualities comparable to existing check cultivars, and have a protein + oil content that is greater than the check cultivars.
+
+The overall objective of this experiment is to identify recombinant inbred lines (RILs) that have yield and agronomic qualities comparable to existing check cultivars, and have a protein + oil content that is greater than the protein + oil content of the check cultivars.
 
 ## Experimental design
+
 The experiment consists of two tests, names test 1 and test 2, that are comprised of 15 RILs, and 5 check cultivars.
@@
 ## Population development
+
 The RILs used in these two tests come from two mapping populations that were initially grown as plant rows in 2018 at CLA.
@@
 
-After this data was collected, another round of selection was done that focused on the observed yield performance of the lines.
-Only lines that were within, or above a least significant difference of the average of the checks for each test were considered for advancement.
-Then, the thirty lines with the highest protein + oil content across all four tests were identified from among
+After this data was collected, another round of selection was done that focused on the observed yield and agronomic performance of the lines.
+Lines with poor agronomic qualities like significant lodging of poor pod load were first excluded from advancement.
+Then, only lines that were within or above a least significant difference of the average of the checks for each test were kept for consideration.
+Then, the thirty lines with the highest protein + oil content across all four tests were identified from among those that passed the yield threshold.
+These thirty lines were then split into two halves based on maturity date.
+Five checks were then added to each test for two final tests of 20 genotypes.
+These two tests were then grown over two years in the design from the section above.
+The same phenotypes were measured in field and after harvest that were measured in the preliminary trials in 2019.
 
-## Analysis
+I've added a small diagram of this overall development in the flowchart below.
 
-## Reproducibility
+```{r pop_flowchart, echo = FALSE, warning=FALSE, fig.align="center"}
 
-<details><summary>Reproducibility receipt</summary>
-
-```{r}
-## datetime
-Sys.time()
-
-## repository
-if(requireNamespace('git2r', quietly = TRUE)) {
-  git2r::repository()
-} else {
-  c(
-    system2("git", args = c("log", "--name-status", "-1"), stdout = TRUE),
-    system2("git", args = c("remote", "-v"), stdout = TRUE)
-  )
-}
-
-## session info
-sessionInfo()
+knitr::include_graphics(pop_development_pdf)
 ```
 
-</details>
+## Collected data
+
+The main traits we're interested in analyzing/summarizing are yield and the seed composition traits seed protein and oil.
+We do however have data on several agronomic traits including height, maturity date, seed weight, seed quality, and lodging.
+Yield was measured for all reps for both years while seed protein and oil were measured for reps 1-2 for both years.
+
+## Analysis and questions
+
+We used a linear model to analyze the data with the formula:
+
+$$y = \mu + GEN + ENV + GEN:ENV + REP(ENV) + \epsilon$$
+
+Where y is the value of some phenotype, $\mu$ is the overall mean, GEN is the genotype effect, ENV is the environment effect, GEN:ENV is the genotype x environment interaction effect, REP(ENV) is the effect of replication nested within environment, and $\epsilon$ is the measurement error.
+This model was used to perform an analysis of variance and to obtain genotype least square means.
+
+Going back to the overall goal of the experiment, we want to identify genotypes which have a yield comparable to or superior to that of some existing high-yielding cultivars, and seed composition traits that are superior to those high-yielding cultivars.
+The criteria by which we can declare that a RIL has these qualities is where I have the most questions.
+I've seen a few papers that used a least-significant difference value to compare means of new cultivars to other established cultivars and was wondering if this would be an appropriate test to use.
+I have also read a fair amount of criticism for using the least significant difference to compare means since it doesn't correct for multiple comparisons.
+Because of that, I was considering using Tukeys HSD instead, or another correction to the standard LSD test to account for multiple comparisons.
+We also used multiple check cultivars within each test, but as far as I can tell the multiple comparison statistics are only strictly appropriate for comparing the means of one cultivar with the means of one other, and I didn't know how appropriate it would be to use a LSD/HSD value to compare the mean of one RIL with the average of the checks for each test.

### 2022-04-26 R/export_pop_development_pdf.R

@@ -1,0 +1,15 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param pop_development_flowchart
+export_pop_development_pdf <- function(pop_development_flowchart) {
+
+  DiagrammeR::grViz(pop_development_flowchart) %>% 
+    export_svg() %>% 
+    charToRaw() %>% 
+    rsvg_png(file = here("exports", "plots", "pop_development_flowchart.png"))
+  
+  return(here("exports", "plots", "pop_development_flowchart.png"))
+}

### 2022-04-26 R/merge_yield_data.R

@@ -105,11 +105,14 @@ merge_yield_data <- function(yield_2019_file, cas_maturity_file,
   all_merged <- map(all_yield, function(x) filter_fn(x, keep_cols)) %>% 
     reduce(bind_rows) %>% 
     mutate(across(any_of(num_cols), as.numeric), 
+           protein = ifelse(as.numeric(rep) > 2, NA, protein), 
+           oil     = ifelse(as.numeric(rep) > 2, NA, oil),
            protein_plus_oil = protein + oil, 
            yield = ifelse(year %in% c("2020"), yield*0.033, 
                           ifelse(year == "2019", yield/67.2510693716674, 
                             ifelse(loc %in% c("PLY", "SAN"), yield*0.0252, yield*0.0228))), 
-           ENV = paste(loc, year, sep = " - "))
+           ENV = paste(loc, year, sep = " - ")) %>% 
+    distinct()
   
   # Standardize genotype names so that each genotype is identified with
   # only name. See the function definition in the utils.R script.

### 2022-04-26 _targets.R

@@ -72,6 +72,16 @@ tar_plan(
              here("data", "utils", "summary_column_names.xlsx"), 
              format = "file"),
   
+  # A flowchart to show the population development as a graphviz file
+  tar_target(pop_development_flowchart, 
+             here("graphviz_docs", "graph.gv"), 
+             format = "file"),
+  
+  # Export this flowchart as a pdf
+  tar_target(pop_development_pdf, 
+             export_pop_development_pdf(pop_development_flowchart), 
+             format = "file"),
+  
   ## Section: Data cleaning
   ##################################################
   

### 2022-04-26 packages.R

@@ -28,7 +28,10 @@ pacman::p_load(ggthemes,
                patchwork,
                extrafont, 
                GGally, 
-               scales)
+               scales, 
+               DiagrammeRsvg, 
+               DiagrammeR, 
+               rsvg)
 
 # Analysis
 pacman::p_load(metan,

### 2022-04-26 sandbox/reproducibility tab.R

@@ -1,0 +1,21 @@
+<details><summary>Reproducibility receipt</summary>
+  
+  ```{r}
+## datetime
+Sys.time()
+
+## repository
+if(requireNamespace('git2r', quietly = TRUE)) {
+  git2r::repository()
+} else {
+  c(
+    system2("git", args = c("log", "--name-status", "-1"), stdout = TRUE),
+    system2("git", args = c("remote", "-v"), stdout = TRUE)
+  )
+}
+
+## session info
+sessionInfo()
+```
+
+</details>

### 2022-04-26 doc/manuscript/manuscript.Rmd
Some small changes to the targets file to use the here functioninstead of absolute file paths

@@
 This Rmd-skeleton uses the mdpi Latex template published 2019/02.
-However, the official template gets more frequently updated than the 'rticles'
-package. Therefore, please make sure prior to paper submission, that you're 
-using the most recent .cls, .tex and .bst files 
-(available [here](http://www.mdpi.com/authors/latex)).
+However, the official template gets more frequently updated than the 'rticles' package.
+Therefore, please make sure prior to paper submission, that you're using the most recent .cls, .tex and .bst files (available [here](http://www.mdpi.com/authors/latex)).
 
@@
 
-Soybean lines typically contain about 20\% oil and 40\% protein content on a dry weight basis[@ProteinGenomics].
-The market for soybean meal requires 47.5\% protein content in the meal, which corresponds to approximately 41.5\% protein content on a dry weight basis[@ProteinGenomics].
+Soybean lines typically contain about 20% oil and 40% protein content on a dry weight basis[@ProteinGenomics].
+The market for soybean meal requires 47.5% protein content in the meal, which corresponds to approximately 41.5% protein content on a dry weight basis[@ProteinGenomics].
 Oil and protein content are two of the most important seed composition traits in soybean so if one is decreased, the other should be correspondingly increased to account for the loss in value.
@@
 Despite the difficulty in simultaneously breeding for all three of these traits, releases of varieties with elevated protein contents and only moderately reduced yield has shown that it is not impossible.
-The high protein germplasm lines R05-1415 and R05-1772 were released recently and contain 46.9\% and 46.1\% protein content with while still producing yields 94\% and 91\% of that of the high yielding 5002T cultivar[@HiProtHiYield02].
-Lines TN03-350 and TN04-5321 contain 43.9\% and 43.1\% protein content while having superior or comparable performance to yield checks[@HiProtHiYield04].
-The Prolina cultivar has a protein content of 46.1\% with a yield only 13\% reduced from the Centennial check[@HiProtHiYield01].
-The Highpro1 cultivar was released in 2016 and has a yield which is greater than or equal to 97\% of that of the highest yielding check cultivar, IA3023 with a protein content of 40.1\%[@HighPro1].
+The high protein germplasm lines R05-1415 and R05-1772 were released recently and contain 46.9% and 46.1% protein content with while still producing yields 94% and 91% of that of the high yielding 5002T cultivar[@HiProtHiYield02].
+Lines TN03-350 and TN04-5321 contain 43.9% and 43.1% protein content while having superior or comparable performance to yield checks[@HiProtHiYield04].
+The Prolina cultivar has a protein content of 46.1% with a yield only 13% reduced from the Centennial check[@HiProtHiYield01].
+The Highpro1 cultivar was released in 2016 and has a yield which is greater than or equal to 97% of that of the highest yielding check cultivar, IA3023 with a protein content of 40.1%[@HighPro1].
 Cultivars produced through conventional breeding techniques such as these have shown that it is possible to identify lines with both high seed protein and seed yield.
@@
 ## Population development
+
 In 2018, oil mapping populations 201 and 202 were grown as plant rows at the Central Crops Research Station in Clayton, NC.
@@
 Lodging was scored on a scale of 1-5 where 5 indicates that all plants in a plot are on the ground, and a score of 1 indicates that all plants are erect[@fehr1987soybeans].
-The agronomic score aimed to capture other traits of value such as visual estimation of pod load and plot uniformity to provide a general score of a line’s agronomic desirability.
+The agronomic score aimed to capture other traits of value such as visual estimation of pod load and plot uniformity to provide a general score of a line's agronomic desirability.
 Agronomic score was recorded on a scale of 1-5 as well, with 1 identifying the best lines of a population, and 5 the worst.
@@
 ## Statistical Analysis
+
 Phenotypic traits were analysed with a linear model with the form:
@@
 
-* First bullet
-* Second bullet
-* Third bullet
+-   First bullet
+-   Second bullet
+-   Third bullet
 
@@
 
+```{=tex}
 \begin{figure}[H]
@@
 \end{figure}
-
+```
+```{=tex}
 \begin{figure}[H]
@@
 \end{figure}
-
+```
+```{=tex}
 \begin{table}[H]
@@
 \end{table}
-
+```
 ```{r test_table, results = "asis", echo = FALSE}
@@
 \mathbb{S}
-\end{equation}
-<!-- If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
+\end{equation} <!-- If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
 This ensures correct linenumbering.
@@
 <!-- Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows: -->
+
 Example of a theorem:
+
+```{=tex}
 \begin{Theorem}
@@
 \end{Theorem}
-
+```
 The text continues here. Proofs must be formatted as follows:
@@
 Example of a proof:
+
+```{=tex}
 \begin{proof}[Proof of Theorem 1]
@@
 \end{proof}
+```
 The text continues here.

### 2022-04-26 R/get_lsd_values.R

@@ -60,9 +60,6 @@ get_lsd_values <- function(df = all_yield_data$two_year) {
       ungroup()  %>%
       mutate(data = map(data, clean_data))
     
-    # I took this part out to test using the HSD test function with the unbalanced
-    # data
-    #
     
     model_fn <- function(pheno_data) {
       

### 2022-04-26 _targets.R

@@ -166,9 +166,9 @@ tar_plan(
   
   ## Section: Writeup documents
   ##################################################
-  tar_render(analysis_writeup, "doc/analysis_writeup.Rmd"), 
+  tar_render(analysis_writeup, here("doc", "analysis_writeup.Rmd")), 
 
-  tar_render(overview_document, "doc/overview_document.Rmd"),
+  tar_render(overview_document, here("doc", "overview_document.Rmd")),
   
   tar_render(manuscript_document, here("doc", "manuscript", "manuscript.Rmd"))
   

### 2022-04-26 sandbox/selection plots development.R

@@ -29,7 +29,7 @@ selected_genotypes_2019 <- all_yield_data %>%
   dplyr::filter(!is.na(md)) %>% 
   bind_rows(plant_row_data) %>%
   mutate(p_o = protein_dry_basis + oil_dry_basis) %>%
-  select(test, genotype, population, md, ht, sdwt, bulk_weight, oil_dry_basis, protein_dry_basis, p_o) %>%
+  select(test, genotype, population, year, md, ht, sdwt, bulk_weight, oil_dry_basis, protein_dry_basis, p_o) %>%
   split_factors(population, keep_factors = TRUE)
 
 # The data for one of the population to test plotting functions
@@ -52,5 +52,9 @@ bulk_weight_plot <- ggplot(pop_201_data, aes(x = bulk_weight, fill = test)) +
 x11()
 (bulk_weight_plot+ p_o_plot) / md_plot + plot_layout(guides = "collect")
 
+DiagrammeR::grViz(pop_development_flowchart) %>% 
+  export_svg() %>% 
+  charToRaw() %>% 
+  rsvg_pdf(file = here("exports", "plots", "pop_development_flowchart.pdf"))
 
 

### 2022-04-29 doc/manuscript/manuscript.Rmd
Added some cleaned up contrast functions to the main R folder that I can use to analyze the lists of linear/mixed models.

@@
 
-Phenotypic traits were analysed with a linear model with the form:
+Phenotypic traits were analysed with a mixed effects model with the form:
 
-$$y_{ijk} = \mu + L_i + B(L_i) + G_k + GL_{ik} + \epsilon_{ijk}$$
+$$y_{ijk} = \mu + E_i + B(E_i) + G_k + GE_{ik} + \epsilon_{ijk}$$
 
-Where $y_{ijk}$ is the phenotypic measurement for rep$j$ of genotype $k$ in environment $i$, $L_i$ is the effect of location $i$, $G_k$ is the effect of genotype $G$, $GL_{ik}$ is the interaction effect of location $L$ and genotype $G$, and $\epsilon_{ijk}$ is the measurement error.
+Where $y_{ijk}$ is the phenotypic measurement for rep$j$ of genotype $k$ in environment $i$, $E_i$ is the effect of environment $i$, $B(E_i)$ is the effect of replication nested within environment, $G_k$ is the effect of genotype $G$, $GE_{ik}$ is the interaction effect of environment $E$ and genotype $G$, and $\epsilon_{ijk}$ is the measurement error.
+The genotype effect was treated as fixed and all other factors were treated as random.
 
-Models were fit using the lm function in R[@rcoreteamLanguageEnvironmentStatistical2022], and analysis of variance (ANOVA) performed using the anova function.
+Models were fit using the gamem_met function from the metan package[@olivotoMetanPackageMultienvironment2020].
 Least-square means (LS Means) for each genotype and trait were calculated using the above model using the emmeans package[@lenthEmmeansEstimatedMarginal2022] in R.
-Least-significant difference values for each trait were calculated using the LSD.test function from the agricolae[@de2014agricolae] package.
+The emmeans package was also used to calculate contrasts as a post-hoc test to compare RIL means to check means.
 Pearson correlation coefficients between each phenotype were calculated with the cor function in R.

### 2022-04-29 doc/manuscript/manuscript.tex
Added some cleaned up contrast functions to the main R folder that I can use to analyze the lists of linear/mixed models.

@@
 
-Phenotypic traits were analysed with a linear model with the form:
+Phenotypic traits were analysed with a mixed effects model with the
+form:
 
-\[y_{ijk} = \mu + L_i + B(L_i) + G_k + GL_{ik} + \epsilon_{ijk}\]
+\[y_{ijk} = \mu + E_i + B(E_i) + G_k + GE_{ik} + \epsilon_{ijk}\]
 
 Where \(y_{ijk}\) is the phenotypic measurement for rep\(j\) of genotype
-\(k\) in environment \(i\), \(L_i\) is the effect of location \(i\),
-\(G_k\) is the effect of genotype \(G\), \(GL_{ik}\) is the interaction
-effect of location \(L\) and genotype \(G\), and \(\epsilon_{ijk}\) is
-the measurement error.
+\(k\) in environment \(i\), \(E_i\) is the effect of environment \(i\),
+\(B(E_i)\) is the effect of replication nested within environment,
+\(G_k\) is the effect of genotype \(G\), \(GE_{ik}\) is the interaction
+effect of environment \(E\) and genotype \(G\), and \(\epsilon_{ijk}\)
+is the measurement error. The genotype effect was treated as fixed and
+all other factors were treated as random.
 
-Models were fit using the lm function in
-R\citep{rcoreteamLanguageEnvironmentStatistical2022}, and analysis of
-variance (ANOVA) performed using the anova function. Least-square means
-(LS Means) for each genotype and trait were calculated using the above
-model using the emmeans package\citep{lenthEmmeansEstimatedMarginal2022}
-in R. Least-significant difference values for each trait were calculated
-using the LSD.test function from the agricolae\citep{de2014agricolae}
-package. Pearson correlation coefficients between each phenotype were
-calculated with the cor function in R.
+Models were fit using the gamem\_met function from the metan
+package\citep{olivotoMetanPackageMultienvironment2020}. Least-square
+means (LS Means) for each genotype and trait were calculated using the
+above model using the emmeans
+package\citep{lenthEmmeansEstimatedMarginal2022} in R. The emmeans
+package was also used to calculate contrasts as a post-hoc test to
+compare RIL means to check means. Pearson correlation coefficients
+between each phenotype were calculated with the cor function in R.
 

### 2022-04-29 R/contrast_functions.R

@@ -1,0 +1,93 @@
+##################################################
+## Project: Jay Gillenwater
+## Script purpose: Holds multiple functions for perfoming post-hoc comparison
+## tests on linear/mixed models by using contrasts to compare RIL vs check means
+## Date: 2022-04-29
+## Author: Jay Gillenwater
+##################################################
+
+# A function to identify the checks vs the RILs and return
+# a list of named contrast lists
+check_ril_contrasts <- function(mar_means, check_genotypes = util_tables$yield_checks){
+  
+  # Convert the emmgrid to a tibble
+  means_tibble <- as_tibble(mar_means)
+  
+  # Identify checks and RILs with numeric vectors
+  check_contrasts <- means_tibble$GEN %in% check_genotypes$genotype
+  ril_contrasts   <- !check_contrasts %>% as.numeric()
+  check_contrasts <- as.numeric(check_contrasts)
+  
+  # I'm not sure if this is accomplishing what I really want to do right now...
+  # Maybe a set of contrasts for each RIL and one for the average of checks(?)
+  # Need to open the stats textbook back up
+  ril_contrasts   <- ril_contrasts/sum(ril_contrasts)
+  check_contrasts <- check_contrasts/sum(check_contrasts)
+  
+  # Maybe something like this?
+  ril_genos <- means_tibble$GEN[ril_contrasts != 0]
+  
+  # A function to return a vector with a 1 in the position of a genotype
+  # name match, and a zero everywhere else
+  genotype_contrast <- function(genotype, genotype_vector = means_tibble$GEN){
+    
+    (genotype_vector == genotype) %>% 
+      as.numeric()
+    
+  }
+  
+  # A function to return a named list of genotype vs check contrasts
+  genotype_minus_check_contrast <- function(genotype){
+    
+    ril_contrast <- genotype_contrast(genotype)
+    
+    res <- ril_contrast - check_contrasts
+    
+    return(res)
+  }
+  
+  # Get the names for all the ril by check contrasts and then get
+  # these contrasts
+  contrast_names <- paste(ril_genos, "Checks", sep = " - ")
+  
+  all_ril_contrasts <- map(ril_genos, genotype_minus_check_contrast) %>% 
+    set_names(contrast_names)
+  
+  res <- list("overall_means" = list("RIL - Check" = ril_contrasts - check_contrasts), 
+              "individual_RIL_contrasts" = all_ril_contrasts)
+  
[…]

### 2022-04-29 _targets.R

@@ -66,7 +66,7 @@ tar_plan(
              here("data", "utils", "trait_shortname_lookup.xlsx"), 
              format = "file"),
   
-  # A table to convert short column names in sumamry tables to longer, 
+  # A table to convert short column names in summary tables to longer, 
   # more descriptive names
   tar_target(column_shortname_conversion, 
              here("data", "utils", "summary_column_names.xlsx"), 

### 2022-05-06 doc/overview_document.tex
Added a script to work on emmean se plots

--- 2022-04-26 doc/overview_document.Rmd
@@
----
-title: "Project Overview"
-author: "Jay Gillenwater"
-date: "`r format(Sys.time(), '%d %B, %Y')`"
-output: pdf_document
----
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+]{article}
+\usepackage{amsmath,amssymb}
+\usepackage{lmodern}
+\usepackage{ifxetex,ifluatex}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={Project Overview},
+  pdfauthor={Jay Gillenwater},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
+\usepackage[margin=1in]{geometry}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+\ifluatex
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
-## target knits Rmds in their own session, so load libraries here.
-source(here::here("packages.R"))
-```
+\title{Project Overview}
+\author{Jay Gillenwater}
+\date{06 May, 2022}
 
-```{r load-targets, include=FALSE}
-tar_load(c(pop_development_pdf))
-```
+\begin{document}
+\maketitle
 
-## Introduction
+\hypertarget{introduction}{%
+\subsection{Introduction}\label{introduction}}
 
-This document is a high-level overview of the experimental design and objectives of the "Jay" yield tests.
+This document is a high-level overview of the experimental design and
+objectives of the ``Jay'' yield tests.
 
-## Objectives
+\hypertarget{objectives}{%
+\subsection{Objectives}\label{objectives}}
 
-The overall objective of this experiment is to identify recombinant inbred lines (RILs) that have yield and agronomic qualities comparable to existing check cultivars, and have a protein + oil content that is greater than the protein + oil content of the check cultivars.
+The overall objective of this experiment is to identify recombinant
+inbred lines (RILs) that have yield and agronomic qualities comparable
+to existing check cultivars, and have a protein + oil content that is
+greater than the protein + oil content of the check cultivars.
 
-## Experimental design
+\hypertarget{experimental-design}{%
+\subsection{Experimental design}\label{experimental-design}}
 
-The experiment consists of two tests, names test 1 and test 2, that are comprised of 15 RILs, and 5 check cultivars.
-These two tests were grown in a RCBD in 2020 and 2021, in two locations for each year.
-In 2020, each test was grown at the Clayton (CLA) and Caswell (CAS) research stations, while in 2021 each test was grown at the Plymouth (PLY) research station and CAS.
-Each test was grown in four replications within each location for both years.
+The experiment consists of two tests, names test 1 and test 2, that are
+comprised of 15 RILs, and 5 check cultivars. These two tests were grown
+in a RCBD in 2020 and 2021, in two locations for each year. In 2020,
+each test was grown at the Clayton (CLA) and Caswell (CAS) research
+stations, while in 2021 each test was grown at the Plymouth (PLY)
+research station and CAS. Each test was grown in four replications
+within each location for both years.
 
-## Population development
+\hypertarget{population-development}{%
+\subsection{Population development}\label{population-development}}
 
-The RILs used in these two tests come from two mapping populations that were initially grown as plant rows in 2018 at CLA.
-We noticed some of the lines in these two populations had some good combinations of agronomic qualities, and seed composition traits and this is how we first got the idea to more rigorously evaluate the yield performance potential of a selection of the lines from these two populations.
-These two populations were too large to test every line so we first made some selections to identify 80 lines from each population that would be tested for yield performance.
-Briefly, this selection scheme first removed any lines from consideration that had poor lodging, seed load, or bulk weight, and any lines with extreme maturity dates.
-Lines were then selected so that the entire distribution of protein and oil content of the starting mapping populations would be represented in the selection.
-The 80 lines for each population were then split into two tests of 40 RILs based on maturity date.
-Three check cultivars and the mapping population parents were then included in the tests as well for a final set of four tests with 45 lines each.
+The RILs used in these two tests come from two mapping populations that
+were initially grown as plant rows in 2018 at CLA. We noticed some of
+the lines in these two populations had some good combinations of
+agronomic qualities, and seed composition traits and this is how we
+first got the idea to more rigorously evaluate the yield performance
+potential of a selection of the lines from these two populations. These
+two populations were too large to test every line so we first made some
+selections to identify 80 lines from each population that would be
+tested for yield performance. Briefly, this selection scheme first
+removed any lines from consideration that had poor lodging, seed load,
+or bulk weight, and any lines with extreme maturity dates. Lines were
+then selected so that the entire distribution of protein and oil content
+of the starting mapping populations would be represented in the
+selection. The 80 lines for each population were then split into two
+tests of 40 RILs based on maturity date. Three check cultivars and the
+mapping population parents were then included in the tests as well for a
+final set of four tests with 45 lines each.
 
-These four tests were grown in PLY and CAS in 2019.
-Agronomic notes including lodging, height, maturity date, and an agronomic score based on overall appearance were taken in the field and yield, seed weight, protein, and oil content were measured after harvesting.
+These four tests were grown in PLY and CAS in 2019. Agronomic notes
+including lodging, height, maturity date, and an agronomic score based
+on overall appearance were taken in the field and yield, seed weight,
+protein, and oil content were measured after harvesting.
 
-After this data was collected, another round of selection was done that focused on the observed yield and agronomic performance of the lines.
-Lines with poor agronomic qualities like significant lodging of poor pod load were first excluded from advancement.
-Then, only lines that were within or above a least significant difference of the average of the checks for each test were kept for consideration.
-Then, the thirty lines with the highest protein + oil content across all four tests were identified from among those that passed the yield threshold.
-These thirty lines were then split into two halves based on maturity date.
-Five checks were then added to each test for two final tests of 20 genotypes.
-These two tests were then grown over two years in the design from the section above.
-The same phenotypes were measured in field and after harvest that were measured in the preliminary trials in 2019.
+After this data was collected, another round of selection was done that
+focused on the observed yield and agronomic performance of the lines.
+Lines with poor agronomic qualities like significant lodging of poor pod
+load were first excluded from advancement. Then, only lines that were
+within or above a least significant difference of the average of the
+checks for each test were kept for consideration. Then, the thirty lines
+with the highest protein + oil content across all four tests were
+identified from among those that passed the yield threshold. These
+thirty lines were then split into two halves based on maturity date.
+Five checks were then added to each test for two final tests of 20
+genotypes. These two tests were then grown over two years in the design
+from the section above. The same phenotypes were measured in field and
+after harvest that were measured in the preliminary trials in 2019.
 
-I've added a small diagram of this overall development in the flowchart below.
+I've added a small diagram of this overall development in the flowchart
+below.
 
-```{r pop_flowchart, echo = FALSE, warning=FALSE, fig.align="center"}
+\begin{center}\includegraphics{C:/Users/Jay/Desktop/Documents/R/Jay_yield/exports/plots/pop_development_flowchart} \end{center}
 
-knitr::include_graphics(pop_development_pdf)
-```
+\hypertarget{collected-data}{%
+\subsection{Collected data}\label{collected-data}}
 
-## Collected data
+The main traits we're interested in analyzing/summarizing are yield and
+the seed composition traits seed protein and oil. We do however have
+data on several agronomic traits including height, maturity date, seed
+weight, seed quality, and lodging. Yield was measured for all reps for
+both years while seed protein and oil were measured for reps 1-2 for
+both years.
 
-The main traits we're interested in analyzing/summarizing are yield and the seed composition traits seed protein and oil.
-We do however have data on several agronomic traits including height, maturity date, seed weight, seed quality, and lodging.
-Yield was measured for all reps for both years while seed protein and oil were measured for reps 1-2 for both years.
-
-## Analysis and questions
+\hypertarget{analysis-and-questions}{%
+\subsection{Analysis and questions}\label{analysis-and-questions}}
 
@@
 
-$$y = \mu + GEN + ENV + GEN:ENV + REP(ENV) + \epsilon$$
+\[y = \mu + GEN + ENV + GEN:ENV + REP(ENV) + \epsilon\]
 
-Where y is the value of some phenotype, $\mu$ is the overall mean, GEN is the genotype effect, ENV is the environment effect, GEN:ENV is the genotype x environment interaction effect, REP(ENV) is the effect of replication nested within environment, and $\epsilon$ is the measurement error.
-This model was used to perform an analysis of variance and to obtain genotype least square means.
+Where y is the value of some phenotype, \(\mu\) is the overall mean, GEN
+is the genotype effect, ENV is the environment effect, GEN:ENV is the
+genotype x environment interaction effect, REP(ENV) is the effect of
+replication nested within environment, and \(\epsilon\) is the
+measurement error. This model was used to perform an analysis of
+variance and to obtain genotype least square means.
 
-Going back to the overall goal of the experiment, we want to identify genotypes which have a yield comparable to or superior to that of some existing high-yielding cultivars, and seed composition traits that are superior to those high-yielding cultivars.
-The criteria by which we can declare that a RIL has these qualities is where I have the most questions.
-I've seen a few papers that used a least-significant difference value to compare means of new cultivars to other established cultivars and was wondering if this would be an appropriate test to use.
-I have also read a fair amount of criticism for using the least significant difference to compare means since it doesn't correct for multiple comparisons.
-Because of that, I was considering using Tukeys HSD instead, or another correction to the standard LSD test to account for multiple comparisons.
-We also used multiple check cultivars within each test, but as far as I can tell the multiple comparison statistics are only strictly appropriate for comparing the means of one cultivar with the means of one other, and I didn't know how appropriate it would be to use a LSD/HSD value to compare the mean of one RIL with the average of the checks for each test.
+Going back to the overall goal of the experiment, we want to identify
+genotypes which have a yield comparable to or superior to that of some
+existing high-yielding cultivars, and seed composition traits that are
+superior to those high-yielding cultivars. The criteria by which we can
+declare that a RIL has these qualities is where I have the most
+questions. I've seen a few papers that used a least-significant
+difference value to compare means of new cultivars to other established
+cultivars and was wondering if this would be an appropriate test to use.
+I have also read a fair amount of criticism for using the least
+significant difference to compare means since it doesn't correct for
+multiple comparisons. Because of that, I was considering using Tukeys
+HSD instead, or another correction to the standard LSD test to account
+for multiple comparisons. We also used multiple check cultivars within
+each test, but as far as I can tell the multiple comparison statistics
+are only strictly appropriate for comparing the means of one cultivar
+with the means of one other, and I didn't know how appropriate it would
+be to use a LSD/HSD value to compare the mean of one RIL with the
+average of the checks for each test.
+
+\end{document}

### 2022-05-06 R/contrast_functions.R

@@ -62,7 +62,7 @@ check_ril_contrasts <- function(mar_means, check_genotypes = util_tables$yield_c
 
 # A function to apply the above function to the nested anova list in the 
 # anova_two_years object
-make_contrast_tibble <- function(test_list, test_names = names(test_list), model_type = "linear"){
+make_contrast_tibble <- function(test_list, test_names = names(test_list), model_type = "linear", check_genos = util_tables$yield_checks){
   
   pluck_item <- ifelse(model_type == "linear", "model", 
                        ifelse(model_type == "mixed", "modellme", stop("model_type should be one of 'linear' or 'mixed'")))
@@ -79,7 +79,7 @@ make_contrast_tibble <- function(test_list, test_names = names(test_list), model
     contrast_tibble <- tibble(pheno = names(model_data)) %>% 
       mutate(test_name = test_name, 
              mar_means = map(model_data, function(x) x %>% pluck(pluck_item) %>% emmeans("GEN")), 
-             contrast_vecs = map(mar_means, check_ril_contrasts), 
+             contrast_vecs = map(mar_means, check_ril_contrasts, check_genos), 
              contrasts = map2(mar_means, contrast_vecs, function(x, y) contrast(x, y$individual_RIL_contrasts, adjust = "sidak"))) %>% 
       relocate(test_name, 1)
     

### 2022-05-06 _targets.R

@@ -134,6 +134,17 @@ tar_plan(
   tar_target(least_sig_differences, 
              get_lsd_values(df = all_yield_data$two_year)),
   
+  # Conrasts of RIL means vs check means
+  tar_target(genotype_contrasts_anova, 
+             make_contrast_tibble(anova_two_years, 
+                                  model_type = "linear", 
+                                  check_genos = util_tables$yield_checks)), 
+  
+  tar_target(genotype_contrasts_mixed, 
+             make_contrast_tibble(mixed_models_two_years,
+                                  model_type = "mixed", 
+                                  check_genos = util_tables$yield_checks)),
+  
   
   ## Section: Analysis summaries
   ##################################################

### 2022-05-06 sandbox/emmean SE plot.R

@@ -1,0 +1,47 @@
+##################################################
+## Project: Jay Yield
+## Script purpose: Get marginal means from mixed models with standard errors
+## Date: 2022-05-06
+## Author: Jay Gillenwater
+##################################################
+
+source("./packages.R")
+tar_load(c(mixed_models_two_years, util_tables))
+
+
+get_mar_means <- function(test_data, pheno_names = names(test_data)){
+  
+  one_pheno_means <- function(pheno_model, pheno_name){
+    pheno_model %>% 
+      pluck("modellme") %>% 
+      emmeans("GEN") %>% 
+      as_tibble() %>% 
+      mutate(pheno_name = pheno_name) %>% 
+      relocate(pheno_name, .after = "GEN")
+  }
+  
+  map2(test_data, pheno_names, one_pheno_means) %>% 
+    reduce(bind_rows)
+  
+}
+
+
+
+one_test <- map(mixed_models_two_years, get_mar_means)$`Jay Test 1`
+
+
+check_means <- one_test %>% 
+  dplyr::filter(GEN %in% util_tables$yield_checks$genotype) %>% 
+  group_by(pheno_name) %>% 
+  summarise(check_avg = mean(emmean))
+
+se_table <- left_join(one_test, check_means, by = "pheno_name") %>% 
+  mutate(above_avg = ifelse(emmean > check_avg, "Above check average", "Below check average")) %>% 
+  select(GEN, pheno_name, emmean, SE, above_avg) %>% 
+  dplyr::filter(pheno_name == "yield")
+
+ggplot(se_table, aes(x = emmean, y = reorder(GEN, emmean), fill = above_avg)) + 
+  geom_point(shape = 21, size = 3) + 
+  geom_errorbarh(aes(xmax = emmean + SE, xmin = emmean - SE)) + 
+  theme_hc()
+

### 2022-05-06 sandbox/yield summary tables.R

@@ -82,7 +82,10 @@ make_pheno_comparison <- function(test_data, keep_phenos = c("yield", "protein",
     summarise(check_avg_value = mean(value, na.rm = TRUE)) %>% 
     mutate(check_avg_value = round(check_avg_value, 2))
   
-  left_join(genotype_ranks, check_pheno_avg, by = "pheno")
+  full_data <- left_join(genotype_ranks, check_pheno_avg, by = "pheno") %>% 
+    mutate(value = paste0(value, " (", round((value/check_avg_value)*100, 1), "%)"))
+  
+  return(full_data)
   
 }
 
@@ -187,7 +190,7 @@ remove_phenotype_names <- function(column_names, pheno_names = c("yield", "prote
 
 
 # A function to make a kable table with group headings to match phenotypes
-make_phenotype_comparison_table <- function(comparison_table_output, pheno_names = c("yield", "protein", "oil", "protein_plus_oil")){
+make_phenotype_comparison_table <- function(comparison_table_output, pheno_names = c("yield", "protein", "oil", "protein_plus_oil"), keep_msd = TRUE){
   
   # First, sort the indices of the phenotypes by the order in which they appear 
   # in the comparison table
@@ -234,6 +237,32 @@ make_phenotype_comparison_table <- function(comparison_table_output, pheno_names
   
   current_table <- as.data.frame(current_table)
   
+  # If you want to remove the MSD columns (Like if I'm data from mixed models instead of the linear models)
+  if(!keep_msd){
+    
+    # Remove the HSD columns from the collapse rows indices
+    exclude_cols     <- which(colnames(current_table) == "HSD")
+    
+    newcolnames <- colnames(current_table)[-exclude_cols]
+    
+    # And reduce the header widths by 1 for each phenotype
+    column_groups <- c(rep("", pheno_start_col-1), phenotype_widths-1)
+    
+    # Finally, remove the HSD columns from the overall data
+    current_table <- current_table[, -exclude_cols]
+    colnames(current_table) <- newcolnames
+    
+    # variables that can have their rows collapsed
+    collapse_cols <- c("Test Average", 
+                       "Check Average")
+    
+    # The indices of these columns
+    collapse_indices <- map(collapse_cols, function(x) which(str_detect(colnames(current_table), x))) %>% 
+      unlist() %>% 
+      unique() %>% 
+      sort()
+  }
+  
   
[…]

### 2022-05-09 doc/manuscript/manuscript.Rmd
Added a function to make a latex version of the yield summary table

@@
 abstract: |
-  A single paragraph of about 200 words maximum. For research articles, 
-  abstracts should give a pertinent overview of the work. We strongly encourage
-  authors to use the following style of structured abstracts, but without 
-  headings: 1) Background: Place the question addressed in a broad context and
-  highlight the purpose of the study; 2) Methods: Describe briefly the main
-  methods or treatments applied; 3) Results: Summarize the article's main 
-  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
-  The abstract should be an objective representation of the article, it must not 
-  contain results which are not presented and substantiated in the main text and 
-  should not exaggerate the main conclusions.
+  In current markets, the primary uses for soybean seed are in products derived from 
+  it's oil or protein content. However, growers are compensated based on seed oil so 
+  a more valuable crop is one with both high yield, and high protein, oil, or a combination of the two. A negative 
+  correlation between seed yield and seed protein makes improving these traits simultaneously difficult but 
+  not impossible through conventional breeding. A selection of lines with exceptional yield and seed 
+  composition qualities was made from two recombinant inbred line (RIL) soybean mapping populations to identify soybean
+  varieties with yield comparable to existing cultivars, and seed composition traits superior to existing cultivars.
 keywords: |
@@
 source(here("packages.R"))
-tar_load(c(example_table))
+tar_load(c(example_table, 
+           yield_summary_tables))
 ```
@@
 The emmeans package was also used to calculate contrasts as a post-hoc test to compare RIL means to check means.
-Pearson correlation coefficients between each phenotype were calculated with the cor function in R.
+Pearson correlation coefficients between each phenotype were calculated and visualized with the metan package.
 
@@
 
-This section may be divided by subheadings.
-It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
+Multiple RILs in each test were identified with yield comparable to, or superior to that of the check cultivars included in each test.
+
+```{r test1_summary_table, results = "asis", echo = FALSE}
+
+print(yield_summary_tables$`Jay Test 1`)
+
+```
 

### 2022-05-09 doc/manuscript/manuscript.tex
Added a function to make a latex version of the yield summary table

@@
 % Abstract (Do not insert blank lines, i.e. \\)
-\abstract{A single paragraph of about 200 words maximum. For research
-articles, abstracts should give a pertinent overview of the work. We
-strongly encourage authors to use the following style of structured
-abstracts, but without headings: 1) Background: Place the question
-addressed in a broad context and highlight the purpose of the study; 2)
-Methods: Describe briefly the main methods or treatments applied; 3)
-Results: Summarize the article's main findings; and 4) Conclusion:
-Indicate the main conclusions or interpretations. The abstract should be
-an objective representation of the article, it must not contain results
-which are not presented and substantiated in the main text and should
-not exaggerate the main conclusions.}
+\abstract{In current markets, the primary uses for soybean seed are in
+products derived from it's oil or protein content. However, growers are
+compensated based on seed oil so a more valuable crop is one with both
+high yield, and high protein, oil, or a combination of the two. A
+negative correlation between seed yield and seed protein makes improving
+these traits simultaneously difficult but not impossible through
+conventional breeding. A selection of lines with exceptional yield and
+seed composition qualities was made from two recombinant inbred line
+(RIL) soybean mapping populations to identify soybean varieties with
+yield comparable to existing cultivars, and seed composition traits
+superior to existing cultivars.}
 
@@
 compare RIL means to check means. Pearson correlation coefficients
-between each phenotype were calculated with the cor function in R.
+between each phenotype were calculated and visualized with the metan
+package.
 
@@
 
-This section may be divided by subheadings. It should provide a concise
-and precise description of the experimental results, their
-interpretation as well as the experimental conclusions that can be
-drawn.
+Multiple RILs in each test were identified with yield comparable to, or
+superior to that of the check cultivars included in each test.
+
+\begin{table}
+
+\caption{Marginal means and rankings of genotypes in Jay Test 1 for seed yield, seed oil, and seed protein.}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}[t]{ccccccccccccc}
+\toprule
+\multicolumn{1}{c}{} & \multicolumn{4}{c}{Protein} & \multicolumn{4}{c}{Yield} & \multicolumn{4}{c}{Oil} \\
+\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9} \cmidrule(l{3pt}r{3pt}){10-13}
+Genotype & Value \textbackslash{}textsuperscript\{*\} & Rank\textbackslash{}\textbackslash{}textsuperscript\{\textbackslash{}\textbackslash{}dag\} & Test Average\textbackslash{}\textbackslash{}textsuperscript\{\textbackslash{}\textbackslash{}ddag\} & Check Average\textbackslash{}\textbackslash{}textsuperscript\{\textbackslash{}\textbackslash{}S\} & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average\\
+\midrule
+LMN09-119 & 51.37 (125.5\%) & 1 &  &  & 39.36 (87.4\%) & 18 &  &  & 18.01 (80.2\%) & 20 &  & \\
+\cmidrule{1-3}
+\cmidrule{6-7}
+\cmidrule{10-11}
+N18-1763 & 47.82 (116.8\%) & 2 &  &  & 39.45 (87.6\%) & 17 &  &  & 19.58 (87.2\%) & 18 &  & \\
+\cmidrule{1-3}
+\cmidrule{6-7}
+\cmidrule{10-11}
+N18-1855 & 47.52 (116.1\%) & 3 &  &  & 43.17 (95.8\%) & 10 &  &  & 20.6 (91.8\%) & 14 &  & \\
+\cmidrule{1-3}
+\cmidrule{6-7}
+\cmidrule{10-11}
+N18-1595 & 47.36 (115.7\%) & 4 &  &  & 43.52 (96.6\%) & 9 &  &  & 19.52 (86.9\%) & 19 &  & \\
+\cmidrule{1-3}
+\cmidrule{6-7}
+\cmidrule{10-11}
+Dunphy & 41.71 (101.9\%) & 18 &  &  & 47.33 (105.1\%) & 1 &  &  & 21.52 (95.9\%) & 4 &  & \\
+\cmidrule{1-3}
+\cmidrule{6-7}
+\cmidrule{10-11}
+Dilday & 41.22 (100.7\%) & 19 &  &  & 46.78 (103.8\%) & 2 &  &  & 22.33 (99.5\%) & 2 &  & \\
+\cmidrule{1-3}
+\cmidrule{6-7}
+\cmidrule{10-11}
+N18-1632-2 & 46.67 (114\%) & 5 &  &  & 46.34 (102.9\%) & 5 &  &  & 20.8 (92.7\%) & 11 &  & \\
+\cmidrule{1-3}
+\cmidrule{6-7}
+\cmidrule{10-11}
+N18-1632-1 & 46.64 (113.9\%) & 6 &  &  & 45.73 (101.5\%) & 6 &  &  & 20.76 (92.5\%) & 12 &  & \\
+\cmidrule{1-3}
+\cmidrule{6-7}
+\cmidrule{10-11}
+N18-1620 & 43.63 (106.6\%) & 15 &  &  & 46.54 (103.3\%) & 3 &  &  & 21.4 (95.3\%) & 6 &  & \\
+\cmidrule{1-3}
+\cmidrule{6-7}
+\cmidrule{10-11}
+N18-1635 & 43.61 (106.5\%) & 16 &  &  & 46.45 (103.1\%) & 4 &  &  & 21.72 (96.7\%) & 3 &  & \\
+\cmidrule{1-3}
+\cmidrule{6-7}
+\cmidrule{10-11}
+N09-09 & 46.31 (113.1\%) & 7 &  &  & 41.61 (92.4\%) & 14 &  &  & 19.77 (88.1\%) & 17 &  & \\
+\cmidrule{1-3}
+\cmidrule{6-7}
+\cmidrule{10-11}
+N18-1731 & 46.1 (112.6\%) & 8 &  &  & 43.16 (95.8\%) & 11 &  &  & 20.49 (91.3\%) & 15 &  & \\
+\cmidrule{1-3}
+\cmidrule{6-7}
+\cmidrule{10-11}
+N18-1674 & 45.19 (110.4\%) & 9 &  &  & 44.26 (98.2\%) & 7 &  &  & 21.21 (94.5\%) & 9 &  & \\
+\cmidrule{1-3}
+\cmidrule{6-7}
+\cmidrule{10-11}
+N18-1682 & 45.11 (110.2\%) & 10 &  &  & 43.64 (96.9\%) & 8 &  &  & 20.76 (92.5\%) & 13 &  & \\
+\cmidrule{1-3}
+\cmidrule{6-7}
+\cmidrule{10-11}
+N18-1572 & 45.08 (110.1\%) & 11 &  &  & 38.58 (85.6\%) & 19 &  &  & 21.19 (94.4\%) & 10 &  & \\
+\cmidrule{1-3}
+\cmidrule{6-7}
+\cmidrule{10-11}
+N18-1751 & 44.8 (109.4\%) & 12 &  &  & 41.59 (92.3\%) & 15 &  &  & 20.44 (91\%) & 16 &  & \\
+\cmidrule{1-3}
+\cmidrule{6-7}
+\cmidrule{10-11}
+N18-1956 & 44.55 (108.8\%) & 13 &  &  & 34.79 (77.2\%) & 20 &  &  & 21.51 (95.8\%) & 5 &  & \\
+\cmidrule{1-3}
+\cmidrule{6-7}
+\cmidrule{10-11}
+N18-1604 & 43.83 (107.1\%) & 14 &  &  & 43.15 (95.8\%) & 12 &  &  & 21.34 (95.1\%) & 8 &  & \\
+\cmidrule{1-3}
+\cmidrule{6-7}
+\cmidrule{10-11}
+N18-1641 & 43.33 (105.8\%) & 17 &  &  & 41.99 (93.2\%) & 13 &  &  & 21.36 (95.1\%) & 7 &  & \\
+\cmidrule{1-3}
+\cmidrule{6-7}
+\cmidrule{10-11}
+NC-Raleigh & 39.91 (97.5\%) & 20 & \multirow{-20}{*}{\centering\arraybackslash 45.09} & \multirow{-20}{*}{\centering\arraybackslash 40.94} & 41.04 (91.1\%) & 16 & \multirow{-20}{*}{\centering\arraybackslash 42.92} & \multirow{-20}{*}{\centering\arraybackslash 45.05} & 23.5 (104.7\%) & 1 & \multirow{-20}{*}{\centering\arraybackslash 20.89} & \multirow{-20}{*}{\centering\arraybackslash 22.45}\\
+\bottomrule
+\multicolumn{13}{l}{\rule{0pt}{1em}\textsuperscript{*} Observed marginal mean of the phenotype (value of the phenotype/check average * 100\%).}\\
+\multicolumn{13}{l}{\rule{0pt}{1em}\textsuperscript{\dag} Rank of the genotype within the particular phenotype.}\\
+\multicolumn{13}{l}{\rule{0pt}{1em}\textsuperscript{\ddag} The average value of the phenotype for all lines in the test.}\\
+\multicolumn{13}{l}{\rule{0pt}{1em}\textsuperscript{\S} The average value of the phenotype for the checks in the test.}\\
+\end{tabular}}
+\end{table}
 

### 2022-05-09 R/make_yield_summary_tables.R

@@ -1,0 +1,261 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param blue_data
+#' @param utility_tables
+#' @param lsd_data
+#' @param linear_means
+make_yield_summary_tables <- function(blue_data = genotype_BLUEs,
+                                      utility_tables = util_tables, lsd_data =
+                                      least_sig_differences, linear_means =
+                                      linear_means, 
+                                      summary_phenos = c("yield", "protein", "oil")) {
+
+  # A function to get the minimum significant difference from the lsd results list
+  get_msd <- function(fit_model){
+    msd <- fit_model %>% 
+      pluck("hsd") %>% 
+      pluck("statistics") %>% 
+      pluck("MSD")
+    
+    if(is.null(msd)){
+      msd <- NA
+    }
+    
+    msd <- round(msd, 2)
+    
+    return(msd)
+  }
+  
+  # A helper function for identifying the column indices of some phenotype
+  # when multiple variables are recorded for multiple phenotypes. The specific
+  # issue this function resolves is overlaps in matches for oil/protein with
+  # oil_plus_protein
+  get_pheno_indices <- function(column_names, pheno_name, name_conversion = utility_tables$trait_shortnames){
+    
+    # Get all the string matches and then exclude protein_plus_oil if the pheno_name
+    # is either protein or oil
+    all_matches <- str_detect(column_names, pheno_name)
+    
+    if(pheno_name %in% c("protein", "oil")){
+      p_o_matches <- str_detect(column_names, "protein_plus_oil")
+      final_matches <- (all_matches & !p_o_matches) %>% 
+        which()
+    }else{
+      final_matches <- which(all_matches)
+    }
+    
+    # Get cleaned up names for the column indices
+    return(final_matches)
+  }
+  
+  
+  # A function that takes the phenotype BLUEs table and calculates some summary
+  # information for each phenotype: 
+  #
+  # 1. The overall test average, 
+  # 2. The average for the checks
+  # 3. The rank of each genotype
+  make_pheno_comparison <- function(test_data, keep_phenos = summary_phenos){
+    
+    genotype_ranks <- test_data %>% 
+      pivot_longer(cols = utility_tables$trait_shortnames$name, 
+                   names_to = "pheno") %>% 
+      group_by(pheno) %>% 
+      arrange(desc(value)) %>% 
+      mutate(rank = 1:n()) %>% 
+      ungroup() %>%
[…]

### 2022-05-09 _targets.R

@@ -174,6 +174,13 @@ tar_plan(
   tar_target(anova_tables, 
              make_anova_tables(anova_data = anova_two_years)),
 
+tar_target(yield_summary_tables, 
+           make_yield_summary_tables(blue_data = genotype_BLUEs, 
+                                     utility_tables = util_tables, 
+                                     lsd_data = least_sig_differences, 
+                                     linear_means = linear_means, 
+                                     summary_phenos = c("yield", "protein", "oil"))),
+
   
   ## Section: Writeup documents
   ##################################################

### 2022-05-10 doc/manuscript/manuscript.tex
Added to the step that makes heatmaps for phenotype average values across environments

@@
 \cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9} \cmidrule(l{3pt}r{3pt}){10-13}
-Genotype & Value \textbackslash{}textsuperscript\{*\} & Rank\textbackslash{}\textbackslash{}textsuperscript\{\textbackslash{}\textbackslash{}dag\} & Test Average\textbackslash{}\textbackslash{}textsuperscript\{\textbackslash{}\textbackslash{}ddag\} & Check Average\textbackslash{}\textbackslash{}textsuperscript\{\textbackslash{}\textbackslash{}S\} & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average\\
+Genotype & Value\textbackslash{}textsuperscript\{*\} & Rank\textbackslash{}\textbackslash{}textsuperscript\{\textbackslash{}\textbackslash{}dag\} & Test Average\textbackslash{}\textbackslash{}textsuperscript\{\textbackslash{}\textbackslash{}ddag\} & Check Average\textbackslash{}\textbackslash{}textsuperscript\{\textbackslash{}\textbackslash{}S\} & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average\\
 \midrule

### 2022-05-10 R/make_genotype_blue_plots.R

@@ -4,7 +4,7 @@
 #'
 #' @title
 #' @param fit_models
-make_genotype_blue_plots <- function(fit_models = mixed_models_two_years, all_data = all_yield_data$two_year) {
+make_genotype_blue_plots <- function(fit_models = mixed_models_two_years, all_data = all_yield_data$two_year, util_tables) {
 
   
   # A function to relevel the environment factor variable in the yield data
@@ -14,20 +14,92 @@ make_genotype_blue_plots <- function(fit_models = mixed_models_two_years, all_da
       mutate(ENV = fct_relevel(ENV, 'CLA - 2020', 'CAS - 2020', 'CAS - 2021', 'PLY - 2021'), 
              genotype = fct_reorder(genotype, yield, .fun = mean, na.rm = TRUE)) %>% 
       rename(Genotype = genotype, 
-             Environment = ENV, 
-             Yield = yield)
+             Environment = ENV)
   }
   
   all_data <- map(all_data, reorder_environment)
   
+  # Get the minimum and maximum yield to set a common scale limit to both plots
+  combined_data <- all_data %>% 
+    reduce(bind_rows)
+  
+  yield_range <- range(combined_data$yield, na.rm = TRUE)
+  
+  yield_scale_min <- yield_range[[1]] - 5
+  yield_scale_max <- yield_range[[2]] + 5
+  
   # A genotype by environment plot for yield
-  test_1_yield <- ge_plot(pluck(all_data, "Jay Test 1"), env = Environment, gen = Genotype, resp = Yield)
-  test_2_yield <- ge_plot(pluck(all_data, "Jay Test 2"), env = Environment, gen = Genotype, resp = Yield)
+  test_1_yield <- ge_plot(pluck(all_data, "Jay Test 1"), env = Environment, gen = Genotype, resp = yield) + 
+    scale_fill_viridis_c(limits = c(yield_scale_min, yield_scale_max))
+  
+  test_2_yield <- ge_plot(pluck(all_data, "Jay Test 2"), env = Environment, gen = Genotype, resp = yield) + 
+    scale_fill_viridis_c(limits = c(yield_scale_min, yield_scale_max))
   
   both_test_plots <- arrange_ggplot(test_1_yield, test_2_yield, 
-                                    tag_levels = list(c("Test 1", "Test 2")))
+                                    tag_levels      = list(c("Test 1", "Test 2")), 
+                                    guides          = "collect", 
+                                    legend.position = "right")
   
-  res <- list("ge_plot" = both_test_plots)
[…]

### 2022-05-10 R/make_phenotype_scatterplots.R

@@ -1,0 +1,135 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param mixed_models_two_years
+#' @param util_tables
+make_phenotype_scatterplots <- function(mixed_models_two_years, util_tables, phenos = c("protein", "oil", "yield")) {
+
+  # A function to get the marginal means from the model component of the 
+  # mixed models output
+  get_mar_means <- function(test_data, pheno_names = names(test_data)){
+    
+    one_pheno_means <- function(pheno_model, pheno_name){
+      pheno_model %>% 
+        pluck("modellme") %>% 
+        emmeans("GEN") %>% 
+        as_tibble() %>% 
+        mutate(pheno_name = pheno_name) %>% 
+        relocate(pheno_name, .after = "GEN")
+    }
+    
+    map2(test_data, pheno_names, one_pheno_means) %>% 
+      reduce(bind_rows)
+    
+  }
+  
+  # use the function to get the marginal means for both tests and then get the 
+  # output from just the first test
+  all_means <- map(mixed_models_two_years, get_mar_means)
+  
+  # A function to make a table of marginal means with genotypes labelled 
+  # according to if they had phenotype values greater than or less than 
+  # the average value of the checks
+  make_se_table <- function(test_data, test_name){
+    
+    # Get the marginal means for just the checks and get the average value for
+    # each phenotype
+    check_means <- test_data %>% 
+      dplyr::filter(GEN %in% util_tables$yield_checks$genotype) %>% 
+      group_by(pheno_name) %>% 
+      summarise(check_avg = mean(emmean))
+    
+    # Add a column to the test marginal means to indicate if the value for a phenotype is
+    # above the average of the checks
+    se_table <- left_join(test_data, check_means, by = "pheno_name") %>% 
+      mutate(above_avg = ifelse(emmean > check_avg, "Above check average", "Below check average")) %>% 
+      select(GEN, pheno_name, emmean, SE, above_avg, check_avg) %>% 
+      mutate(test_name = test_name) %>% 
+      relocate(test_name, .before = GEN)
+    
+    return(se_table)
+  }
+  
+  # Apply this function to the means list to get a list of means tables
+  # that are ready for ggplot
+  all_se_tables <- map2(all_means, names(all_means), make_se_table)
+  
+  # A function to make a dotplot with error bars for some given trait
[…]

### 2022-05-10 R/make_yield_summary_tables.R

@@ -230,7 +230,7 @@ make_yield_summary_tables <- function(blue_data = genotype_BLUEs,
     
     table_caption <- paste("Marginal means and rankings of genotypes in", test_name, "for seed yield, seed oil, and seed protein.")
     
-    names(current_table)[2] <- paste(names(current_table)[2], 
+    names(current_table)[2] <- paste0(names(current_table)[2], 
                                       footnote_marker_symbol(1, format = "latex"))
     
     names(current_table)[3] <- paste0(names(current_table)[3], 

### 2022-05-10 _targets.R

@@ -159,7 +159,7 @@ tar_plan(
   
   # Plots of the genotype blues
   tar_target(BLUE_plots_two_years, 
-             make_genotype_blue_plots(fit_models = mixed_models_two_years, all_data = all_yield_data$two_year)),
+             make_genotype_blue_plots(fit_models = mixed_models_two_years, all_data = all_yield_data$two_year, util_tables)),
   
 # A example latex table to use for testing targets with the manuscript template
   tar_target(example_table, 
@@ -173,6 +173,11 @@ tar_plan(
   # Cleaner ANOVA tables
   tar_target(anova_tables, 
              make_anova_tables(anova_data = anova_two_years)),
+
+  # Scatterplots to show phenotype marginal means and the standard errors on those
+  # means 
+tar_target(phenotype_scatterplots, 
+           make_phenotype_scatterplots(mixed_models_two_years, util_tables)),
 
 tar_target(yield_summary_tables, 
            make_yield_summary_tables(blue_data = genotype_BLUEs, 

### 2022-05-10 sandbox/emmean SE plot.R

@@ -29,7 +29,7 @@ get_mar_means <- function(test_data, pheno_names = names(test_data)){
 # use the function to get the marginal means for both tests and then get the 
 # output from just the first test
 all_means <- map(mixed_models_two_years, get_mar_means)
-one_test  <- all_means$`Jay Test 1`
+one_test  <- all_means$`Jay Test 2`
 
 # Get the marginal means for just the checks and get the average value for
 # each phenotype
@@ -42,8 +42,7 @@ check_means <- one_test %>%
 # above the average of the checks
 se_table <- left_join(one_test, check_means, by = "pheno_name") %>% 
   mutate(above_avg = ifelse(emmean > check_avg, "Above check average", "Below check average")) %>% 
-  select(GEN, pheno_name, emmean, SE, above_avg) %>% 
-  dplyr::filter(pheno_name == "yield")
+  select(GEN, pheno_name, emmean, SE, above_avg, check_avg)
 
 
 ggplot(se_table, aes(x = emmean, y = reorder(GEN, emmean), fill = above_avg)) + 
@@ -53,4 +52,37 @@ ggplot(se_table, aes(x = emmean, y = reorder(GEN, emmean), fill = above_avg)) +
   ylab("Genotype") + 
   xlab("Yield (bu/acre)") + 
   theme(legend.title = element_blank())
+
+# A function to make a dotplot with error bars for some given trait
+make_pheno_dotplot <- function(emmean_data = se_table, pheno = "yield", pheno_lookup = util_tables$trait_lookup){
+  
+  # Filter the full marginal mean data to just the data for the chosen phenotype
+  pheno_data <- emmean_data %>% 
+    dplyr::filter(pheno_name == pheno)
+  
+  # Get the longer name for the phenotype from the phenotype name utility table
+  pheno_longname <- match_from_table(pheno, pheno_lookup)
+  
+  # The average value of the checks for the given phenotype
+  pheno_check_avg <- unique(pheno_data$check_avg)
+  
+  # Make a dotplot with errorbars to intidate the standard error 
+  p <- ggplot(pheno_data, aes(x = emmean, y = reorder(GEN, emmean), fill = above_avg)) + 
+    geom_point(shape = 21, size = 3.5) + 
+    geom_errorbarh(aes(xmax = emmean + SE, xmin = emmean - SE)) + 
+    theme_hc() + 
+    ylab("Genotype") + 
[…]

### 2022-05-10 sandbox/histogram development.R

@@ -64,8 +64,6 @@ labelled_histogram <- function(blue_data, test_colors, trait_name, check_genotyp
     geom_vline(xintercept = CheckAvg, linetype = 'dotted', colour = 'black', size = 1.25) + 
     geom_vline(xintercept = TestAvg, linetype = 2, colour = 'red', size = 1.25)
   
-  
-  
   # Get data for the other genotypes to label
   LabelGenotypes <- blue_data %>% dplyr::filter(genotype %in% label_genotypes)
   LabelGenotypes <- LabelGenotypes[, c("genotype", trait_name)]
@@ -136,34 +134,65 @@ labelled_histogram <- function(blue_data, test_colors, trait_name, check_genotyp
 # publication ready names
 match_from_table("md", util_tables$trait_lookup)
 
+# A function to make a patchwork plot with protein, oil, and yield
+make_patchwork_plot <- function(means_data, label_genos){
+  
+  # Make plots for oil, protein, and yield with the genotypes labelled
+  test_oil <- labelled_histogram(means_data, 
+                                   test_colors       = test_name_colors, 
+                                   trait_name        = "oil", 
+                                   check_genotypes   = util_tables$check_table, 
+                                   trait_name_lookup = util_tables$trait_lookup, 
+                                   label_genotypes   = label_genos)
+  
+  test_pro <- labelled_histogram(means_data, 
+                                   test_colors       = test_name_colors, 
+                                   trait_name        = "protein", 
+                                   check_genotypes   = util_tables$check_table, 
+                                   trait_name_lookup = util_tables$trait_lookup, 
+                                   label_genotypes   = label_genos)
+  
+  test_yield <- labelled_histogram(means_data, 
+                                     test_colors       = test_name_colors, 
+                                     trait_name        = "yield", 
+                                     check_genotypes   = util_tables$check_table, 
+                                     trait_name_lookup = util_tables$trait_lookup, 
+                                     label_genotypes   = label_genos)
+  
+  # Patchwork of the three plots with protein and oil on top and yield on the bottom
+  p <- (test_oil | test_pro)/(test_yield)
+  
+  return(p)
+}
 
-test_1_oil <- labelled_histogram(linear_means$`Jay Test 1`, 
+
+test_1_oil <- labelled_histogram(linear_means$`Jay Test 2`, 
                                  test_colors       = test_name_colors, 
                                  trait_name        = "oil", 
                                  check_genotypes   = util_tables$check_table, 
[…]

### 2022-05-10 _targets.R
Added a function to export the labelled histograms for each test

@@ -186,10 +186,18 @@ tar_plan(
                                        linear_means = linear_means, 
                                        summary_phenos = c("yield", "protein", "oil"))),
 
+tar_target(labelled_test_histograms, 
+           make_test_histograms(geno_means = genotype_BLUEs$BLUEs, 
+                                util_tables, 
+                                test_name_colors, 
+                                test_1_genos = c("N18-1632-2", "N18-1635", "N18-1855", "N18-1620", "N18-1674"), 
+                                test_2_genos = c("N18-1615", "N18-1796", "N18-1579", "N18-1586", "N18-1761"))),
+
   # Export plots 
   tar_target(phenotype_summary_plots, 
              export_phenotype_plots(BLUE_plots_two_years, 
                                     phenotype_scatterplots, 
+                                    labelled_test_histograms,
                                     export_dir = here("exports", "plots")), 
              format = "file"),
 

### 2022-05-10 doc/manuscript/manuscript.Rmd
Cleaned up the targets file a bit and saved some small changes to the main manuscript document

@@
 
-Multiple RILs in each test were identified with yield comparable to, or superior to that of the check cultivars included in each test.
+Several RILs in each of the tests had yield that was comparable to that of their check cultivars.
+This was determined both quanititatively through the use of contrasts between the mean of each RIL with the average of the yield check means, and qualitatively by inspecting the standard errors on the estimation of the genotype marginal means for yield.
+Among these genotypes with yield comparable to that of the check cultivars were several genotypes with
 

### 2022-05-10 R/custom_ggplot_themes.R

@@ -5,7 +5,7 @@
 ## Author: Jay Gillenwater
 ##################################################
 
-theme_jay_yield_base <- function(){
+theme_jay_yield_base <- function(base_size = 12, base_family=""){
   theme(axis.text = element_text(size = 12), 
         axis.title = element_text(size = 14))
 }

### 2022-05-10 _targets.R

@@ -137,12 +137,12 @@ tar_plan(
   # Conrasts of RIL means vs check means
   tar_target(genotype_contrasts_anova, 
              make_contrast_tibble(anova_two_years, 
-                                  model_type = "linear", 
+                                  model_type  = "linear", 
                                   check_genos = util_tables$yield_checks)), 
   
   tar_target(genotype_contrasts_mixed, 
              make_contrast_tibble(mixed_models_two_years,
-                                  model_type = "mixed", 
+                                  model_type  = "mixed", 
                                   check_genos = util_tables$yield_checks)),
   
   
@@ -159,7 +159,9 @@ tar_plan(
   
   # Plots of the genotype blues
   tar_target(BLUE_plots_two_years, 
-             make_genotype_blue_plots(fit_models = mixed_models_two_years, all_data = all_yield_data$two_year, util_tables)),
+             make_genotype_blue_plots(fit_models = mixed_models_two_years, 
+                                      all_data   = all_yield_data$two_year, 
+                                      util_tables)),
   
 # A example latex table to use for testing targets with the manuscript template
   tar_target(example_table, 
@@ -167,7 +169,9 @@ tar_plan(
   
   # A example plot to use for testing manuscript markdown rendering
   tar_target(example_plot, 
-             make_example_plot(all_yield_data, test_name_colors, dir = here("exports", "plots", "example_plot.pdf")), 
+             make_example_plot(all_yield_data, 
+                               test_name_colors, 
+                               dir = here("exports", "plots", "example_plot.pdf")), 
              format = "file"),
 
   # Cleaner ANOVA tables
@@ -179,19 +183,21 @@ tar_plan(
   tar_target(phenotype_scatterplots, 
              make_phenotype_scatterplots(mixed_models_two_years, util_tables)),
 
+  # Latex tables of summary data for the yield marginal means
   tar_target(yield_summary_tables, 
-             make_yield_summary_tables(blue_data = genotype_BLUEs, 
+             make_yield_summary_tables(blue_data      = genotype_BLUEs, 
                                        utility_tables = util_tables, 
-                                       lsd_data = least_sig_differences, 
-                                       linear_means = linear_means, 
+                                       lsd_data       = least_sig_differences, 
+                                       linear_means   = linear_means, 
                                        summary_phenos = c("yield", "protein", "oil"))),
-
-tar_target(labelled_test_histograms, 
[…]

### 2022-05-10 sandbox/contrast filtering.R

@@ -1,0 +1,34 @@
+##################################################
+## Project: Jay Yield
+## Script purpose: Exploring the mixed model contrasts to identify genotypes
+## with similar/superior yield, protein, and oil when compared to the checks
+## Date: 2022-05-10
+## Author: Jay Gillenwater
+##################################################
+
+# Setting up environment
+source("./packages.R")
+tar_make()
+
+tar_load(genotype_contrasts_mixed)
+
+all_contrasts <- genotype_contrasts_mixed %>% 
+  dplyr::filter(pheno %in% c("oil", "protein", "yield")) %>% 
+  mutate(contrasts = map(contrasts, as_tibble)) %>% 
+  select(test_name, pheno, contrasts) %>% 
+  unnest(contrasts) %>% 
+  group_by(test_name, pheno) %>% 
+  mutate(estimate_scaled = as.numeric(scale(estimate))) %>% 
+  arrange(test_name, contrast, pheno)
+
+scaled_estimates <- all_contrasts %>% 
+  group_by(test_name, contrast) %>% 
+  summarise(avg_scaled_estimate = mean(estimate_scaled))
+  
+
+all_contrasts_summary <- left_join(all_contrasts, scaled_estimates, by = c("test_name", "contrast"))
+
+
+all_contrasts_summary %>% 
+  arrange(test_name, desc(avg_scaled_estimate)) %>% 
+  View()

### 2022-05-10 sandbox/waas models.R

@@ -1,0 +1,33 @@
+##################################################
+## Project: Jay Yield
+## Script purpose: Testing out the multi-trait indexes from metan
+## Date: 2022-05-09
+## Author: Jay Gillenwater
+##################################################
+
+source("./packages.R")
+tar_make()
+
+tar_load(c(all_yield_data, genotype_contrasts_mixed))
+
+fit_waas <- function(yield_data, si = 20){
+  
+  waas_mod <- waasb(yield_data, 
+                    env = ENV, 
+                    gen = genotype, 
+                    rep = rep, 
+                    resp = c(oil, protein, yield, lod), 
+                    mresp = c("h", "h", "h", "l"), 
+                    wresp = c(25, 25, 100, 5))
+
+  mtsi(waas_mod, SI = si) %>% 
+    plot()
+  
+  
+}
+
+
+x11()
+fit_waas(all_yield_data$two_year$`Jay Test 1`, si = 50)
+x11()
+fit_waas(all_yield_data$two_year$`Jay Test 2`, si = 50)

### 2022-05-10 sandbox/yield summary tables.R

@@ -8,10 +8,13 @@
 
 
 # Load in the BLUEs, utility tables, and MSDs
-tar_load(genotype_BLUEs)
-tar_load(util_tables)
-tar_load(least_sig_differences)
-tar_load(linear_means)
+source("./packages.R")
+tar_make()
+
+tar_load(c(genotype_BLUEs, 
+           util_tables, 
+           least_sig_differences, 
+           linear_means))
 
 # A function to get the minimum significant difference from the lsd results list
 get_msd <- function(fit_model){
@@ -75,7 +78,7 @@ make_pheno_comparison <- function(test_data, keep_phenos = c("yield", "protein",
            test_avg = round(test_avg, 2))
   
   check_pheno_avg <- test_data %>% 
-    dplyr::filter(genotype %in% util_tables$check_table$genotype) %>% 
+    dplyr::filter(genotype %in% util_tables$yield_checks$genotype) %>% 
     pivot_longer(cols = util_tables$trait_shortnames$name, 
                  names_to = "pheno") %>% 
     group_by(pheno) %>% 
@@ -143,7 +146,7 @@ full_comparison_long <- function(blue_data, lsd_data, keep_phenos = c("yield", "
 }
 
 # Testing the functions together
-comparison_tables <- full_comparison_table(blue_data = linear_means, least_sig_differences)
+comparison_tables <- full_comparison_table(blue_data = genotype_BLUEs$BLUEs, least_sig_differences)
 
 # TODO:
 # Need to make a function that takes this data and converts it to a more 
@@ -264,11 +267,11 @@ make_phenotype_comparison_table <- function(comparison_table_output, pheno_names
   }
   
   
-  knitr::kable(current_table, "html") %>% 
+  knitr::kable(current_table, "latex") %>% 
     kable_classic() %>% 
     collapse_rows(columns = collapse_indices) %>%
     add_header_above(column_groups)
   
 }
 
-make_phenotype_comparison_table(comparison_tables$`Jay Test 1`, keep_msd = FALSE)
+make_phenotype_comparison_table(comparison_tables$`Jay Test 2`, keep_msd = FALSE)

### 2022-05-13 doc/manuscript/manuscript.tex
Small updates to the contrast filtering and labelled histogram functions

@@
 
-Multiple RILs in each test were identified with yield comparable to, or
-superior to that of the check cultivars included in each test.
+Several RILs in each of the tests had yield that was comparable to that
+of their check cultivars. This was determined both quanititatively
+through the use of contrasts between the mean of each RIL with the
+average of the yield check means, and qualitatively by inspecting the
+standard errors on the estimation of the genotype marginal means for
+yield. Among these genotypes with yield comparable to that of the check
+cultivars were several genotypes with
 
@@
 \centering
-\includegraphics[width=10 cm]{C:/Users/jhgille2/Documents/R/projects/Jay_yield/exports/plots/example_plot.pdf}
+\includegraphics[width=10 cm]{C:/Users/Jay/Desktop/Documents/R/Jay_yield/exports/plots/example_plot.pdf}
 \caption{This is a figure, Schemes follow the same formatting.

### 2022-05-13 sandbox/contrast filtering.R

@@ -28,6 +28,49 @@ scaled_estimates <- all_contrasts %>%
 
 all_contrasts_summary <- left_join(all_contrasts, scaled_estimates, by = c("test_name", "contrast"))
 
+# A function that returns a character string to indicate if an observation has a phenotypic value comparable
+# to or greater than that of the check average
+comparable_pheno <- function(test_name, contrast, pheno, estimate, p.value){
+  
+  if(p.value < 0.05){
+    if(estimate > 0){
+      res <- switch(pheno, 
+                    "oil"     = "HO",
+                    "protein" = "HP", 
+                    "yield"   = "HY")
+    }else{ 
+      res <- switch(pheno, 
+                    "oil"     = "LO",
+                    "protein" = "LP", 
+                    "yield"   = "LY")
+      }
+  }else{
+    res <- switch(pheno, 
+                  "oil"     = "SO",
+                  "protein" = "SP", 
+                  "yield"   = "SY")
+  }
+  
+  return(res)
+}
+
+
+find_elites <- function(contrast, test_name, oil, protein, yield){
+  
+  res <- ifelse(oil == "SO" & protein == "HP" & yield == 'SY', "yes", "no")
+
+  return(res)  
+}
+
+pheno_categories <- all_contrasts %>% 
+  ungroup() %>% 
+  select(test_name, contrast, pheno, estimate, p.value) %>% 
+  mutate(pheno_group = pmap_chr(., comparable_pheno), 
+         contrast = str_remove(contrast, " - Checks")) %>% 
+  {. ->> pheno_categories_full } %>%
+  pivot_wider(names_from = pheno, values_from = pheno_group, id_cols = c(contrast, test_name)) %>% 
+  mutate(elite_geno = pmap_chr(., find_elites))
+
 
 all_contrasts_summary %>% 
   arrange(test_name, desc(avg_scaled_estimate)) %>% 

### 2022-05-13 sandbox/histogram development.R

@@ -166,6 +166,13 @@ make_patchwork_plot <- function(means_data, label_genos){
 }
 
 
+make_patchwork_plot(genotype_BLUEs$BLUEs$`Jay Test 1`, label_genos = c("N18-1632-1", 
+                                                                       "N18-1595"))
+
+make_patchwork_plot(genotype_BLUEs$BLUEs$`Jay Test 2`, label_genos = c("N18-1761", 
+                                                                       "N18-1577", 
+                                                                       "N18-1796"))
+
 test_1_oil <- labelled_histogram(linear_means$`Jay Test 2`, 
                                  test_colors       = test_name_colors, 
                                  trait_name        = "oil", 

### 2022-05-31 doc/manuscript/manuscript.Rmd
Added to the manuscript document. Also made some changes to the summary tables and added a step to make summary tables for smaller selections of genotypes.

@@
 tar_load(c(example_table, 
-           yield_summary_tables))
+           yield_summary_tables, 
+           elite_genotype_tables))
 ```
@@
 To meet this goal, two recombinant inbred line (RIL) oil mapping populations were screened for lines which showed promising combinations of yield and seed composition traits.
-Successive rounds of selection were conducted to identify and characterize lines with high values for yield as well as protein and oil composition were performed between 2018 and 2021 to identify soybean lines with elevated yield as well as the valuable seed composition traits when compared with existing check cultivars.
+Successive rounds of selection were conducted to identify and characterize lines with high values for yield as well as protein and oil composition were performed between 2018 and 2021 to identify soybean lines with yield comparable to existing check cultivars and protein and or oil composition superior to that of the check cultivars.
 
@@
 Least-square means (LS Means) for each genotype and trait were calculated using the above model using the emmeans package[@lenthEmmeansEstimatedMarginal2022] in R.
-The emmeans package was also used to calculate contrasts as a post-hoc test to compare RIL means to check means.
+The emmeans package was also used to calculate contrasts as a post-hoc test to compare RIL phenotype means to check means.
 Pearson correlation coefficients between each phenotype were calculated and visualized with the metan package.
@@
 This was determined both quanititatively through the use of contrasts between the mean of each RIL with the average of the yield check means, and qualitatively by inspecting the standard errors on the estimation of the genotype marginal means for yield.
-Among these genotypes with yield comparable to that of the check cultivars were several genotypes with
+No genotypes had yield that was quantitatively higher than that of the yield checks, however many had comparable yield.
+Many of these genotypes with comparable yield also had protein content that was superior to the check average in each test.
+No genotypes had oil that was superior to the check cultivars, but some had comparable yield and oil content as well as superior protein content.
+These genotypes with comparable yield and superior protein also had desirable agronomic qualities such as low lodging and good seed quality which would make them ideal candidates for future breeding material.
 
-```{r test1_summary_table, results = "asis", echo = FALSE}
+## Genotypes with omparable yield and oil and superior protein
+Four genotypes had yield and oil that was similar to that of the yield checks, and seed protein that was greater than the average of the checks.
+These genotypes are N18-1635 from Test 1 and genotypes N18-1627, N18-1643, and N18-1783 from Test 2.
 
-print(yield_summary_tables$`Jay Test 1`)
+```{r elite_geno_table, results = "asis", echo = FALSE}
+
+print(elite_genotype_tables$elite_genos)
+
+```
+
+```{r high_po_table, results = "asis", echo = FALSE}
+
+print(elite_genotype_tables$po_top_ten)
 

### 2022-05-31 doc/manuscript/manuscript.tex
Added to the manuscript document. Also made some changes to the summary tables and added a step to make summary tables for smaller selections of genotypes.

@@
 yield as well as protein and oil composition were performed between 2018
-and 2021 to identify soybean lines with elevated yield as well as the
-valuable seed composition traits when compared with existing check
-cultivars.
+and 2021 to identify soybean lines with yield comparable to existing
+check cultivars and protein and or oil composition superior to that of
+the check cultivars.
 
@@
 package was also used to calculate contrasts as a post-hoc test to
-compare RIL means to check means. Pearson correlation coefficients
-between each phenotype were calculated and visualized with the metan
-package.
+compare RIL phenotype means to check means. Pearson correlation
+coefficients between each phenotype were calculated and visualized with
+the metan package.
 
@@
 standard errors on the estimation of the genotype marginal means for
-yield. Among these genotypes with yield comparable to that of the check
-cultivars were several genotypes with
+yield. No genotypes had yield that was quantitatively higher than that
+of the yield checks, however many had comparable yield. Many of these
+genotypes with comparable yield also had protein content that was
+superior to the check average in each test. No genotypes had oil that
+was superior to the check cultivars, but some had comparable yield and
+oil content as well as superior protein content. These genotypes with
+comparable yield and superior protein also had desirable agronomic
+qualities such as low lodging and good seed quality which would make
+them ideal candidates for future breeding material.
 
-\begin{table}
+\hypertarget{genotypes-with-omparable-yield-and-oil-and-superior-protein}{%
+\subsection{Genotypes with omparable yield and oil and superior
+protein}\label{genotypes-with-omparable-yield-and-oil-and-superior-protein}}
 
-\caption{Marginal means and rankings of genotypes in Jay Test 1 for seed yield, seed oil, and seed protein.}
+Four genotypes had yield and oil that was similar to that of the yield
+checks, and seed protein that was greater than the average of the
+checks. These genotypes are N18-1635 from Test 1 and genotypes N18-1627,
+N18-1643, and N18-1783 from Test 2.
+
+\begin{table}[H]
+
+\caption{Soybean genotypes with yield and seed oil comparable to check cultivars, and seed protein superior to check cultivars.}
 \centering
 \resizebox{\linewidth}{!}{
-\begin{tabular}[t]{ccccccccccccc}
+\begin{tabular}[t]{llrlllrll}
 \toprule
-\multicolumn{1}{c}{} & \multicolumn{4}{c}{Protein} & \multicolumn{4}{c}{Yield} & \multicolumn{4}{c}{Oil} \\
-\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9} \cmidrule(l{3pt}r{3pt}){10-13}
-Genotype & Value\textbackslash{}textsuperscript\{*\} & Rank\textbackslash{}\textbackslash{}textsuperscript\{\textbackslash{}\textbackslash{}dag\} & Test Average\textbackslash{}\textbackslash{}textsuperscript\{\textbackslash{}\textbackslash{}ddag\} & Check Average\textbackslash{}\textbackslash{}textsuperscript\{\textbackslash{}\textbackslash{}S\} & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average\\
+\multicolumn{1}{c}{} & \multicolumn{4}{c}{Protein + Oil} & \multicolumn{4}{c}{Yield} \\
+\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
+Genotype & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average\\
 \midrule
-LMN09-119 & 51.37 (125.5\%) & 1 &  &  & 39.36 (87.4\%) & 18 &  &  & 18.01 (80.2\%) & 20 &  & \\
+N18-1635 & 65.32 (103\%) & 13 & 65.98 & 63.39 & 46.45 (103.1\%) & 4 & 42.92 & 45.05\\
+\cmidrule{1-9}
+N18-1783 & 67.38 (105.1\%) & 8 &  &  & 37.63 (86.6\%) & 19 &  & \\
 \cmidrule{1-3}
 \cmidrule{6-7}
-\cmidrule{10-11}
-N18-1763 & 47.82 (116.8\%) & 2 &  &  & 39.45 (87.6\%) & 17 &  &  & 19.58 (87.2\%) & 18 &  & \\
+N18-1627 & 66.52 (103.7\%) & 10 &  &  & 46.01 (105.9\%) & 8 &  & \\
 \cmidrule{1-3}
 \cmidrule{6-7}
-\cmidrule{10-11}
-N18-1855 & 47.52 (116.1\%) & 3 &  &  & 43.17 (95.8\%) & 10 &  &  & 20.6 (91.8\%) & 14 &  & \\
+N18-1643 & 65.8 (102.6\%) & 13 & \multirow{-3}{*}{\raggedright\arraybackslash 66.4} & \multirow{-3}{*}{\raggedright\arraybackslash 64.14} & 40.54 (93.3\%) & 16 & \multirow{-3}{*}{\raggedright\arraybackslash 43.65} & \multirow{-3}{*}{\raggedright\arraybackslash 43.44}\\
+\bottomrule
+\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{*} The genotype name.}\\
+\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\dag} The genotype marginal mean for the phenotype (value divided by check average).}\\
+\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\ddag} The ranking of this genotype for the phenotype within its test.}\\
+\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\S} The average phenotype value for all genotypes in the test.}\\
+\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\P} The average value of the checks in the test.}\\
+\end{tabular}}
+\end{table}
+
+\begin{table}[H]
+
+\caption{Top 10 soybean genotypes on the basis of protein plus oil content.}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}[t]{llrlllrll}
+\toprule
+\multicolumn{1}{c}{} & \multicolumn{4}{c}{Protein + Oil} & \multicolumn{4}{c}{Yield} \\
+\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
+Genotype & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average\\
+\midrule
+N18-1855 & 68.13 (107.5\%) & 2 &  &  & 43.17 (95.8\%) & 10 &  & \\
 \cmidrule{1-3}
 \cmidrule{6-7}
-\cmidrule{10-11}
-N18-1595 & 47.36 (115.7\%) & 4 &  &  & 43.52 (96.6\%) & 9 &  &  & 19.52 (86.9\%) & 19 &  & \\
+N18-1632-2 & 67.47 (106.4\%) & 3 &  &  & 46.34 (102.9\%) & 5 &  & \\
 \cmidrule{1-3}
 \cmidrule{6-7}
-\cmidrule{10-11}
-Dunphy & 41.71 (101.9\%) & 18 &  &  & 47.33 (105.1\%) & 1 &  &  & 21.52 (95.9\%) & 4 &  & \\
+N18-1763 & 67.4 (106.3\%) & 5 &  &  & 39.45 (87.6\%) & 17 &  & \\
 \cmidrule{1-3}
 \cmidrule{6-7}
-\cmidrule{10-11}
-Dilday & 41.22 (100.7\%) & 19 &  &  & 46.78 (103.8\%) & 2 &  &  & 22.33 (99.5\%) & 2 &  & \\
+N18-1595 & 66.87 (105.5\%) & 6 &  &  & 43.52 (96.6\%) & 9 &  & \\
 \cmidrule{1-3}
 \cmidrule{6-7}
-\cmidrule{10-11}
-N18-1632-2 & 46.67 (114\%) & 5 &  &  & 46.34 (102.9\%) & 5 &  &  & 20.8 (92.7\%) & 11 &  & \\
+N18-1731 & 66.59 (105\%) & 7 &  &  & 43.16 (95.8\%) & 11 &  & \\
 \cmidrule{1-3}
 \cmidrule{6-7}
-\cmidrule{10-11}
-N18-1632-1 & 46.64 (113.9\%) & 6 &  &  & 45.73 (101.5\%) & 6 &  &  & 20.76 (92.5\%) & 12 &  & \\
+N18-1674 & 66.4 (104.7\%) & 8 & \multirow{-6}{*}{\raggedright\arraybackslash 65.98} & \multirow{-6}{*}{\raggedright\arraybackslash 63.39} & 44.26 (98.2\%) & 7 & \multirow{-6}{*}{\raggedright\arraybackslash 42.92} & \multirow{-6}{*}{\raggedright\arraybackslash 45.05}\\
+\cmidrule{1-9}
+N18-1575 & 69.04 (107.6\%) & 1 &  &  & 42.49 (97.8\%) & 12 &  & \\
 \cmidrule{1-3}
 \cmidrule{6-7}
-\cmidrule{10-11}
-N18-1620 & 43.63 (106.6\%) & 15 &  &  & 46.54 (103.3\%) & 3 &  &  & 21.4 (95.3\%) & 6 &  & \\
+N18-1761 & 68.48 (106.8\%) & 3 &  &  & 45.74 (105.3\%) & 9 &  & \\
 \cmidrule{1-3}
 \cmidrule{6-7}
-\cmidrule{10-11}
-N18-1635 & 43.61 (106.5\%) & 16 &  &  & 46.45 (103.1\%) & 4 &  &  & 21.72 (96.7\%) & 3 &  & \\
-\cmidrule{1-3}
-\cmidrule{6-7}
-\cmidrule{10-11}
-N09-09 & 46.31 (113.1\%) & 7 &  &  & 41.61 (92.4\%) & 14 &  &  & 19.77 (88.1\%) & 17 &  & \\
-\cmidrule{1-3}
-\cmidrule{6-7}
-\cmidrule{10-11}
-N18-1731 & 46.1 (112.6\%) & 8 &  &  & 43.16 (95.8\%) & 11 &  &  & 20.49 (91.3\%) & 15 &  & \\
-\cmidrule{1-3}
-\cmidrule{6-7}
-\cmidrule{10-11}
-N18-1674 & 45.19 (110.4\%) & 9 &  &  & 44.26 (98.2\%) & 7 &  &  & 21.21 (94.5\%) & 9 &  & \\
-\cmidrule{1-3}
-\cmidrule{6-7}
-\cmidrule{10-11}
-N18-1682 & 45.11 (110.2\%) & 10 &  &  & 43.64 (96.9\%) & 8 &  &  & 20.76 (92.5\%) & 13 &  & \\
-\cmidrule{1-3}
-\cmidrule{6-7}
-\cmidrule{10-11}
-N18-1572 & 45.08 (110.1\%) & 11 &  &  & 38.58 (85.6\%) & 19 &  &  & 21.19 (94.4\%) & 10 &  & \\
-\cmidrule{1-3}
-\cmidrule{6-7}
-\cmidrule{10-11}
-N18-1751 & 44.8 (109.4\%) & 12 &  &  & 41.59 (92.3\%) & 15 &  &  & 20.44 (91\%) & 16 &  & \\
-\cmidrule{1-3}
-\cmidrule{6-7}
-\cmidrule{10-11}
-N18-1956 & 44.55 (108.8\%) & 13 &  &  & 34.79 (77.2\%) & 20 &  &  & 21.51 (95.8\%) & 5 &  & \\
-\cmidrule{1-3}
-\cmidrule{6-7}
-\cmidrule{10-11}
-N18-1604 & 43.83 (107.1\%) & 14 &  &  & 43.15 (95.8\%) & 12 &  &  & 21.34 (95.1\%) & 8 &  & \\
-\cmidrule{1-3}
-\cmidrule{6-7}
-\cmidrule{10-11}
-N18-1641 & 43.33 (105.8\%) & 17 &  &  & 41.99 (93.2\%) & 13 &  &  & 21.36 (95.1\%) & 7 &  & \\
-\cmidrule{1-3}
-\cmidrule{6-7}
-\cmidrule{10-11}
-NC-Raleigh & 39.91 (97.5\%) & 20 & \multirow{-20}{*}{\centering\arraybackslash 45.09} & \multirow{-20}{*}{\centering\arraybackslash 40.94} & 41.04 (91.1\%) & 16 & \multirow{-20}{*}{\centering\arraybackslash 42.92} & \multirow{-20}{*}{\centering\arraybackslash 45.05} & 23.5 (104.7\%) & 1 & \multirow{-20}{*}{\centering\arraybackslash 20.89} & \multirow{-20}{*}{\centering\arraybackslash 22.45}\\
+N18-1769 & 67.95 (105.9\%) & 6 & \multirow{-3}{*}{\raggedright\arraybackslash 66.4} & \multirow{-3}{*}{\raggedright\arraybackslash 64.14} & 37.88 (87.2\%) & 18 & \multirow{-3}{*}{\raggedright\arraybackslash 43.65} & \multirow{-3}{*}{\raggedright\arraybackslash 43.44}\\
 \bottomrule
-\multicolumn{13}{l}{\rule{0pt}{1em}\textsuperscript{*} Observed marginal mean of the phenotype (value of the phenotype/check average * 100\%).}\\
-\multicolumn{13}{l}{\rule{0pt}{1em}\textsuperscript{\dag} Rank of the genotype within the particular phenotype.}\\
-\multicolumn{13}{l}{\rule{0pt}{1em}\textsuperscript{\ddag} The average value of the phenotype for all lines in the test.}\\
-\multicolumn{13}{l}{\rule{0pt}{1em}\textsuperscript{\S} The average value of the phenotype for the checks in the test.}\\
+\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{*} The genotype name.}\\
+\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\dag} The genotype marginal mean for the phenotype (value divided by check average).}\\
+\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\ddag} The ranking of this genotype for the phenotype within its test.}\\
+\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\S} The average phenotype value for all genotypes in the test.}\\
+\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\P} The average value of the checks in the test.}\\
 \end{tabular}}
@@
 \centering
-\includegraphics[width=10 cm]{C:/Users/Jay/Desktop/Documents/R/Jay_yield/exports/plots/example_plot.pdf}
+\includegraphics[width=10 cm]{C:/Users/Jay/Documents/R/Projects/Jay_yield/exports/plots/example_plot.pdf}
 \caption{This is a figure, Schemes follow the same formatting.

### 2022-05-31 R/make_elite_summary_tables.R

@@ -5,14 +5,10 @@
 #' @title
 #' @param blue_data
 #' @param utility_tables
-#' @param lsd_data
-#' @param linear_means
-make_yield_summary_tables <- function(blue_data = genotype_BLUEs,
-                                      utility_tables = util_tables, lsd_data =
-                                      least_sig_differences, linear_means =
-                                      linear_means, 
-                                      summary_phenos = c("yield", "protein", "oil"), 
-                                      contrast_data  = genotype_contrasts_mixed) {
+#' @param summary_phenos
+make_elite_summary_tables <- function(blue_data = genotype_BLUEs,
+                                      utility_tables = util_tables, 
+                                      lsd_data = least_sig_differences) {
 
   # A function to get the minimum significant difference from the lsd results list
   get_msd <- function(fit_model){
@@ -59,7 +55,7 @@ make_yield_summary_tables <- function(blue_data = genotype_BLUEs,
   # 1. The overall test average, 
   # 2. The average for the checks
   # 3. The rank of each genotype
-  make_pheno_comparison <- function(test_data, keep_phenos = summary_phenos){
+  make_pheno_comparison <- function(test_data, keep_phenos = c("yield", "protein_plus_oil")){
     
     genotype_ranks <- test_data %>% 
       pivot_longer(cols = utility_tables$trait_shortnames$name, 
@@ -93,7 +89,7 @@ make_yield_summary_tables <- function(blue_data = genotype_BLUEs,
   # This function joins the augmented test summary data to the MSD table
   # to add the MSD for each phenotype onto the table and then pivot back to 
   # a wider format
-  full_comparison_table <- function(blue_data, lsd_data, keep_phenos = summary_phenos){
+  full_comparison_table <- function(blue_data, lsd_data, keep_phenos = c("yield", "protein_plus_oil")){
     
     # Get just the MSD from the msd dataframe
     just_msd <- lsd_data %>% 
@@ -122,9 +118,9 @@ make_yield_summary_tables <- function(blue_data = genotype_BLUEs,
     return(res)
   }
   
-  # The same function from above, but keep the data in a long format
+  # The same function from above, but keep the dat ain a long format
   # that is more helpful for plotting and other data management
-  full_comparison_long <- function(blue_data, lsd_data, keep_phenos = summary_phenos){
+  full_comparison_long <- function(blue_data, lsd_data, keep_phenos = c("yield", "protein_plus_oil")){
     
     # Get just the MSD from the msd dataframe
     just_msd <- lsd_data %>% 
[…]

### 2022-05-31 _targets.R

@@ -196,6 +196,14 @@ tar_plan(
                                        lsd_data       = least_sig_differences, 
                                        linear_means   = linear_means, 
                                        summary_phenos = c("yield", "protein", "oil"))),
+
+  # Summary tables for selections of elite genotypes
+tar_target(elite_genotype_tables, 
+           make_elite_summary_tables(blue_data      = genotype_BLUEs,
+                                     utility_tables = util_tables, 
+                                     lsd_data       = least_sig_differences)),
+             
+             
   
   # Histograms for each test with a selection of genotypes labelled for each test
   tar_target(labelled_test_histograms, 
@@ -219,7 +227,7 @@ tar_plan(
   ##################################################
   tar_render(analysis_writeup, here("doc", "analysis_writeup.Rmd")), 
 
-  tar_render(overview_document, here("doc", "overview_document.Rmd")),
+  # tar_render(overview_document, here("doc", "overview_document.Rmd")),
   
   tar_render(manuscript_document, here("doc", "manuscript", "manuscript.Rmd"))
   

### 2022-05-31 packages.R

@@ -45,7 +45,8 @@ pacman::p_load(rmdformats,
                kableExtra, 
                pander, 
                kableExtra, 
-               rmarkdown)
+               rmarkdown, 
+               rticles)
 
 # Function conflict preferences
 conflicted::conflict_prefer("filter", "dplyr", "base")

### 2022-05-31 sandbox/contrast filtering.R

@@ -8,12 +8,12 @@
 
 # Setting up environment
 source("./packages.R")
-tar_make()
+tar_make(-overview_document)
 
 tar_load(genotype_contrasts_mixed)
 
 all_contrasts <- genotype_contrasts_mixed %>% 
-  dplyr::filter(pheno %in% c("oil", "protein", "yield")) %>% 
+  dplyr::filter(pheno %in% c("oil", "protein", "yield", "lod", "sq")) %>% 
   mutate(contrasts = map(contrasts, as_tibble)) %>% 
   select(test_name, pheno, contrasts) %>% 
   unnest(contrasts) %>% 
@@ -37,25 +37,31 @@ comparable_pheno <- function(test_name, contrast, pheno, estimate, p.value){
       res <- switch(pheno, 
                     "oil"     = "HO",
                     "protein" = "HP", 
-                    "yield"   = "HY")
+                    "yield"   = "HY", 
+                    "lod"     = "HL", 
+                    "sq"      = "HSQ")
     }else{ 
       res <- switch(pheno, 
                     "oil"     = "LO",
                     "protein" = "LP", 
-                    "yield"   = "LY")
+                    "yield"   = "LY", 
+                    "lod"     = "LL", 
+                    "sq"      = "LSQ")
       }
   }else{
     res <- switch(pheno, 
                   "oil"     = "SO",
                   "protein" = "SP", 
-                  "yield"   = "SY")
+                  "yield"   = "SY", 
+                  "lod"     = "SL", 
+                  "sq"      = "SSQ")
   }
   
   return(res)
 }
 
 
-find_elites <- function(contrast, test_name, oil, protein, yield){
+find_elites <- function(contrast, test_name, oil, protein, yield, sq, lod){
   
   res <- ifelse(oil == "SO" & protein == "HP" & yield == 'SY', "yes", "no")
 
@@ -69,9 +75,23 @@ pheno_categories <- all_contrasts %>%
          contrast = str_remove(contrast, " - Checks")) %>% 
   {. ->> pheno_categories_full } %>%
   pivot_wider(names_from = pheno, values_from = pheno_group, id_cols = c(contrast, test_name)) %>% 
-  mutate(elite_geno = pmap_chr(., find_elites))
+  mutate(elite_geno = pmap_chr(., find_elites)) %>% 
[…]

### 2022-05-31 sandbox/yield summary tables.R

@@ -193,7 +193,21 @@ remove_phenotype_names <- function(column_names, pheno_names = c("yield", "prote
 
 
 # A function to make a kable table with group headings to match phenotypes
-make_phenotype_comparison_table <- function(comparison_table_output, pheno_names = c("yield", "protein", "oil", "protein_plus_oil"), keep_msd = TRUE){
+make_phenotype_comparison_table <- function(comparison_table_output, pheno_names = c("yield", "protein", "oil", "protein_plus_oil"), keep_msd = TRUE, keep_genos = NULL){
+  
+  if(all(names(comparison_table_output) == c("Jay Test 1", "Jay Test 2"))){
+    merged_comparison_tables <- map(comparison_table_output, function(x) pluck(x, "comparison_table")) %>% 
+      reduce(bind_rows)
+    
+    comparison_table_output <- list("comparison_table"  = merged_comparison_tables, 
+                                    "phenotype_indices" = comparison_table_output[[1]]$phenotype_indices)
+  }
+  
+  # If keep_genos is specified, first filter the comparison table fo just those genotypes
+  if(!is.null(keep_genos)){
+    comparison_table_output$comparison_table <- comparison_table_output$comparison_table %>% 
+      dplyr::filter(genotype %in% keep_genos)
+  }
   
   # First, sort the indices of the phenotypes by the order in which they appear 
   # in the comparison table
@@ -266,12 +280,34 @@ make_phenotype_comparison_table <- function(comparison_table_output, pheno_names
       sort()
   }
   
+  # names(current_table)[1] <- paste0(names(current_table)[1], 
+  #                                   footnote_marker_symbol(1, format = "latex"))
+  # 
+  # names(current_table)[2] <- paste0(names(current_table)[2], 
+  #                                   footnote_marker_symbol(2, format = "latex"))
+  # 
+  # names(current_table)[3] <- paste0(names(current_table)[3], 
+  #                                   footnote_marker_symbol(3, format = "latex"))
+  # 
+  # names(current_table)[4] <- paste0(names(current_table)[4], 
+  #                                   footnote_marker_symbol(4, format = "latex"))
+  # 
+  # names(current_table)[5] <- paste0(names(current_table)[5], 
+  #                                   footnote_marker_symbol(5, format = "latex"))
+  # 
   
-  knitr::kable(current_table, "latex") %>% 
+  knitr::kable(current_table, "html") %>% 
     kable_classic() %>% 
[…]

### 2022-06-01 doc/manuscript/manuscript.Rmd
Added to the manuscript

@@
   varieties with yield comparable to existing cultivars, and seed composition traits superior to existing cultivars.
+The performance of these RILs were evaluated in multiple environments and several genotypes were identified with yield comparable to that of existing high-performance cultivars with seed protein and or oil that is equal to or superior to the high-performing cultivars.
+These genotypes will provide breeders with additional sources of germplasm for continuing efforts to improve seed composition traits, and provide growers with valuable genotype options.
 keywords: |
@@
 conflictsofinterest: |
-  Declare conflicts of interest or state 'The authors declare no conflict of 
-  interest.' Authors must identify and declare any personal circumstances or
-  interest that may be perceived as inappropriately influencing the
-  representation or interpretation of reported research results. Any role of the
-  funding sponsors in the design of the study; in the collection, analyses or 
-  interpretation of data in the writing of the manuscript, or in the decision to 
-  publish the results must be declared in this section. If there is no role, 
-  please state 'The founding sponsors had no role in the design of the study; 
-  in the collection, analyses, or interpretation of data; in the writing of the 
-  manuscript, an in the decision to publish the results'.
+  The authors declare no conflict of 
+  interest.
 sampleavailability: |
@@
 ```
-
-# Version
-
-This Rmd-skeleton uses the mdpi Latex template published 2019/02.
-However, the official template gets more frequently updated than the 'rticles' package.
-Therefore, please make sure prior to paper submission, that you're using the most recent .cls, .tex and .bst files (available [here](http://www.mdpi.com/authors/latex)).
 
@@
 Least-square means (LS Means) for each genotype and trait were calculated using the above model using the emmeans package[@lenthEmmeansEstimatedMarginal2022] in R.
-The emmeans package was also used to calculate contrasts as a post-hoc test to compare RIL phenotype means to check means.
-Pearson correlation coefficients between each phenotype were calculated and visualized with the metan package.
+The emmeans package was also used to calculate contrasts as a post-hoc test to compare RIL phenotype means to check means for all collected phenotypes.
+Pearson correlation coefficients between each phenotype were calculated with the metan package.
 
@@
 
-Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
-Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers.
-Please disclose at the submission stage any restrictions on the availability of materials or information.
-New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.
+# Results and discussion
 
-Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers.
-If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
-They must be provided prior to publication.
+## Phenotypic correlations
+A strong negative correlation was observed in both tests between seed protein and seed oil content.
+A coefficient of r = -0.93 was observed in both populations.
+A negative correlation was observed between seed protein and yield with correlation coefficient of r = -0.29 was observed in both tests.
+This correlation was not statistically significant in either population.
+A weak positive correlation was observed between seed oil and seed yield in both populations.
+A correlation coefficient of r = 0.24 was observed in Test 1 while a coefficient of r = 0.28 was observed in Test 2.
+These correlation coefficients were not statistically significant in either population.
 
-Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
-
-# Results
-
+## Yield contrasts
 Several RILs in each of the tests had yield that was comparable to that of their check cultivars.
@@
 No genotypes had oil that was superior to the check cultivars, but some had comparable yield and oil content as well as superior protein content.
-These genotypes with comparable yield and superior protein also had desirable agronomic qualities such as low lodging and good seed quality which would make them ideal candidates for future breeding material.
 
-## Genotypes with omparable yield and oil and superior protein
+RILs were also evaluated for lodging and seed quality.
+All RILs had seed quality that was on par with that of the high-yielding checks however, however 11 genotypes had lodging scores that were significantly greater than the checks on the basis of contrasts.
+These RILs were removed from consideration for recommendation on the basis of their relatively poor agronomic performance.
+
+## Genotypes with comparable yield and oil and superior protein
 Four genotypes had yield and oil that was similar to that of the yield checks, and seed protein that was greater than the average of the checks.
 These genotypes are N18-1635 from Test 1 and genotypes N18-1627, N18-1643, and N18-1783 from Test 2.
+Summary data for these lines is given in table 1.
 
@@
 
+From among these lines, only
+
+## Genotypes with comparable yield and superior protein
+Seventeen RILs had a similar yield and superior protein content to the check cultivars. Summary data for the seed protein and seed yield of these lines is given in table 2. The maximum yielding line
+
 ```{r high_po_table, results = "asis", echo = FALSE}
 
-print(elite_genotype_tables$po_top_ten)
+print(elite_genotype_tables$hp_sy_table)
 
@@
 
-## Subsection Heading Here
-
-Subsection text here.
-
-### Subsubsection Heading Here
-
-Bulleted lists look like this:
-
--   First bullet
--   Second bullet
--   Third bullet
-
-Numbered lists can be added as follows:
-
-1.  First item
-2.  Second item
-3.  Third item
-
-The text continues here.
-
-All figures and tables should be cited in the main text as Figure 1, Table 1, etc.
-
-```{r example_plot, echo = FALSE}
-tar_load(example_plot)
-```
-
-```{=tex}
-\begin{figure}[H]
-\centering
-\includegraphics[width=10 cm]{`r example_plot`}
-\caption{This is a figure, Schemes follow the same formatting.
-If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
-(\textbf{b}) Description of what is contained in the second panel.
-Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.}
-\end{figure}
-```
 ```{=tex}
@@
 ```
-```{=tex}
-\begin{table}[H]
-\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
-\centering
-%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
-\begin{tabular}{ccc}
-\toprule
-\textbf{Title 1}    & \textbf{Title 2}  & \textbf{Title 3}\\
-\midrule
-entry 1     & data          & data\\
-entry 2     & data          & data\\
-\bottomrule
-\end{tabular}
-\end{table}
-```
-```{r test_table, results = "asis", echo = FALSE}
-print(example_table)
-```
-
-This is an example of an equation:
-
-\begin{equation}
-\mathbb{S}
-\end{equation} <!-- If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
-This ensures correct linenumbering.
-The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
--->
-
-<!-- Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows: -->
-
-Example of a theorem:
-
-```{=tex}
-\begin{Theorem}
-Example text of a theorem.
-\end{Theorem}
-```
-The text continues here. Proofs must be formatted as follows:
-
-Example of a proof:
-
-```{=tex}
-\begin{proof}[Proof of Theorem 1]
-Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
-\end{proof}
-```
-The text continues here.
-
-# Discussion
-
-Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
 
@@
 
-This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
-
-# Patents
-
-This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
+We have identified several genotypes with seed yield that is comparable to existing cultivars that are commonly used in production.
+Many of these genotypes have seed protein content that exceeds that of the check cultivars, and some of these with superior protein have a seed oil content that is comparable to these check cultivars as well.
+These genotypes have good agronomic qualities as well and will provide both breeders and growers with new options for genotypes that can be used in production or used in breeding programs that seek to improve valuable soybean seed composition traits.

### 2022-06-01 doc/manuscript/manuscript.tex
Added to the manuscript

@@
 yield comparable to existing cultivars, and seed composition traits
-superior to existing cultivars.}
+superior to existing cultivars. The performance of these RILs were
+evaluated in multiple environments and several genotypes were identified
+with yield comparable to that of existing high-performance cultivars
+with seed protein and or oil that is equal to or superior to the
+high-performing cultivars. These genotypes will provide breeders with
+additional sources of germplasm for continuing efforts to improve seed
+composition traits, and provide growers with valuable genotype options.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\hypertarget{version}{%
-\section{Version}\label{version}}
-
-This Rmd-skeleton uses the mdpi Latex template published 2019/02.
-However, the official template gets more frequently updated than the
-`rticles' package. Therefore, please make sure prior to paper
-submission, that you're using the most recent .cls, .tex and .bst files
-(available \href{http://www.mdpi.com/authors/latex}{here}).
 
@@
 package was also used to calculate contrasts as a post-hoc test to
-compare RIL phenotype means to check means. Pearson correlation
-coefficients between each phenotype were calculated and visualized with
-the metan package.
+compare RIL phenotype means to check means for all collected phenotypes.
+Pearson correlation coefficients between each phenotype were calculated
+with the metan package.
 
@@
 
-Materials and Methods should be described with sufficient details to
-allow others to replicate and build on published results. Please note
-that publication of your manuscript implicates that you must make all
-materials, data, computer code, and protocols associated with the
-publication available to readers. Please disclose at the submission
-stage any restrictions on the availability of materials or information.
-New methods and protocols should be described in detail while
-well-established methods can be briefly described and appropriately
-cited.
-
-Research manuscripts reporting large datasets that are deposited in a
-publicly available database should specify where the data have been
-deposited and provide the relevant accession numbers. If the accession
-numbers have not yet been obtained at the time of submission, please
-state that they will be provided during review. They must be provided
-prior to publication.
-
-Interventionary studies involving animals or humans, and other studies
-require ethical approval must list the authority that provided approval
-and the corresponding ethical approval code.
-
 \hypertarget{results}{%
 \section{Results}\label{results}}
+
+\hypertarget{phenotypic-correlations}{%
+\subsection{Phenotypic correlations}\label{phenotypic-correlations}}
+
+A strong negative correlation was observed in both tests between seed
+protein and seed oil content. A coefficient of r = -0.93 was observed in
+both populations. A negative correlation was observed between seed
+protein and yield with correlation coefficient of r = -0.29 was observed
+in both tests. This correlation was not statistically significant in
+either population. A weak positive correlation was observed between seed
+oil and seed yield in both populations. A correlation coefficient of r =
+0.24 was observed in Test 1 while a coefficient of r = 0.28 was observed
+in Test 2. These correlation coefficients were not statistically
+significant in either population.
+
+\hypertarget{yield-contrasts}{%
+\subsection{Yield contrasts}\label{yield-contrasts}}
 
@@
 was superior to the check cultivars, but some had comparable yield and
-oil content as well as superior protein content. These genotypes with
-comparable yield and superior protein also had desirable agronomic
-qualities such as low lodging and good seed quality which would make
-them ideal candidates for future breeding material.
+oil content as well as superior protein content.
 
-\hypertarget{genotypes-with-omparable-yield-and-oil-and-superior-protein}{%
-\subsection{Genotypes with omparable yield and oil and superior
-protein}\label{genotypes-with-omparable-yield-and-oil-and-superior-protein}}
+RILs were also evaluated for lodging and seed quality. All RILs had seed
+quality that was on par with that of the high-yielding checks however,
+however 11 genotypes had lodging scores that were significantly greater
+than the checks on the basis of contrasts. These RILs were removed from
+consideration for recommendation on the basis of their relatively poor
+agronomic performance.
+
+\hypertarget{genotypes-with-comparable-yield-and-oil-and-superior-protein}{%
+\subsection{Genotypes with comparable yield and oil and superior
+protein}\label{genotypes-with-comparable-yield-and-oil-and-superior-protein}}
 
@@
 \resizebox{\linewidth}{!}{
-\begin{tabular}[t]{llrlllrll}
+\begin{tabular}[t]{lllrlllrlllrll}
 \toprule
-\multicolumn{1}{c}{} & \multicolumn{4}{c}{Protein + Oil} & \multicolumn{4}{c}{Yield} \\
-\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
-Genotype & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average\\
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{4}{c}{Protein} & \multicolumn{4}{c}{Yield} & \multicolumn{4}{c}{Oil} \\
+\cmidrule(l{3pt}r{3pt}){3-6} \cmidrule(l{3pt}r{3pt}){7-10} \cmidrule(l{3pt}r{3pt}){11-14}
+Genotype & Test Name & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average\\
 \midrule
-N18-1635 & 65.32 (103\%) & 13 & 65.98 & 63.39 & 46.45 (103.1\%) & 4 & 42.92 & 45.05\\
-\cmidrule{1-9}
-N18-1783 & 67.38 (105.1\%) & 8 &  &  & 37.63 (86.6\%) & 19 &  & \\
-\cmidrule{1-3}
-\cmidrule{6-7}
-N18-1627 & 66.52 (103.7\%) & 10 &  &  & 46.01 (105.9\%) & 8 &  & \\
-\cmidrule{1-3}
-\cmidrule{6-7}
-N18-1643 & 65.8 (102.6\%) & 13 & \multirow{-3}{*}{\raggedright\arraybackslash 66.4} & \multirow{-3}{*}{\raggedright\arraybackslash 64.14} & 40.54 (93.3\%) & 16 & \multirow{-3}{*}{\raggedright\arraybackslash 43.65} & \multirow{-3}{*}{\raggedright\arraybackslash 43.44}\\
+N18-1635 & Jay Test 1 & 43.61 (106.5\%) & 16 & 45.09 & 40.94 & 46.45 (103.1\%) & 4 & 42.92 & 45.05 & 21.72 (96.7\%) & 3 & 20.89 & 22.45\\
+\cmidrule{1-14}
+N18-1783 &  & 46.74 (109.3\%) & 8 &  &  & 37.63 (86.6\%) & 19 &  &  & 20.63 (96.5\%) & 11 &  & \\
+\cmidrule{1-1}
+\cmidrule{3-4}
+\cmidrule{7-8}
+\cmidrule{11-12}
+N18-1627 &  & 45.9 (107.3\%) & 9 &  &  & 46.01 (105.9\%) & 8 &  &  & 20.62 (96.5\%) & 12 &  & \\
+\cmidrule{1-1}
+\cmidrule{3-4}
+\cmidrule{7-8}
+\cmidrule{11-12}
+N18-1643 & \multirow{-3}{*}{\raggedright\arraybackslash Jay Test 2} & 44.35 (103.7\%) & 13 & \multirow{-3}{*}{\raggedright\arraybackslash 45.7} & \multirow{-3}{*}{\raggedright\arraybackslash 42.77} & 40.54 (93.3\%) & 16 & \multirow{-3}{*}{\raggedright\arraybackslash 43.65} & \multirow{-3}{*}{\raggedright\arraybackslash 43.44} & 21.45 (100.4\%) & 7 & \multirow{-3}{*}{\raggedright\arraybackslash 20.7} & \multirow{-3}{*}{\raggedright\arraybackslash 21.37}\\
 \bottomrule
-\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{*} The genotype name.}\\
-\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\dag} The genotype marginal mean for the phenotype (value divided by check average).}\\
-\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\ddag} The ranking of this genotype for the phenotype within its test.}\\
-\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\S} The average phenotype value for all genotypes in the test.}\\
-\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\P} The average value of the checks in the test.}\\
+\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{*} The genotype name.}\\
+\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\dag} The genotype marginal mean for the phenotype (value divided by check average).}\\
+\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\ddag} The ranking of this genotype for the phenotype within its test.}\\
+\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\S} The average phenotype value for all genotypes in the test.}\\
+\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\P} The average value of the checks in the test.}\\
 \end{tabular}}
@@
 
+\hypertarget{genotypes-with-comparable-yield-and-superior-protein}{%
+\subsection{Genotypes with comparable yield and superior
+protein}\label{genotypes-with-comparable-yield-and-superior-protein}}
+
+Seventeen out of the thirty RILs had a similar yield and superior
+protein content to the check cultivars.
+
 \begin{table}[H]
 
-\caption{Top 10 soybean genotypes on the basis of protein plus oil content.}
+\caption{Soybean RILs with superior protein content and comparable yield performance to high-yielding check cultivars.}
 \centering
 \resizebox{\linewidth}{!}{
-\begin{tabular}[t]{llrlllrll}
+\begin{tabular}[t]{lllrlllrll}
 \toprule
-\multicolumn{1}{c}{} & \multicolumn{4}{c}{Protein + Oil} & \multicolumn{4}{c}{Yield} \\
-\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
-Genotype & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average\\
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{4}{c}{Protein} & \multicolumn{4}{c}{Yield} \\
+\cmidrule(l{3pt}r{3pt}){3-6} \cmidrule(l{3pt}r{3pt}){7-10}
+Genotype & Test Name & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average\\
 \midrule
-N18-1855 & 68.13 (107.5\%) & 2 &  &  & 43.17 (95.8\%) & 10 &  & \\
-\cmidrule{1-3}
-\cmidrule{6-7}
-N18-1632-2 & 67.47 (106.4\%) & 3 &  &  & 46.34 (102.9\%) & 5 &  & \\
-\cmidrule{1-3}
-\cmidrule{6-7}
-N18-1763 & 67.4 (106.3\%) & 5 &  &  & 39.45 (87.6\%) & 17 &  & \\
-\cmidrule{1-3}
-\cmidrule{6-7}
-N18-1595 & 66.87 (105.5\%) & 6 &  &  & 43.52 (96.6\%) & 9 &  & \\
-\cmidrule{1-3}
-\cmidrule{6-7}
-N18-1731 & 66.59 (105\%) & 7 &  &  & 43.16 (95.8\%) & 11 &  & \\
-\cmidrule{1-3}
-\cmidrule{6-7}
-N18-1674 & 66.4 (104.7\%) & 8 & \multirow{-6}{*}{\raggedright\arraybackslash 65.98} & \multirow{-6}{*}{\raggedright\arraybackslash 63.39} & 44.26 (98.2\%) & 7 & \multirow{-6}{*}{\raggedright\arraybackslash 42.92} & \multirow{-6}{*}{\raggedright\arraybackslash 45.05}\\
-\cmidrule{1-9}
-N18-1575 & 69.04 (107.6\%) & 1 &  &  & 42.49 (97.8\%) & 12 &  & \\
-\cmidrule{1-3}
-\cmidrule{6-7}
-N18-1761 & 68.48 (106.8\%) & 3 &  &  & 45.74 (105.3\%) & 9 &  & \\
-\cmidrule{1-3}
-\cmidrule{6-7}
-N18-1769 & 67.95 (105.9\%) & 6 & \multirow{-3}{*}{\raggedright\arraybackslash 66.4} & \multirow{-3}{*}{\raggedright\arraybackslash 64.14} & 37.88 (87.2\%) & 18 & \multirow{-3}{*}{\raggedright\arraybackslash 43.65} & \multirow{-3}{*}{\raggedright\arraybackslash 43.44}\\
+N18-1763 &  & 47.82 (116.8\%) & 2 &  &  & 39.45 (87.6\%) & 17 &  & \\
+\cmidrule{1-1}
+\cmidrule{3-4}
+\cmidrule{7-8}
+N18-1855 &  & 47.52 (116.1\%) & 3 &  &  & 43.17 (95.8\%) & 10 &  & \\
+\cmidrule{1-1}
+\cmidrule{3-4}
+\cmidrule{7-8}
+N18-1595 &  & 47.36 (115.7\%) & 4 &  &  & 43.52 (96.6\%) & 9 &  & \\
+\cmidrule{1-1}
+\cmidrule{3-4}
+\cmidrule{7-8}
+N18-1632-1 &  & 46.64 (113.9\%) & 6 &  &  & 45.73 (101.5\%) & 6 &  & \\
+\cmidrule{1-1}
+\cmidrule{3-4}
+\cmidrule{7-8}
+N18-1620 &  & 43.63 (106.6\%) & 15 &  &  & 46.54 (103.3\%) & 3 &  & \\
+\cmidrule{1-1}
+\cmidrule{3-4}
+\cmidrule{7-8}
+N18-1635 &  & 43.61 (106.5\%) & 16 &  &  & 46.45 (103.1\%) & 4 &  & \\
+\cmidrule{1-1}
+\cmidrule{3-4}
+\cmidrule{7-8}
+N18-1731 &  & 46.1 (112.6\%) & 8 &  &  & 43.16 (95.8\%) & 11 &  & \\
+\cmidrule{1-1}
+\cmidrule{3-4}
+\cmidrule{7-8}
+N18-1674 &  & 45.19 (110.4\%) & 9 &  &  & 44.26 (98.2\%) & 7 &  & \\
+\cmidrule{1-1}
+\cmidrule{3-4}
+\cmidrule{7-8}
+N18-1682 &  & 45.11 (110.2\%) & 10 &  &  & 43.64 (96.9\%) & 8 &  & \\
+\cmidrule{1-1}
+\cmidrule{3-4}
+\cmidrule{7-8}
+N18-1572 &  & 45.08 (110.1\%) & 11 &  &  & 38.58 (85.6\%) & 19 &  & \\
+\cmidrule{1-1}
+\cmidrule{3-4}
+\cmidrule{7-8}
+N18-1751 & \multirow{-11}{*}{\raggedright\arraybackslash Jay Test 1} & 44.8 (109.4\%) & 12 & \multirow{-11}{*}{\raggedright\arraybackslash 45.09} & \multirow{-11}{*}{\raggedright\arraybackslash 40.94} & 41.59 (92.3\%) & 15 & \multirow{-11}{*}{\raggedright\arraybackslash 42.92} & \multirow{-11}{*}{\raggedright\arraybackslash 45.05}\\
+\cmidrule{1-10}
+N18-1761 &  & 49.1 (114.8\%) & 2 &  &  & 45.74 (105.3\%) & 9 &  & \\
+\cmidrule{1-1}
+\cmidrule{3-4}
+\cmidrule{7-8}
+N18-1575 &  & 48.67 (113.8\%) & 4 &  &  & 42.49 (97.8\%) & 12 &  & \\
+\cmidrule{1-1}
+\cmidrule{3-4}
+\cmidrule{7-8}
+N18-1769 &  & 48.58 (113.6\%) & 5 &  &  & 37.88 (87.2\%) & 18 &  & \\
+\cmidrule{1-1}
+\cmidrule{3-4}
+\cmidrule{7-8}
+N18-1783 &  & 46.74 (109.3\%) & 8 &  &  & 37.63 (86.6\%) & 19 &  & \\
+\cmidrule{1-1}
+\cmidrule{3-4}
+\cmidrule{7-8}
+N18-1627 &  & 45.9 (107.3\%) & 9 &  &  & 46.01 (105.9\%) & 8 &  & \\
+\cmidrule{1-1}
+\cmidrule{3-4}
+\cmidrule{7-8}
+N18-1643 & \multirow{-6}{*}{\raggedright\arraybackslash Jay Test 2} & 44.35 (103.7\%) & 13 & \multirow{-6}{*}{\raggedright\arraybackslash 45.7} & \multirow{-6}{*}{\raggedright\arraybackslash 42.77} & 40.54 (93.3\%) & 16 & \multirow{-6}{*}{\raggedright\arraybackslash 43.65} & \multirow{-6}{*}{\raggedright\arraybackslash 43.44}\\
 \bottomrule
-\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{*} The genotype name.}\\
-\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\dag} The genotype marginal mean for the phenotype (value divided by check average).}\\
-\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\ddag} The ranking of this genotype for the phenotype within its test.}\\
-\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\S} The average phenotype value for all genotypes in the test.}\\
-\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\P} The average value of the checks in the test.}\\
+\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{*} The genotype name.}\\
+\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\dag} The genotype marginal mean for the phenotype (value divided by check average).}\\
+\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\ddag} The ranking of this genotype for the phenotype within its test.}\\
+\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\S} The average phenotype value for all genotypes in the test.}\\
+\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\P} The average value of the checks in the test.}\\
 \end{tabular}}
 \end{table}
-
-\hypertarget{subsection-heading-here}{%
-\subsection{Subsection Heading Here}\label{subsection-heading-here}}
-
-Subsection text here.
-
-\hypertarget{subsubsection-heading-here}{%
-\subsubsection{Subsubsection Heading
-Here}\label{subsubsection-heading-here}}
-
-Bulleted lists look like this:
-
-\begin{itemize}
-\tightlist
-\item
-  First bullet
-\item
-  Second bullet
-\item
-  Third bullet
-\end{itemize}
-
-Numbered lists can be added as follows:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  First item
-\item
-  Second item
-\item
-  Third item
-\end{enumerate}
-
-The text continues here.
-
-All figures and tables should be cited in the main text as Figure 1,
-Table 1, etc.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=10 cm]{C:/Users/Jay/Documents/R/Projects/Jay_yield/exports/plots/example_plot.pdf}
-\caption{This is a figure, Schemes follow the same formatting.
-If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
-(\textbf{b}) Description of what is contained in the second panel.
-Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.}
-\end{figure}
 
@@
 
-\begin{table}[H]
-\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
-\centering
-%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
-\begin{tabular}{ccc}
-\toprule
-\textbf{Title 1}    & \textbf{Title 2}  & \textbf{Title 3}\\
-\midrule
-entry 1     & data          & data\\
-entry 2     & data          & data\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{table}
-
-\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
-\centering
-\begin{tabular}[t]{lrrrrrrrrrrr}
-\toprule
-\textbf{ } & \textbf{mpg} & \textbf{cyl} & \textbf{disp} & \textbf{hp} & \textbf{drat} & \textbf{wt} & \textbf{qsec} & \textbf{vs} & \textbf{am} & \textbf{gear} & \textbf{carb}\\
-\midrule
-Mazda RX4 & 21.0 & 6 & 160 & 110 & 3.90 & 2.620 & 16.46 & 0 & 1 & 4 & 4\\
-Mazda RX4 Wag & 21.0 & 6 & 160 & 110 & 3.90 & 2.875 & 17.02 & 0 & 1 & 4 & 4\\
-Datsun 710 & 22.8 & 4 & 108 & 93 & 3.85 & 2.320 & 18.61 & 1 & 1 & 4 & 1\\
-Hornet 4 Drive & 21.4 & 6 & 258 & 110 & 3.08 & 3.215 & 19.44 & 1 & 0 & 3 & 1\\
-Hornet Sportabout & 18.7 & 8 & 360 & 175 & 3.15 & 3.440 & 17.02 & 0 & 0 & 3 & 2\\
-\addlinespace
-Valiant & 18.1 & 6 & 225 & 105 & 2.76 & 3.460 & 20.22 & 1 & 0 & 3 & 1\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-This is an example of an equation:
-
-\begin{equation}
-\mathbb{S}
-\end{equation}
-
-Example of a theorem:
-
-\begin{Theorem}
-Example text of a theorem.
-\end{Theorem}
-
-The text continues here. Proofs must be formatted as follows:
-
-Example of a proof:
-
-\begin{proof}[Proof of Theorem 1]
-Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
-\end{proof}
-
-The text continues here.
-
 \hypertarget{discussion}{%
 \section{Discussion}\label{discussion}}
-
-Authors should discuss the results and how they can be interpreted in
-perspective of previous studies and of the working hypotheses. The
-findings and their implications should be discussed in the broadest
-context possible. Future research directions may also be highlighted.
 
@@
 
-This section is not mandatory, but can be added to the manuscript if the
-discussion is unusually long or complex.
-
-\hypertarget{patents}{%
-\section{Patents}\label{patents}}
-
-This section is not mandatory, but may be added if there are patents
-resulting from the work reported in this manuscript.
+We have identified several genotypes with seed yield that is comparable
+to existing cultivars that are commonly used in production. Many of
+these genotypes have seed protein content that exceeds that of the check
+cultivars, and some of these with superior protein have a seed oil
+content that is comparable to these check cultivars as well. These
+genotypes have good agronomic qualities as well and will provide both
+breeders and growers with new options for genotypes that can be used in
+production or used in breeding programs that seek to improve valuable
+soybean seed composition traits.
 

### 2022-06-01 R/make_elite_summary_tables.R

@@ -104,7 +104,7 @@ make_elite_summary_tables <- function(blue_data = genotype_BLUEs,
     # and then pivot to a wide format using the phenotypes to name columns
     # and all the columns that have been added to fill the values
     full_comparisons <- map2(test_comparisons, just_msd, function(x, y) left_join(x, y, by = c("pheno" = "trait")) %>% 
-                               pivot_wider(id_cols = c("genotype"), names_from = "pheno", values_from = c("value", "rank", "test_avg", "check_avg_value", "msd"), names_vary = "slowest"))
+                               pivot_wider(id_cols = c("genotype", "test_name"), names_from = "pheno", values_from = c("value", "rank", "test_avg", "check_avg_value", "msd"), names_vary = "slowest"))
     
     
     pheno_indices <- map(full_comparisons, 
@@ -131,16 +131,27 @@ make_elite_summary_tables <- function(blue_data = genotype_BLUEs,
     # a summary table for each test
     test_comparisons <- map(blue_data, make_pheno_comparison, keep_phenos = keep_phenos)
     
+    # Get the test that each genotype belongs to 
+    geno_tests <- blue_data %>% 
+      select(test_name, genotype)
+    
     # Now join each summary table to the corresponding MSD table for each test
     # and then pivot to a wide format using the phenotypes to name columns
     # and all the columns that have been added to fill the values
-    full_comparisons <- map2(test_comparisons, just_msd, function(x, y) left_join(x, y, by = c("pheno" = "trait")))
+    full_comparisons <- map2(test_comparisons, just_msd, function(x, y) left_join(x, y, by = c("pheno" = "trait"))) %>% 
+      left_join(geno_tests, by = genotype)
     
     return(full_comparisons)
   }
   
   # Testing the functions together
   comparison_tables <- full_comparison_table(blue_data = blue_data$BLUEs, lsd_data)
+  
+  # Protein and yield comparison tables
+  py_comparison_tables <- full_comparison_table(blue_data = blue_data$BLUEs, lsd_data,keep_phenos = c("yield", "protein"))
+  
+  # Protein oil yield comparison tables
+  poy_comparison_tables <- full_comparison_table(blue_data = blue_data$BLUEs, lsd_data,keep_phenos = c("yield", "protein", "oil"))
   
   # TODO:
   # Need to make a function that takes this data and converts it to a more 
@@ -187,7 +198,7 @@ make_elite_summary_tables <- function(blue_data = genotype_BLUEs,
   
   
   # A function to make a kable table with group headings to match phenotypes
[…]

### 2022-06-01 sandbox/contrast filtering.R

@@ -8,7 +8,7 @@
 
 # Setting up environment
 source("./packages.R")
-tar_make(-overview_document)
+tar_make()
 
 tar_load(genotype_contrasts_mixed)
 

### 2022-06-01 doc/manuscript/manuscript.Rmd
saved manuscript

@@
 Several RILs in each of the tests had yield that was comparable to that of their check cultivars.
-This was determined both quanititatively through the use of contrasts between the mean of each RIL with the average of the yield check means, and qualitatively by inspecting the standard errors on the estimation of the genotype marginal means for yield.
+This was determined both quantitatively through the use of contrasts between the mean of each RIL with the average of the yield check means, and qualitatively by inspecting the standard errors on the estimation of the genotype marginal means for yield.
 No genotypes had yield that was quantitatively higher than that of the yield checks, however many had comparable yield.
@@
 RILs were also evaluated for lodging and seed quality.
-All RILs had seed quality that was on par with that of the high-yielding checks however, however 11 genotypes had lodging scores that were significantly greater than the checks on the basis of contrasts.
+All RILs had seed quality that was on par with that of the high-yielding checks however, however 11 genotypes had lodging scores that were statistically significantly greater than the checks on the basis of contrasts.
 These RILs were removed from consideration for recommendation on the basis of their relatively poor agronomic performance.
@@
 
-From among these lines, only
+A strong negative correlation was observed in both populations betweeen seed oil and seed protein.
+This observation matches well with previous findings on the inverse correlation between seed protein and seed oil.
+Many RILs had high protein when compared with the check cultivars so it was not surprising that relatively few had both a superior seed protein content, and a comparable seed oil content.
 
@@
 ```
+
+Among these genotypes are several with both average seed protein and average seed yield that were greater than the averages of the checks for each test.
+These N18-1632-1, N18-1620, N18-1635 from test 1 and RILs N18-1761 and N18-1627 from test 2.
+Of particular note are genotypes N18-1632-1 from test 1 and N18-1761 from test 2.
+On average, genotype N18-1632-1 had a protein content that was 113.9% of the check average while maintaining a yield average that was 101.5% that of the check average.
+SImilarly, RIL N18-1761 from test 2 had a protein
 

### 2022-06-02 doc/manuscript/manuscript.Rmd
Added to manuscript

@@
 The emmeans package was also used to calculate contrasts as a post-hoc test to compare RIL phenotype means to check means for all collected phenotypes.
+A sidak adjustment was used to account for multiple comparisons in the calculation of contrasts.
+
 Pearson correlation coefficients between each phenotype were calculated with the metan package.
@@
 These correlation coefficients were not statistically significant in either population.
+Visualizations of the pairwise correlation coefficients for Tests 1 and 2 can be seen in supplementary figures 2 and 3, respectively.
 
@@
 These RILs were removed from consideration for recommendation on the basis of their relatively poor agronomic performance.
+
+A detailed summary of all contrasts can be seen in supplementary table 1.
 
@@
 On average, genotype N18-1632-1 had a protein content that was 113.9% of the check average while maintaining a yield average that was 101.5% that of the check average.
-SImilarly, RIL N18-1761 from test 2 had a protein
 
@@
 \centering
-\includegraphics[width=3 cm]{logo-mdpi}
+\includegraphics[width=15 cm]{C:/Users/Jay/Documents/R/Projects/Jay_yield/exports/plots/supplemental/supplemental_figure_1.pdf}
 \caption{This is a figure, Schemes follow the same formatting.

### 2022-06-02 doc/manuscript/manuscript.tex
Added to manuscript

@@
 compare RIL phenotype means to check means for all collected phenotypes.
+A sidak adjustment was used to account for multiple comparisons in the
+calculation of contrasts.
+
 Pearson correlation coefficients between each phenotype were calculated
@@
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+\hypertarget{results-and-discussion}{%
+\section{Results and discussion}\label{results-and-discussion}}
 
@@
 in Test 2. These correlation coefficients were not statistically
-significant in either population.
+significant in either population. Visualizations of the pairwise
+correlation coefficients for Tests 1 and 2 can be seen in supplementary
+figures 2 and 3, respectively.
 
@@
 Several RILs in each of the tests had yield that was comparable to that
-of their check cultivars. This was determined both quanititatively
+of their check cultivars. This was determined both quantitatively
 through the use of contrasts between the mean of each RIL with the
@@
 quality that was on par with that of the high-yielding checks however,
-however 11 genotypes had lodging scores that were significantly greater
-than the checks on the basis of contrasts. These RILs were removed from
-consideration for recommendation on the basis of their relatively poor
-agronomic performance.
+however 11 genotypes had lodging scores that were statistically
+significantly greater than the checks on the basis of contrasts. These
+RILs were removed from consideration for recommendation on the basis of
+their relatively poor agronomic performance.
+
+A detailed summary of all contrasts can be seen in supplementary table
+1.
 
@@
 checks. These genotypes are N18-1635 from Test 1 and genotypes N18-1627,
-N18-1643, and N18-1783 from Test 2.
+N18-1643, and N18-1783 from Test 2. Summary data for these lines is
+given in table 1.
 
@@
 
+A strong negative correlation was observed in both populations betweeen
+seed oil and seed protein. This observation matches well with previous
+findings on the inverse correlation between seed protein and seed oil.
+Many RILs had high protein when compared with the check cultivars so it
+was not surprising that relatively few had both a superior seed protein
+content, and a comparable seed oil content.
+
 \hypertarget{genotypes-with-comparable-yield-and-superior-protein}{%
@@
 
-Seventeen out of the thirty RILs had a similar yield and superior
-protein content to the check cultivars.
+Seventeen RILs had a similar yield and superior protein content to the
+check cultivars. Summary data for the seed protein and seed yield of
+these lines is given in table 2. The maximum yielding line
 
@@
 
+Among these genotypes are several with both average seed protein and
+average seed yield that were greater than the averages of the checks for
+each test. These N18-1632-1, N18-1620, N18-1635 from test 1 and RILs
+N18-1761 and N18-1627 from test 2. Of particular note are genotypes
+N18-1632-1 from test 1 and N18-1761 from test 2. On average, genotype
+N18-1632-1 had a protein content that was 113.9\% of the check average
+while maintaining a yield average that was 101.5\% that of the check
+average.
+
 \begin{figure}[H]
 \centering
-\includegraphics[width=3 cm]{logo-mdpi}
+\includegraphics[width=15 cm]{C:/Users/Jay/Documents/R/Projects/Jay_yield/exports/plots/supplemental/supplemental_figure_1.pdf}
 \caption{This is a figure, Schemes follow the same formatting.
@@
 \end{figure}
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\conflictsofinterest{Declare conflicts of interest or state `The authors
-declare no conflict of interest.' Authors must identify and declare any
-personal circumstances or interest that may be perceived as
-inappropriately influencing the representation or interpretation of
-reported research results. Any role of the funding sponsors in the
-design of the study; in the collection, analyses or interpretation of
-data in the writing of the manuscript, or in the decision to publish the
-results must be declared in this section. If there is no role, please
-state `The founding sponsors had no role in the design of the study; in
-the collection, analyses, or interpretation of data; in the writing of
-the manuscript, an in the decision to publish the results'.}
+\conflictsofinterest{The authors declare no conflict of interest.}
 

### 2022-06-02 R/export_contrasts.R

@@ -1,0 +1,27 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param genotype_contrasts_mixed
+#' @param util_tables
+export_contrasts <- function(genotype_contrasts_mixed, util_tables, exportdir = here("exports", "data", "supplementary")) {
+
+  # Unnest the contrasts
+  contrasts_wide <- genotype_contrasts_mixed %>% 
+    mutate(contrasts = map(contrasts, as_tibble)) %>% 
+    select(test_name, pheno, contrasts) %>% 
+    unnest(contrasts) 
+  
+  # Rename the variables in the pheno column
+  contrasts_wide <- convert_from_table(contrasts_wide, "pheno", util_tables$trait_lookup) %>% 
+    rename(`Test Name` = test_name)
+  
+  # Export the table
+  save_path <- paste0(exportdir, "/", "supplementary_table_1.csv")
+  
+  write_csv(contrasts_wide, save_path)
+  
+  return(save_path)
+
+}

### 2022-06-02 R/export_phenotype_plots.R

@@ -5,7 +5,7 @@
 #' @title
 #' @param BLUE_plots_two_years
 #' @param phenotype_scatterplots
-export_phenotype_plots <- function(BLUE_plots_two_years, phenotype_scatterplots, labelled_test_histograms, export_dir = here("exports", "plots")) {
+export_phenotype_plots <- function(BLUE_plots_two_years, phenotype_scatterplots, labelled_test_histograms, correlation_plots, export_dir = here("exports", "plots")) {
 
   
   ## Section: Scatterplots
@@ -37,6 +37,16 @@ export_phenotype_plots <- function(BLUE_plots_two_years, phenotype_scatterplots,
   
   # All filepaths to the saved scatterplots
   all_scatterplots <- export_scatterplots(phenotype_scatterplots$side_by_side)
+  
+  both_plots_scatter_filepath <- paste0(export_dir, "/supplemental/", "supplemental_figure_1.pdf")
+  
+  ggsave(filename = both_plots_scatter_filepath, 
+         plot = phenotype_scatterplots$combined, 
+         device = "pdf", 
+         width = 12, 
+         height = 10, 
+         units = "in", 
+         dpi = 800)
   
   
   ## Section: Labelled histograms
@@ -96,6 +106,27 @@ export_phenotype_plots <- function(BLUE_plots_two_years, phenotype_scatterplots,
     return(current_filename)
   }
   
+  # Correlation plots
+  export_correlation_plots <- function(correlation_data, test_name, file_ext = "pdf"){
+    
+    # Get a filepath to save the plot to
+    current_filename <- paste0(export_dir, "/supplemental/", test_name, "correlation_plot.", file_ext)
+    
+    current_plot <- pluck(correlation_data, "correlation_plot")
+    
+    # Save the plot to the filepath
+    ggsave(filename = current_filename, 
+           plot = current_plot, 
+           device = file_ext, 
+           width = 8, 
+           height = 8, 
+           units = "in")
+    
+    # And return the path
+    return(current_filename)
+  }
+  
+  all_correlation_plots <- map2_chr(correlation_plots, names(correlation_plots), export_correlation_plots)
   
   # Export all plots
   all_scatter_heatmaps <- map2_chr(scatter_heatmap_all, names(scatter_heatmap_all), export_scatter_heatmaps)
@@ -103,5 +134,7 @@ export_phenotype_plots <- function(BLUE_plots_two_years, phenotype_scatterplots,
[…]

### 2022-06-02 R/make_elite_summary_tables.R

@@ -321,8 +321,8 @@ make_elite_summary_tables <- function(blue_data = genotype_BLUEs,
   high_protein <- c("N18-1761", "N18-1575", "N18-1769", "N18-1763", "N18-1855")
   
   # 10 highest p + o
-  high_po <- c("N18-1761", "N18-1575", "N18-1769", "N18-1632-2", "N18-1855", "N18-1763", "N18-1595", "N18-1731", 
-               "N18-1674", "N18-1674")
+  high_po <- c("N18-1761", "N18-1575", "N18-1769", "N18-1632-2", "N18-1855", 
+               "N18-1763", "N18-1595", "N18-1731", "N18-1674", "N18-1674")
   
   # High pro, similar yield
   hp_sy <- c("N18-1572", "N18-1595", "N18-1620", "N18-1632-1", "N18-1635", 

### 2022-06-02 _targets.R

@@ -163,6 +163,11 @@ tar_plan(
                                       all_data   = all_yield_data$two_year, 
                                       util_tables)),
   
+  # A supplementary table with all the contrasts data
+  tar_target(contrast_export, 
+             export_contrasts(genotype_contrasts_mixed, util_tables, exportdir = here("exports", "data", "supplementary")), 
+             format = "file"),
+  
 # A example latex table to use for testing targets with the manuscript template
   tar_target(example_table, 
              make_example_table()),
@@ -218,8 +223,11 @@ tar_target(elite_genotype_tables,
              export_phenotype_plots(BLUE_plots_two_years, 
                                     phenotype_scatterplots, 
                                     labelled_test_histograms,
+                                    correlation_plots,
                                     export_dir = here("exports", "plots")), 
              format = "file"),
+
+
 
 
   

### 2022-06-02 packages.R

@@ -31,7 +31,8 @@ pacman::p_load(ggthemes,
                scales, 
                DiagrammeRsvg, 
                DiagrammeR, 
-               rsvg)
+               rsvg, 
+               cowplot)
 
 # Analysis
 pacman::p_load(metan,

### 2022-06-03 doc/manuscript/manuscript.Rmd
Added more to manuscript. Some changes to add the lsmean plot to the main document

@@
   These authors contributed equally to this work.
-correspondence: |
-  leutnant@fh-muenster.de; Tel.: +XX-000-00-0000.
 journal: Agronomy
@@
 abbreviations:
-  - short: MDPI
-    long: Multidisciplinary Digital Publishing Institute
-  - short: DOAJ
-    long: Directory of open access journals
-  - short: TLA
-    long: Three letter acronym
-  - short: LD 
-    long: linear dichroism
+  - short: RIL
+    long: Recombinant inbred line
+  - short: RCBD
+    long: Randomized complete block design
+  - short: CLA
+    long: Central crops research station
+  - short: CAS
+    long: Caswell research farm
+  - short: PLY  
+    long: Tidewater research station
 output: rticles::mdpi_article
@@
            yield_summary_tables, 
-           elite_genotype_tables))
+           elite_genotype_tables, 
+           phenotype_summary_plots))
 ```
@@
 
+## Experimental design
+
 These four tests were grown in two locations in 2019: the Tidewater Research Station in Plymouth, NC (PLY) and the Caswell Research Farm in Kinston, NC (CAS).
@@
 These tests were grown in CLA and CAS in 2020 and CAS and PLY in 2021.
+RILs were grown in a randomized complete block design with four replications in each location.
 The same phenotypes were evaluated for each genotype in the 2020 and 2021 seasons using the same methodology that was employed in the 2019 season.
@@
 The emmeans package was also used to calculate contrasts as a post-hoc test to compare RIL phenotype means to check means for all collected phenotypes.
-A sidak adjustment was used to account for multiple comparisons in the calculation of contrasts.
+A sidak adjustment was used to account for multiple comparisons in the calculation of contrasts.Pearson correlation coefficients between each phenotype were calculated with the metan package.
+Pearson correlation coefficients between each phenotype were calculated with the metan package as well.
 
-Pearson correlation coefficients between each phenotype were calculated with the metan package.
-
-Pearson correlation is calculated for each pair of traits as:
+The pearson correlation is calculated for each pair of traits as:
 
@@
 
+```{r, lsmean_plot_link, echo = FALSE}
+
+# Get the link to the lsmean scatterplot
+mean_plot_link <- phenotype_summary_plots[grepl("lsmean_scatterplot", phenotype_summary_plots)]
+
+```
+
+```{=tex}
+\begin{figure}[H]
+\centering
+\includegraphics[width=15 cm]{`r mean_plot_link`}
+\caption{Genotype Least square means for seed oil, seed protein, and seed yield for soybean RILs in Test 1 (\textbf{A}) and Test 2 (\textbf{B}).
+Points indicate the least square means and error bars indicate the standard errors in the estimation of least square means.
+Blue dots indicate that a RIL has a least square mean above the average of the checks in the test and a color of red indicates that the RIL has a mean value below the check average.
+The check average is shown with the vertical dashed line.}
+\end{figure}
+```
+
 ## Yield contrasts
@@
 
-## Genotypes with comparable yield and oil and superior protein
+## Genotypes with comparable seed yield and seed oil and superior seed protein content
 Four genotypes had yield and oil that was similar to that of the yield checks, and seed protein that was greater than the average of the checks.
@@
 
-```{=tex}
-\begin{figure}[H]
-\centering
-\includegraphics[width=15 cm]{C:/Users/Jay/Documents/R/Projects/Jay_yield/exports/plots/supplemental/supplemental_figure_1.pdf}
-\caption{This is a figure, Schemes follow the same formatting.
-If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
-(\textbf{b}) Description of what is contained in the second panel.
-Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.}
-\end{figure}
-```
-
 # Conclusion

### 2022-06-03 doc/manuscript/manuscript.tex
Added more to manuscript. Some changes to add the lsmean plot to the main document

@@
 % Contact information of the corresponding author
-\corres{Correspondence: \href{mailto:leutnant@fh-muenster.de}{\nolinkurl{leutnant@fh-muenster.de}};
-Tel.: +XX-000-00-0000.}
+\corres{Correspondence: }
 
@@
 
+\hypertarget{experimental-design}{%
+\subsection{Experimental design}\label{experimental-design}}
+
 These four tests were grown in two locations in 2019: the Tidewater
@@
 These two tests were grown in both the 2020 and 2021 seasons. These
-tests were grown in CLA and CAS in 2020 and CAS and PLY in 2021. The
-same phenotypes were evaluated for each genotype in the 2020 and 2021
-seasons using the same methodology that was employed in the 2019 season.
+tests were grown in CLA and CAS in 2020 and CAS and PLY in 2021. RILs
+were grown in a randomized complete block design with four replications
+in each location. The same phenotypes were evaluated for each genotype
+in the 2020 and 2021 seasons using the same methodology that was
+employed in the 2019 season.
 
@@
 A sidak adjustment was used to account for multiple comparisons in the
-calculation of contrasts.
+calculation of contrasts.Pearson correlation coefficients between each
+phenotype were calculated with the metan package. Pearson correlation
+coefficients between each phenotype were calculated with the metan
+package as well.
 
-Pearson correlation coefficients between each phenotype were calculated
-with the metan package.
-
-Pearson correlation is calculated for each pair of traits as:
+The pearson correlation is calculated for each pair of traits as:
 
@@
 
+\begin{figure}[H]
+\centering
+\includegraphics[width=15 cm]{C:/Users/Jay/Documents/R/Projects/Jay_yield/exports/plots/lsmean_scatterplot.pdf}
+\caption{Genotype Least square means for seed oil, seed protein, and seed yield for soybean RILs in Test 1 (\textbf{A}) and Test 2 (\textbf{B}).
+Points indicate the least square means and error bars indicate the standard errors in the estimation of least square means.
+Blue dots indicate that a RIL has a least square mean above the average of the checks in the test and a color of red indicates that the RIL has a mean value below the check average.
+The check average is shown with the vertical dashed line.}
+\end{figure}
+
 \hypertarget{yield-contrasts}{%
@@
 
-\hypertarget{genotypes-with-comparable-yield-and-oil-and-superior-protein}{%
-\subsection{Genotypes with comparable yield and oil and superior
-protein}\label{genotypes-with-comparable-yield-and-oil-and-superior-protein}}
+\hypertarget{genotypes-with-comparable-seed-yield-and-seed-oil-and-superior-seed-protein-content}{%
+\subsection{Genotypes with comparable seed yield and seed oil and
+superior seed protein
+content}\label{genotypes-with-comparable-seed-yield-and-seed-oil-and-superior-seed-protein-content}}
 
@@
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=15 cm]{C:/Users/Jay/Documents/R/Projects/Jay_yield/exports/plots/supplemental/supplemental_figure_1.pdf}
-\caption{This is a figure, Schemes follow the same formatting.
-If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
-(\textbf{b}) Description of what is contained in the second panel.
-Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.}
-\end{figure}
-
 \hypertarget{conclusion}{%
@@
 \begin{tabular}{@{}ll}
-MDPI & Multidisciplinary Digital Publishing Institute \\
-DOAJ & Directory of open access journals \\
-TLA & Three letter acronym \\
-LD & linear dichroism \\
+RIL & Recombinant inbred line \\
+RCBD & Randomized complete block design \\
+CLA & Central crops research station \\
+CAS & Caswell research farm \\
+PLY & Tidewater research station \\
 \end{tabular}}

### 2022-06-03 R/export_phenotype_plots.R

@@ -38,7 +38,7 @@ export_phenotype_plots <- function(BLUE_plots_two_years, phenotype_scatterplots,
   # All filepaths to the saved scatterplots
   all_scatterplots <- export_scatterplots(phenotype_scatterplots$side_by_side)
   
-  both_plots_scatter_filepath <- paste0(export_dir, "/supplemental/", "supplemental_figure_1.pdf")
+  both_plots_scatter_filepath <- paste0(export_dir, "/", "lsmean_scatterplot.pdf")
   
   ggsave(filename = both_plots_scatter_filepath, 
          plot = phenotype_scatterplots$combined, 

### 2022-06-03 R/make_phenotype_scatterplots.R

@@ -79,7 +79,8 @@ make_phenotype_scatterplots <- function(mixed_models_two_years, util_tables, phe
       geom_vline(xintercept = pheno_check_avg, lty = 2, size = 1.1) + 
       scale_fill_manual(values = c("blue", "red")) + 
       theme(legend.title = element_blank(), 
-                    panel.grid.major.y = element_line(colour = "light grey", size = 0.25)) + 
+            panel.grid.major.y = element_line(colour = "light grey", size = 0.25), 
+            legend.text = element_text(size = 20)) + 
       theme_jay_yield_base()
     
     return(p)
@@ -102,14 +103,16 @@ make_phenotype_scatterplots <- function(mixed_models_two_years, util_tables, phe
     split_data <- test_data %>% 
       metan::split_factors(test_name)
     
-    arrange_pheno_plots <- function(split_test_data = split_data){
+    arrange_pheno_plots <- function(split_test_data = split_data, keep_legend = TRUE){
+      
+      legend_string <- ifelse(keep_legend, "bottom", "none")
       
       # Arrange the scatterplots horizontally beside each other
       p <- ggarrange(plotlist      = split_test_data$scatterplot, 
                      nrow          = 1, 
                      ncol          = nrow(split_test_data), 
                      common.legend = TRUE, 
-                     legend        = "bottom")
+                     legend        = legend_string)
       
       # Add a title that is just the test name
       # annotate_figure(p, top = text_grob(test_name, face = "bold", size = 16))
@@ -118,9 +121,23 @@ make_phenotype_scatterplots <- function(mixed_models_two_years, util_tables, phe
     
     # Apply the function to the split data to make a set of side-by-side plots
     # for each phenotype
-    split_data_plots <- map(split_data, arrange_pheno_plots)
+    split_data_plots <- map(split_data, arrange_pheno_plots) %>% 
+      set_names(names(split_data))
     
-    return(split_data_plots)
+    # And do this separately for each plot so that the first one has no legend
+    test_1_no_legend <- arrange_pheno_plots(split_data[[1]], keep_legend = FALSE)
+    test_2           <- arrange_pheno_plots(split_data[[2]])
+    
+    both_tests <- list(test_1_no_legend, test_2)
+    
+    combined_plot <- plot_grid(plotlist = both_tests, 
+                               labels = list("A", "B"), 
+                               ncol = 1, nrow = 2) 
+    
+    res <- list("side_by_side" = split_data_plots, 
[…]

### 2022-06-05 doc/manuscript/manuscript.Rmd
Added to manuscript

@@
 source(here("packages.R"))
-tar_load(c(example_table, 
-           yield_summary_tables, 
+tar_load(c(yield_summary_tables, 
            elite_genotype_tables, 
@@
 Three high-yielding check cultivars and the two parents of the respective population were also included in each test.
+These yield tests were named test 1 and test 2 for RILs derived from mapping population 201 and test 3 and 4 for RILs derived from mapping population 202.
 Yield check cultivars Dunphy, Osage[@Osage], and Roy were used in tests 1 and 2, while Dunphy, Dilday, and NC-Raleigh[@NCRaleighregistration] were used for tests 3 and 4.
@@
 Yield check cultivars were again assigned to each test to match the maturity dates of the RILs that were in each test.
-Cultivars Dunphy, DIlday, and NC-Raleigh were used as checks in Test 1 and Dunphy, Ellis, N10-697, and Osage were used as checks in Test 2.
+Cultivars Dunphy, Dilday, and NC-Raleigh were used as checks in Test 1 and Dunphy, Ellis, N10-697, and Osage were used as checks in Test 2.
 
@@
 
+Genotype least square means were calculated for all RILs in both tests.
+A visualization of these least square means and the standard error on the estimation of these means for seed protein, seed oil, and seed yield can be seen in figure 1.
+Both tests tended to have more RILs with high protein rather than high oil when compared to the average of the checks, and a moderate number had a yield average greater than the average of the checks.
+Qualitatively, many RILs had a comparable yield to the checks following the relatively large standard error associated with the estimating the yield, and a qualitatively larger seed protein content given the relatively small standard error associated with the estimation of seed protein content.
+To separate means quantitatively, we performed contrasts between each RIL mean and the average of the checks for each test.
+
 ## Yield contrasts
-Several RILs in each of the tests had yield that was comparable to that of their check cultivars.
-This was determined both quantitatively through the use of contrasts between the mean of each RIL with the average of the yield check means, and qualitatively by inspecting the standard errors on the estimation of the genotype marginal means for yield.
+Several RILs in each of the tests had yield that was comparable to that of their check cultivars as per contrasts between RIL means and the average of the check cultivars for each test.
 No genotypes had yield that was quantitatively higher than that of the yield checks, however many had comparable yield.
@@
 
-A strong negative correlation was observed in both populations betweeen seed oil and seed protein.
-This observation matches well with previous findings on the inverse correlation between seed protein and seed oil.
+A strong negative correlation was observed in both populations between seed oil and seed protein, and a weak inverse correlation was observed between seed protein and seed yield.
+This observation matches well with previous findings on the inverse correlation between seed protein and seed oil, and between seed protein and seed yield.
 Many RILs had high protein when compared with the check cultivars so it was not surprising that relatively few had both a superior seed protein content, and a comparable seed oil content.
 
+These RILs can provide valuable germplasm that can be used to simultaneously improve both seed oil and seed protein content without compromising seed yield or agronomics.
+This can be of use both to breeders that are looking to improve seed composition traits in soybean and for growers who are seeking options for novel soybean varieties with seed composition that is superior to that of cultivars that are already used in production.
+
 ## Genotypes with comparable yield and superior protein
-Seventeen RILs had a similar yield and superior protein content to the check cultivars. Summary data for the seed protein and seed yield of these lines is given in table 2. The maximum yielding line
+Seventeen RILs had a similar yield and superior protein content to the check cultivars.
+Summary data for the seed protein and seed yield of these lines is given in table 2.
+From among these RILs, N18-1627 had the highest seed yield relative to the checks included in the test with an average yield that was 105.9% that of the check average of Test 2.
+Genotype N18-1763 had the highest seed protein content on average with a protein content that was 116.8% that of the check average of Test 1.
+We observed a negative correlation between seed protein and seed yield in both tests so RILs with seed protein content that was above the check average tended to have a seed yield content that was comparatively lower.
 
@@
 
-Among these genotypes are several with both average seed protein and average seed yield that were greater than the averages of the checks for each test.
+However, among these genotypes are several with both average seed protein and average seed yield that were greater than the averages of the checks for each test.
 These N18-1632-1, N18-1620, N18-1635 from test 1 and RILs N18-1761 and N18-1627 from test 2.
 Of particular note are genotypes N18-1632-1 from test 1 and N18-1761 from test 2.
-On average, genotype N18-1632-1 had a protein content that was 113.9% of the check average while maintaining a yield average that was 101.5% that of the check average.
+These two RILs have a seed protein content that is substantially above that of the average protein content of he checks while also maintaining an average yield that is above the average yield of the checks.
+These RILs are ideal candidates for use in breeding programs which seek to improve seed protein content in particular without compromising seed yield or argonomics.
 

### 2022-06-05 doc/manuscript/manuscript.tex
Added to manuscript

@@
 high-yielding check cultivars and the two parents of the respective
-population were also included in each test. Yield check cultivars
-Dunphy, Osage\citep{Osage}, and Roy were used in tests 1 and 2, while
-Dunphy, Dilday, and NC-Raleigh\citep{NCRaleighregistration} were used
-for tests 3 and 4. These lines were selected to represent the estimated
-maturities of the RILs in each test. The parents for tests 1 and 2 were
-cultivars LMN09-119 and N09-09, and the parents for tests 3 and 4 were
-LMN09-19 and N13-47.
+population were also included in each test. These yield tests were named
+test 1 and test 2 for RILs derived from mapping population 201 and test
+3 and 4 for RILs derived from mapping population 202. Yield check
+cultivars Dunphy, Osage\citep{Osage}, and Roy were used in tests 1 and
+2, while Dunphy, Dilday, and NC-Raleigh\citep{NCRaleighregistration}
+were used for tests 3 and 4. These lines were selected to represent the
+estimated maturities of the RILs in each test. The parents for tests 1
+and 2 were cultivars LMN09-119 and N09-09, and the parents for tests 3
+and 4 were LMN09-19 and N13-47.
 
@@
 maturity dates of the RILs that were in each test. Cultivars Dunphy,
-DIlday, and NC-Raleigh were used as checks in Test 1 and Dunphy, Ellis,
+Dilday, and NC-Raleigh were used as checks in Test 1 and Dunphy, Ellis,
 N10-697, and Osage were used as checks in Test 2.
@@
 \centering
-\includegraphics[width=15 cm]{C:/Users/Jay/Documents/R/Projects/Jay_yield/exports/plots/lsmean_scatterplot.pdf}
+\includegraphics[width=15 cm]{C:/Users/Jay/Desktop/Documents/R/Jay_yield/exports/plots/lsmean_scatterplot.pdf}
 \caption{Genotype Least square means for seed oil, seed protein, and seed yield for soybean RILs in Test 1 (\textbf{A}) and Test 2 (\textbf{B}).
@@
 
+Genotype least square means were calculated for all RILs in both tests.
+A visualization of these least square means and the standard error on
+the estimation of these means for seed protein, seed oil, and seed yield
+can be seen in figure 1. Both tests tended to have more RILs with high
+protein rather than high oil when compared to the average of the checks,
+and a moderate number had a yield average greater than the average of
+the checks. Qualitatively, many RILs had a comparable yield to the
+checks following the relatively large standard error associated with the
+estimating the yield, and a qualitatively larger seed protein content
+given the relatively small standard error associated with the estimation
+of seed protein content. To separate means quantitatively, we performed
+contrasts between each RIL mean and the average of the checks for each
+test.
+
 \hypertarget{yield-contrasts}{%
@@
 Several RILs in each of the tests had yield that was comparable to that
-of their check cultivars. This was determined both quantitatively
-through the use of contrasts between the mean of each RIL with the
-average of the yield check means, and qualitatively by inspecting the
-standard errors on the estimation of the genotype marginal means for
-yield. No genotypes had yield that was quantitatively higher than that
-of the yield checks, however many had comparable yield. Many of these
-genotypes with comparable yield also had protein content that was
-superior to the check average in each test. No genotypes had oil that
-was superior to the check cultivars, but some had comparable yield and
-oil content as well as superior protein content.
+of their check cultivars as per contrasts between RIL means and the
+average of the check cultivars for each test. No genotypes had yield
+that was quantitatively higher than that of the yield checks, however
+many had comparable yield. Many of these genotypes with comparable yield
+also had protein content that was superior to the check average in each
+test. No genotypes had oil that was superior to the check cultivars, but
+some had comparable yield and oil content as well as superior protein
+content.
 
@@
 
-A strong negative correlation was observed in both populations betweeen
-seed oil and seed protein. This observation matches well with previous
-findings on the inverse correlation between seed protein and seed oil.
-Many RILs had high protein when compared with the check cultivars so it
-was not surprising that relatively few had both a superior seed protein
-content, and a comparable seed oil content.
+A strong negative correlation was observed in both populations between
+seed oil and seed protein, and a weak inverse correlation was observed
+between seed protein and seed yield. This observation matches well with
+previous findings on the inverse correlation between seed protein and
+seed oil, and between seed protein and seed yield. Many RILs had high
+protein when compared with the check cultivars so it was not surprising
+that relatively few had both a superior seed protein content, and a
+comparable seed oil content.
+
+These RILs can provide valuable germplasm that can be used to
+simultaneously improve both seed oil and seed protein content without
+compromising seed yield or agronomics. This can be of use both to
+breeders that are looking to improve seed composition traits in soybean
+and for growers who are seeking options for novel soybean varieties with
+seed composition that is superior to that of cultivars that are already
+used in production.
 
@@
 check cultivars. Summary data for the seed protein and seed yield of
-these lines is given in table 2. The maximum yielding line
+these lines is given in table 2. From among these RILs, N18-1627 had the
+highest seed yield relative to the checks included in the test with an
+average yield that was 105.9\% that of the check average of Test 2.
+Genotype N18-1763 had the highest seed protein content on average with a
+protein content that was 116.8\% that of the check average of Test 1. We
+observed a negative correlation between seed protein and seed yield in
+both tests so RILs with seed protein content that was above the check
+average tended to have a seed yield content that was comparatively
+lower.
 
@@
 
-Among these genotypes are several with both average seed protein and
-average seed yield that were greater than the averages of the checks for
-each test. These N18-1632-1, N18-1620, N18-1635 from test 1 and RILs
-N18-1761 and N18-1627 from test 2. Of particular note are genotypes
-N18-1632-1 from test 1 and N18-1761 from test 2. On average, genotype
-N18-1632-1 had a protein content that was 113.9\% of the check average
-while maintaining a yield average that was 101.5\% that of the check
-average.
+However, among these genotypes are several with both average seed
+protein and average seed yield that were greater than the averages of
+the checks for each test. These N18-1632-1, N18-1620, N18-1635 from test
+1 and RILs N18-1761 and N18-1627 from test 2. Of particular note are
+genotypes N18-1632-1 from test 1 and N18-1761 from test 2. These two
+RILs have a seed protein content that is substantially above that of the
+average protein content of he checks while also maintaining an average
+yield that is above the average yield of the checks. These RILs are
+ideal candidates for use in breeding programs which seek to improve seed
+protein content in particular without compromising seed yield or
+argonomics.
 

### 2022-06-30 doc/manuscript/manuscript.Rmd
Added revisions to the manuscript.rmd file in the pdf file directory

@@
 abstract: |
-  In current markets, the primary uses for soybean seed are in products derived from 
-  it's oil or protein content. However, growers are compensated based on seed oil so 
-  a more valuable crop is one with both high yield, and high protein, oil, or a combination of the two. A negative 
-  correlation between seed yield and seed protein makes improving these traits simultaneously difficult but 
-  not impossible through conventional breeding. A selection of lines with exceptional yield and seed 
-  composition qualities was made from two recombinant inbred line (RIL) soybean mapping populations to identify soybean
-  varieties with yield comparable to existing cultivars, and seed composition traits superior to existing cultivars.
-The performance of these RILs were evaluated in multiple environments and several genotypes were identified with yield comparable to that of existing high-performance cultivars with seed protein and or oil that is equal to or superior to the high-performing cultivars.
-These genotypes will provide breeders with additional sources of germplasm for continuing efforts to improve seed composition traits, and provide growers with valuable genotype options.
+ In current markets, the primary uses for soybean seed are in products derived from it’s oil or protein content.
+However, growers are compensated based on seed yield  so a more valuable crop is the one that is high yielding with an optimum combination of protein and oil.
+A negative correlation of seed protein with seed yield and oil makes simultaneous improvement of  these traits difficult but not impossible through conventional breeding.
+A selection of lines with exceptional yield and seed composition qualities was made from two recombinant inbred line (RIL) soybean mapping populations to identify high protein and/or high oil lines with yield comparable to elite cultivars.
+The performance of these RILs were evaluated in multiple environments and several genotypes were identified with yield comparable to that of high yielding check cultivars with seed protein and/or oil superior to the checks.
+These genotypes will provide breeders with additional sources of germplasm for continuing efforts to improve seed composition traits without compromising seed yield, and provide growers with more profitable varieties.
 keywords: |
@@
 
-Seed yield, oil, and protein are all valuable traits in a soybean variety, however breeding lines which have both high yield and protein has been difficult to develop due to the negative correlation between the two traits[@burton1987quantitative; @ProtOilCorr; @ProtOilCorr_new].
+Seed yield, oil, and protein are all valuable traits in a soybean variety, however breeding lines which have both high yield and high protein has been difficult to develop due to the negative correlation between the two traits [@burton1987quantitative; @ProtOilCorr; @ProtOilCorr_new].
 While considerable efforts have been made to identify loci which control these seed quality traits so that MAS breeding strategies can be utilized for their improvement, to date the applications of such markers have been few.
 This is largely due to the lack of markers which are uniquely associated with one trait, and are also stable across genetic and environmental backgrounds.
-While there is still reason to continue this genetic research, it is important that breeders take every opportunity to identify lines with both high yield, and seed composition traits like oil and protein content so that new varieties can be released.
+While there is still reason to continue this genetic research, it is important that breeders take every opportunity to identify lines with both high yield, and desirable seed composition traits like oil and protein content so that new value-added varieties can be more profitable.
 
-Soybean lines typically contain about 20% oil and 40% protein content on a dry weight basis[@ProteinGenomics].
-The market for soybean meal requires 47.5% protein content in the meal, which corresponds to approximately 41.5% protein content on a dry weight basis[@ProteinGenomics].
-Oil and protein content are two of the most important seed composition traits in soybean so if one is decreased, the other should be correspondingly increased to account for the loss in value.
+Soybean lines typically contain about 20% oil and 40% protein content on a dry weight basis [@ProteinGenomics].
+The market for soybean meal requires 47.5% protein content in the meal, which corresponds to approximately 41.5% protein content with 21% oil, on a dry weight basis[@ProteinGenomics].
+Oil and protein content are two of the most important seed composition traits in soybean, so if one is decreased, the other should be correspondingly increased.
 The inverse correlation between protein and oil contents is well known and is suspected to be due at least partially to the action of pleiotropic genes and competing metabolic pathways which control the expression of each trait[@SeedCompositionGenomics].
 
-Despite the difficulty in simultaneously breeding for all three of these traits, releases of varieties with elevated protein contents and only moderately reduced yield has shown that it is not impossible.
-The high protein germplasm lines R05-1415 and R05-1772 were released recently and contain 46.9% and 46.1% protein content with while still producing yields 94% and 91% of that of the high yielding 5002T cultivar[@HiProtHiYield02].
-Lines TN03-350 and TN04-5321 contain 43.9% and 43.1% protein content while having superior or comparable performance to yield checks[@HiProtHiYield04].
-The Prolina cultivar has a protein content of 46.1% with a yield only 13% reduced from the Centennial check[@HiProtHiYield01].
-The Highpro1 cultivar was released in 2016 and has a yield which is greater than or equal to 97% of that of the highest yielding check cultivar, IA3023 with a protein content of 40.1%[@HighPro1].
-Cultivars produced through conventional breeding techniques such as these have shown that it is possible to identify lines with both high seed protein and seed yield.
-Efforts to find these lines should be continued to provide growers and breeders with additional high value cultivars, and germplasm which can be further used to improve protein and yield traits.
+Despite the difficulty in simultaneously breeding for all three of these traits, varieties with elevated protein contents with little or no yield reduction has been released by public sector breeders.
+The high protein germplasm lines R05-1415 and R05-1772 were released recently that contain 46.9% and 46.1% protein content with 94% and 91% yield, respectively, of the high yielding  cultivar 5002T[@HiProtHiYield02].
+Cultivars TN03-350 and TN04-5321 contain 43.9% and 43.1% protein while having superior or comparable yields with checks cultivars[@HiProtHiYield04].).
+The Highpro1 cultivar was released in 2016 and has a yield which is greater than or equal to that of the check cultivars, while its protein content was 5-6% higher than the checks[@HighPro1].Cultivars produced through conventional breeding techniques such as these have shown that it is possible to identify lines with both high seed protein and seed yield.
+Efforts to find these lines should continue to provide growers and breeders with additional high value cultivars and germplasm which can be used to further improve protein and yield traits.
 
-To meet this goal, two recombinant inbred line (RIL) oil mapping populations were screened for lines which showed promising combinations of yield and seed composition traits.
-Successive rounds of selection were conducted to identify and characterize lines with high values for yield as well as protein and oil composition were performed between 2018 and 2021 to identify soybean lines with yield comparable to existing check cultivars and protein and or oil composition superior to that of the check cultivars.
+To meet this goal, two recombinant inbred line (RIL) mapping populations were screened for lines which showed promising combinations of yield and seed composition traits.
+Successive rounds of selection were conducted between 2018 and 2021 to identify and characterize lines with high values for yield as well as protein and oil composition.
 
@@
 These populations consisted of 273 and 237 recombinant inbred lines (RILs) respectively.
-Several agronomic traits were scored in the field for each population.
 
@@
 Lodging was scored on a scale of 1-5 where 5 indicates that all plants in a plot are on the ground, and a score of 1 indicates that all plants are erect[@fehr1987soybeans].
-The agronomic score aimed to capture other traits of value such as visual estimation of pod load and plot uniformity to provide a general score of a line's agronomic desirability.
+The agronomic score aimed to capture other traits of value such as visual estimation of pod load and plot uniformity to provide a general score of a line’s agronomic desirability.
 Agronomic score was recorded on a scale of 1-5 as well, with 1 identifying the best lines of a population, and 5 the worst.
@@
 Protein and oil contents were measured on a dry basis using a Perten DA 7250 NIR®instrument.
-Yield and seed weight were measured after seed had been sifted and cleaned of debris and cracked seed.
+Yield and seed weight were measured after seed had been sifted and cleaned of debris.
 
-To select lines for the 2019 growing season, lines with abnormally low bulk weights or extreme maturity dates from 2018 were first removed from consideration.
-Two yield trials were then developed for each mapping population.
-The maturity dates of RILs were considered when forming tests such that the lines of each test would have a maturity date range approximately half that of the total mapping population from which it was derived.
-RILs were selected for each test which were also representative of the distribution of seed protein and seed oil traits for each population.
-
-Eighty unique lines were selected from each population which satisfied these criteria, and each yield test was comprised of 40 RILs.
-Three high-yielding check cultivars and the two parents of the respective population were also included in each test.
+To select lines for the yield tests in 2019 growing season, lines with low seed yield or extreme maturity dates in 2018 were removed from consideration.
+Two yield trials were then designed for each mapping population based on maturity dates and desirable agronomic traits, protein and oil contents.
+Eighty unique lines were selected from each population which satisfied these criteria, and each yield test had 40 RILs.
+Three high-yielding check cultivars and the two parents of the respective population were also included in each test based on the maturity spread of the RILs.
 These yield tests were named test 1 and test 2 for RILs derived from mapping population 201 and test 3 and 4 for RILs derived from mapping population 202.
-Yield check cultivars Dunphy, Osage[@Osage], and Roy were used in tests 1 and 2, while Dunphy, Dilday, and NC-Raleigh[@NCRaleighregistration] were used for tests 3 and 4.
-These lines were selected to represent the estimated maturities of the RILs in each test.
+Yield check cultivars Dunphy, Osage, and Roy were used in tests 1 and 2, while Dunphy, Dilday, and NC-Raleigh were used for tests 3 and 4.
 The parents for tests 1 and 2 were cultivars LMN09-119 and N09-09, and the parents for tests 3 and 4 were LMN09-19 and N13-47.
@@
 
-These four tests were grown in two locations in 2019: the Tidewater Research Station in Plymouth, NC (PLY) and the Caswell Research Farm in Kinston, NC (CAS).
-The same data was collected for each test in this season that was collected in the previous season.
+These four tests were grown in two locations in 2019 - the Tidewater Research Station in Plymouth, NC (PLY) and the Caswell Research Farm in Kinston, NC (CAS).
+The same data as earlier were collected for each test in this season.
 
-Using the data collected from the 2019 season season, further selections were done to identify high-yielding lines from the four tests.
-This was done by identifying the RILs with a yield within or above a least significant difference (LSD) of the average yield of the checks for each test.
-Further selection was done using the seed composition traits by identifying the thirty RILs with the highest protein + oil content on a dry basis from among the RILs which had passed the yield selection threshold.
+Based the data collected from the 2019 season season, further selections were done to identify fewer lines from the four tests for further yield testing.
+This was done by identifying the RILs with a yield at or above the average yield of the checks in each test.
+Further selection was done using the seed composition traits by identifying the thirty RILs with the highest protein + oil content among the RILs which had passed the yield selection threshold.
 
 These thirty lines were then grouped into two new tests of 15 RILs each based on maturity date.
-These two new tests are named Test 1 and Test 2.
+These two new tests were named Test 1 and Test 2.
 Yield check cultivars were again assigned to each test to match the maturity dates of the RILs that were in each test.
@@
 RILs were grown in a randomized complete block design with four replications in each location.
-The same phenotypes were evaluated for each genotype in the 2020 and 2021 seasons using the same methodology that was employed in the 2019 season.
+The same phenotypes were evaluated for each line each season using the same methodology that was employed in the 2019 season.
 
@@
 ## Phenotypic correlations
-A strong negative correlation was observed in both tests between seed protein and seed oil content.
-A coefficient of r = -0.93 was observed in both populations.
-A negative correlation was observed between seed protein and yield with correlation coefficient of r = -0.29 was observed in both tests.
-This correlation was not statistically significant in either population.
-A weak positive correlation was observed between seed oil and seed yield in both populations.
+A strong negative correlation (r = -0.93) was observed in both tests between seed protein and seed oil content.
+A weak negative correlation (r = -0.29) was observed between seed protein and yield in both tests which was statistically insignificant in either population.
+Weak positive correlations were also observed between seed oil and seed yield in both populations.
 A correlation coefficient of r = 0.24 was observed in Test 1 while a coefficient of r = 0.28 was observed in Test 2.
 These correlation coefficients were not statistically significant in either population.
-Visualizations of the pairwise correlation coefficients for Tests 1 and 2 can be seen in supplementary figures 2 and 3, respectively.
+The pairwise correlation coefficients for Tests 1 and 2 are presented in supplementary figures 2 and 3, respectively.
 
@@
 Several RILs in each of the tests had yield that was comparable to that of their check cultivars as per contrasts between RIL means and the average of the check cultivars for each test.
-No genotypes had yield that was quantitatively higher than that of the yield checks, however many had comparable yield.
+No genotypes had yield that was higher than that of the yield checks, however many had comparable yield.
 Many of these genotypes with comparable yield also had protein content that was superior to the check average in each test.
 No genotypes had oil that was superior to the check cultivars, but some had comparable yield and oil content as well as superior protein content.
+Such genotypes are extremely valuable for production of soybean meal with higher protein.
+As mentioned earlier, the meal protein of current U.S.
+cultivars is mostly below the minimum market standard of 47.5%.
+The meal protein is calculated by a formula that takes both seed protein and oil contents into account (reference from Pantalone).
+The meal protein contents of these lines with high protein and normal oil contents ranged from xx – xx% compared to the meal protein contents of the checks (Supplementary table XX).
 
-RILs were also evaluated for lodging and seed quality.
+RILs were also evaluated for lodging and seed quality (data not shown?).
 All RILs had seed quality that was on par with that of the high-yielding checks however, however 11 genotypes had lodging scores that were statistically significantly greater than the checks on the basis of contrasts.
-These RILs were removed from consideration for recommendation on the basis of their relatively poor agronomic performance.
+These RILs were removed from consideration for recommendation on the basis of their relatively poor agronomic performance
 
@@
 These RILs can provide valuable germplasm that can be used to simultaneously improve both seed oil and seed protein content without compromising seed yield or agronomics.
-This can be of use both to breeders that are looking to improve seed composition traits in soybean and for growers who are seeking options for novel soybean varieties with seed composition that is superior to that of cultivars that are already used in production.
+This can be of use both to breeders who are looking to improve seed composition traits in soybean and for growers who are seeking options for novel soybean varieties with seed composition that is superior to that of elite cultivars.
 
@@
 Many of these genotypes have seed protein content that exceeds that of the check cultivars, and some of these with superior protein have a seed oil content that is comparable to these check cultivars as well.
-These genotypes have good agronomic qualities as well and will provide both breeders and growers with new options for genotypes that can be used in production or used in breeding programs that seek to improve valuable soybean seed composition traits.
+These genotypes have good agronomic qualities as well and will provide both breeders and growers with new options for genotypes that can be used in production or used in breeding programs that seek to improve valuable soybean seed composition traits with significantly reducing the yield.

### 2022-06-30 doc/manuscript/manuscript.tex
Added a a step to calculate protein meal and re-ran the pipeline. lsmeans seem to have been calculated without issue.
Also added protein meal to the phenotype name conversion utility tables.

@@
 products derived from it's oil or protein content. However, growers are
-compensated based on seed oil so a more valuable crop is one with both
-high yield, and high protein, oil, or a combination of the two. A
-negative correlation between seed yield and seed protein makes improving
-these traits simultaneously difficult but not impossible through
-conventional breeding. A selection of lines with exceptional yield and
-seed composition qualities was made from two recombinant inbred line
-(RIL) soybean mapping populations to identify soybean varieties with
-yield comparable to existing cultivars, and seed composition traits
-superior to existing cultivars. The performance of these RILs were
-evaluated in multiple environments and several genotypes were identified
-with yield comparable to that of existing high-performance cultivars
-with seed protein and or oil that is equal to or superior to the
-high-performing cultivars. These genotypes will provide breeders with
-additional sources of germplasm for continuing efforts to improve seed
-composition traits, and provide growers with valuable genotype options.}
+compensated based on seed yield so a more valuable crop is the one that
+is high yielding with an optimum combination of protein and oil. A
+negative correlation of seed protein with seed yield and oil makes
+simultaneous improvement of these traits difficult but not impossible
+through conventional breeding. A selection of lines with exceptional
+yield and seed composition qualities was made from two recombinant
+inbred line (RIL) soybean mapping populations to identify high protein
+and/or high oil lines with yield comparable to elite cultivars. The
+performance of these RILs were evaluated in multiple environments and
+several genotypes were identified with yield comparable to that of high
+yielding check cultivars with seed protein and/or oil superior to the
+checks. These genotypes will provide breeders with additional sources of
+germplasm for continuing efforts to improve seed composition traits
+without compromising seed yield, and provide growers with more
+profitable varieties.}
 
@@
 Seed yield, oil, and protein are all valuable traits in a soybean
-variety, however breeding lines which have both high yield and protein
-has been difficult to develop due to the negative correlation between
-the two
-traits\citep{burton1987quantitative, ProtOilCorr, ProtOilCorr_new}.
-While considerable efforts have been made to identify loci which control
-these seed quality traits so that MAS breeding strategies can be
-utilized for their improvement, to date the applications of such markers
-have been few. This is largely due to the lack of markers which are
-uniquely associated with one trait, and are also stable across genetic
-and environmental backgrounds. While there is still reason to continue
-this genetic research, it is important that breeders take every
-opportunity to identify lines with both high yield, and seed composition
-traits like oil and protein content so that new varieties can be
-released.
+variety, however breeding lines which have both high yield and high
+protein has been difficult to develop due to the negative correlation
+between the two traits
+\citep{burton1987quantitative, ProtOilCorr, ProtOilCorr_new}. While
+considerable efforts have been made to identify loci which control these
+seed quality traits so that MAS breeding strategies can be utilized for
+their improvement, to date the applications of such markers have been
+few. This is largely due to the lack of markers which are uniquely
+associated with one trait, and are also stable across genetic and
+environmental backgrounds. While there is still reason to continue this
+genetic research, it is important that breeders take every opportunity
+to identify lines with both high yield, and desirable seed composition
+traits like oil and protein content so that new value-added varieties
+can be more profitable.
 
 Soybean lines typically contain about 20\% oil and 40\% protein content
-on a dry weight basis\citep{ProteinGenomics}. The market for soybean
+on a dry weight basis \citep{ProteinGenomics}. The market for soybean
 meal requires 47.5\% protein content in the meal, which corresponds to
-approximately 41.5\% protein content on a dry weight
+approximately 41.5\% protein content with 21\% oil, on a dry weight
 basis\citep{ProteinGenomics}. Oil and protein content are two of the
-most important seed composition traits in soybean so if one is
-decreased, the other should be correspondingly increased to account for
-the loss in value. The inverse correlation between protein and oil
-contents is well known and is suspected to be due at least partially to
-the action of pleiotropic genes and competing metabolic pathways which
-control the expression of each trait\citep{SeedCompositionGenomics}.
+most important seed composition traits in soybean, so if one is
+decreased, the other should be correspondingly increased. The inverse
+correlation between protein and oil contents is well known and is
+suspected to be due at least partially to the action of pleiotropic
+genes and competing metabolic pathways which control the expression of
+each trait\citep{SeedCompositionGenomics}.
 
 Despite the difficulty in simultaneously breeding for all three of these
-traits, releases of varieties with elevated protein contents and only
-moderately reduced yield has shown that it is not impossible. The high
-protein germplasm lines R05-1415 and R05-1772 were released recently and
-contain 46.9\% and 46.1\% protein content with while still producing
-yields 94\% and 91\% of that of the high yielding 5002T
-cultivar\citep{HiProtHiYield02}. Lines TN03-350 and TN04-5321 contain
-43.9\% and 43.1\% protein content while having superior or comparable
-performance to yield checks\citep{HiProtHiYield04}. The Prolina cultivar
-has a protein content of 46.1\% with a yield only 13\% reduced from the
-Centennial check\citep{HiProtHiYield01}. The Highpro1 cultivar was
-released in 2016 and has a yield which is greater than or equal to 97\%
-of that of the highest yielding check cultivar, IA3023 with a protein
-content of 40.1\%\citep{HighPro1}. Cultivars produced through
-conventional breeding techniques such as these have shown that it is
-possible to identify lines with both high seed protein and seed yield.
-Efforts to find these lines should be continued to provide growers and
-breeders with additional high value cultivars, and germplasm which can
-be further used to improve protein and yield traits.
+traits, varieties with elevated protein contents with little or no yield
+reduction has been released by public sector breeders. The high protein
+germplasm lines R05-1415 and R05-1772 were released recently that
+contain 46.9\% and 46.1\% protein content with 94\% and 91\% yield,
+respectively, of the high yielding cultivar
+5002T\citep{HiProtHiYield02}. Cultivars TN03-350 and TN04-5321 contain
+43.9\% and 43.1\% protein while having superior or comparable yields
+with checks cultivars\citep{HiProtHiYield04}.). The Highpro1 cultivar
+was released in 2016 and has a yield which is greater than or equal to
+that of the check cultivars, while its protein content was 5-6\% higher
+than the checks\citep{HighPro1}.Cultivars produced through conventional
+breeding techniques such as these have shown that it is possible to
+identify lines with both high seed protein and seed yield. Efforts to
+find these lines should continue to provide growers and breeders with
+additional high value cultivars and germplasm which can be used to
+further improve protein and yield traits.
 
-To meet this goal, two recombinant inbred line (RIL) oil mapping
-populations were screened for lines which showed promising combinations
-of yield and seed composition traits. Successive rounds of selection
-were conducted to identify and characterize lines with high values for
-yield as well as protein and oil composition were performed between 2018
-and 2021 to identify soybean lines with yield comparable to existing
-check cultivars and protein and or oil composition superior to that of
-the check cultivars.
+To meet this goal, two recombinant inbred line (RIL) mapping populations
+were screened for lines which showed promising combinations of yield and
+seed composition traits. Successive rounds of selection were conducted
+between 2018 and 2021 to identify and characterize lines with high
+values for yield as well as protein and oil composition.
 
@@
 consisted of 273 and 237 recombinant inbred lines (RILs) respectively.
-Several agronomic traits were scored in the field for each population.
 
@@
 using a Perten DA 7250 NIR®instrument. Yield and seed weight were
-measured after seed had been sifted and cleaned of debris and cracked
-seed.
+measured after seed had been sifted and cleaned of debris.
 
-To select lines for the 2019 growing season, lines with abnormally low
-bulk weights or extreme maturity dates from 2018 were first removed from
-consideration. Two yield trials were then developed for each mapping
-population. The maturity dates of RILs were considered when forming
-tests such that the lines of each test would have a maturity date range
-approximately half that of the total mapping population from which it
-was derived. RILs were selected for each test which were also
-representative of the distribution of seed protein and seed oil traits
-for each population.
-
-Eighty unique lines were selected from each population which satisfied
-these criteria, and each yield test was comprised of 40 RILs. Three
-high-yielding check cultivars and the two parents of the respective
-population were also included in each test. These yield tests were named
-test 1 and test 2 for RILs derived from mapping population 201 and test
-3 and 4 for RILs derived from mapping population 202. Yield check
-cultivars Dunphy, Osage\citep{Osage}, and Roy were used in tests 1 and
-2, while Dunphy, Dilday, and NC-Raleigh\citep{NCRaleighregistration}
-were used for tests 3 and 4. These lines were selected to represent the
-estimated maturities of the RILs in each test. The parents for tests 1
-and 2 were cultivars LMN09-119 and N09-09, and the parents for tests 3
-and 4 were LMN09-19 and N13-47.
+To select lines for the yield tests in 2019 growing season, lines with
+low seed yield or extreme maturity dates in 2018 were removed from
+consideration. Two yield trials were then designed for each mapping
+population based on maturity dates and desirable agronomic traits,
+protein and oil contents. Eighty unique lines were selected from each
+population which satisfied these criteria, and each yield test had 40
+RILs. Three high-yielding check cultivars and the two parents of the
+respective population were also included in each test based on the
+maturity spread of the RILs. These yield tests were named test 1 and
+test 2 for RILs derived from mapping population 201 and test 3 and 4 for
+RILs derived from mapping population 202. Yield check cultivars Dunphy,
+Osage, and Roy were used in tests 1 and 2, while Dunphy, Dilday, and
+NC-Raleigh were used for tests 3 and 4. The parents for tests 1 and 2
+were cultivars LMN09-119 and N09-09, and the parents for tests 3 and 4
+were LMN09-19 and N13-47.
 
@@
 
-These four tests were grown in two locations in 2019: the Tidewater
+These four tests were grown in two locations in 2019 - the Tidewater
 Research Station in Plymouth, NC (PLY) and the Caswell Research Farm in
-Kinston, NC (CAS). The same data was collected for each test in this
-season that was collected in the previous season.
+Kinston, NC (CAS). The same data as earlier were collected for each test
+in this season.
 
-Using the data collected from the 2019 season season, further selections
-were done to identify high-yielding lines from the four tests. This was
-done by identifying the RILs with a yield within or above a least
-significant difference (LSD) of the average yield of the checks for each
-test. Further selection was done using the seed composition traits by
-identifying the thirty RILs with the highest protein + oil content on a
-dry basis from among the RILs which had passed the yield selection
-threshold.
+Based the data collected from the 2019 season season, further selections
+were done to identify fewer lines from the four tests for further yield
+testing. This was done by identifying the RILs with a yield at or above
+the average yield of the checks in each test. Further selection was done
+using the seed composition traits by identifying the thirty RILs with
+the highest protein + oil content among the RILs which had passed the
+yield selection threshold.
 
 These thirty lines were then grouped into two new tests of 15 RILs each
-based on maturity date. These two new tests are named Test 1 and Test 2.
-Yield check cultivars were again assigned to each test to match the
+based on maturity date. These two new tests were named Test 1 and Test
+2. Yield check cultivars were again assigned to each test to match the
 maturity dates of the RILs that were in each test. Cultivars Dunphy,
@@
 were grown in a randomized complete block design with four replications
-in each location. The same phenotypes were evaluated for each genotype
-in the 2020 and 2021 seasons using the same methodology that was
-employed in the 2019 season.
+in each location. The same phenotypes were evaluated for each line each
+season using the same methodology that was employed in the 2019 season.
 
@@
 
-A strong negative correlation was observed in both tests between seed
-protein and seed oil content. A coefficient of r = -0.93 was observed in
-both populations. A negative correlation was observed between seed
-protein and yield with correlation coefficient of r = -0.29 was observed
-in both tests. This correlation was not statistically significant in
-either population. A weak positive correlation was observed between seed
-oil and seed yield in both populations. A correlation coefficient of r =
-0.24 was observed in Test 1 while a coefficient of r = 0.28 was observed
-in Test 2. These correlation coefficients were not statistically
-significant in either population. Visualizations of the pairwise
-correlation coefficients for Tests 1 and 2 can be seen in supplementary
-figures 2 and 3, respectively.
+A strong negative correlation (r = -0.93) was observed in both tests
+between seed protein and seed oil content. A weak negative correlation
+(r = -0.29) was observed between seed protein and yield in both tests
+which was statistically insignificant in either population. Weak
+positive correlations were also observed between seed oil and seed yield
+in both populations. A correlation coefficient of r = 0.24 was observed
+in Test 1 while a coefficient of r = 0.28 was observed in Test 2. These
+correlation coefficients were not statistically significant in either
+population. The pairwise correlation coefficients for Tests 1 and 2 are
+presented in supplementary figures 2 and 3, respectively.
 
@@
 \centering
-\includegraphics[width=15 cm]{C:/Users/Jay/Desktop/Documents/R/Jay_yield/exports/plots/lsmean_scatterplot.pdf}
+\includegraphics[width=15 cm]{C:/Users/jhgille2/Documents/R/projects/Jay_yield/exports/plots/lsmean_scatterplot.pdf}
 \caption{Genotype Least square means for seed oil, seed protein, and seed yield for soybean RILs in Test 1 (\textbf{A}) and Test 2 (\textbf{B}).
@@
 average of the check cultivars for each test. No genotypes had yield
-that was quantitatively higher than that of the yield checks, however
-many had comparable yield. Many of these genotypes with comparable yield
-also had protein content that was superior to the check average in each
-test. No genotypes had oil that was superior to the check cultivars, but
-some had comparable yield and oil content as well as superior protein
-content.
+that was higher than that of the yield checks, however many had
+comparable yield. Many of these genotypes with comparable yield also had
+protein content that was superior to the check average in each test. No
+genotypes had oil that was superior to the check cultivars, but some had
+comparable yield and oil content as well as superior protein content.
+Such genotypes are extremely valuable for production of soybean meal
+with higher protein. As mentioned earlier, the meal protein of current
+U.S. cultivars is mostly below the minimum market standard of 47.5\%.
+The meal protein is calculated by a formula that takes both seed protein
+and oil contents into account (reference from Pantalone). The meal
+protein contents of these lines with high protein and normal oil
+contents ranged from xx -- xx\% compared to the meal protein contents of
+the checks (Supplementary table XX).
 
-RILs were also evaluated for lodging and seed quality. All RILs had seed
-quality that was on par with that of the high-yielding checks however,
-however 11 genotypes had lodging scores that were statistically
-significantly greater than the checks on the basis of contrasts. These
-RILs were removed from consideration for recommendation on the basis of
-their relatively poor agronomic performance.
+RILs were also evaluated for lodging and seed quality (data not shown?).
+All RILs had seed quality that was on par with that of the high-yielding
+checks however, however 11 genotypes had lodging scores that were
+statistically significantly greater than the checks on the basis of
+contrasts. These RILs were removed from consideration for recommendation
+on the basis of their relatively poor agronomic performance
 
@@
 compromising seed yield or agronomics. This can be of use both to
-breeders that are looking to improve seed composition traits in soybean
+breeders who are looking to improve seed composition traits in soybean
 and for growers who are seeking options for novel soybean varieties with
-seed composition that is superior to that of cultivars that are already
-used in production.
+seed composition that is superior to that of elite cultivars.
 
@@
 production or used in breeding programs that seek to improve valuable
-soybean seed composition traits.
+soybean seed composition traits with significantly reducing the yield.
 

### 2022-06-30 R/merge_yield_data.R

@@ -111,8 +111,12 @@ merge_yield_data <- function(yield_2019_file, cas_maturity_file,
            yield = ifelse(year %in% c("2020"), yield*0.033, 
                           ifelse(year == "2019", yield/67.2510693716674, 
                             ifelse(loc %in% c("PLY", "SAN"), yield*0.0252, yield*0.0228))), 
-           ENV = paste(loc, year, sep = " - ")) %>% 
-    distinct()
+           ENV = paste(loc, year, sep = " - "), 
+           protein_13_pct = protein*0.87, 
+           oil_13_pct = oil*0.87, 
+           protein_meal = snfR::calc_protein_meal(oil_13_pct, protein_13_pct)) %>% 
+    distinct() %>% 
+    select(-any_of(c("protein_13_pct", "oil_13_pct")))
   
   # Standardize genotype names so that each genotype is identified with
   # only name. See the function definition in the utils.R script.

### 2022-06-30 packages.R

@@ -12,7 +12,12 @@ pacman::p_load(conflicted,
                tarchetypes)
 
 # Data wrangling
-pacman::p_load(tidyverse, 
+pacman::p_load(dplyr,
+               purrr, 
+               stringr,
+               tidyr,
+               forcats,
+               readr,
                here, 
                readxl, 
                janitor, 

### 2022-07-01 doc/manuscript/manuscript.Rmd
Added functions to make and export summplmental data tables. Replaced the function that exported the contrast supplemental table with this new one that exports all the supplemental tables and moved the code to make the contrast supplemental table to the new function that makes the other tables.
Also changed the plot export function a bit to explicitly export the correlation plots as supplemental figure and added protein meal to the correlation figures.

SOme other small changes to the manuscript document to add a formula for protein meal and fix some references that weren't properly rendering.

@@
 cultivars is mostly below the minimum market standard of 47.5%.
-The meal protein is calculated by a formula that takes both seed protein and oil contents into account (reference from Pantalone).
-The meal protein contents of these lines with high protein and normal oil contents ranged from xx – xx% compared to the meal protein contents of the checks (Supplementary table XX).
+The meal protein is calculated by the following formula that takes both seed protein and oil contents into account:
 
-RILs were also evaluated for lodging and seed quality (data not shown?).
-All RILs had seed quality that was on par with that of the high-yielding checks however, however 11 genotypes had lodging scores that were statistically significantly greater than the checks on the basis of contrasts.
+$$Meal\ protein = \frac{Pro13}{1-\frac{Oil13}{100}}/0.92 $$
+
+Where Pro13 and Oil13 are seed protein and oil contents on a 13% moisture basis, respectively[@pantaloneRegistrationTN115102Soybean2018].
+
+The meal protein contents of these lines with high protein and normal oil contents ranged from 103.8% – 108.5% compared to the meal protein contents of the checks.
+Breeding line N18-1783 from test 2 had the maximum protein meal from among these lines.
+(Supplementary table 2).
+
+RILs were also evaluated for lodging and seed quality (Supplementary table 3).
+All RILs had seed quality that was on par with that of the high-yielding checks however, however 11 genotypes had lodging scores that were statistically significantly greater than the checks on the basis of contrasts (Supplementary table 4).
 These RILs were removed from consideration for recommendation on the basis of their relatively poor agronomic performance

### 2022-07-01 doc/manuscript/manuscript.tex
Added functions to make and export summplmental data tables. Replaced the function that exported the contrast supplemental table with this new one that exports all the supplemental tables and moved the code to make the contrast supplemental table to the new function that makes the other tables.
Also changed the plot export function a bit to explicitly export the correlation plots as supplemental figure and added protein meal to the correlation figures.

SOme other small changes to the manuscript document to add a formula for protein meal and fix some references that weren't properly rendering.

@@
 U.S. cultivars is mostly below the minimum market standard of 47.5\%.
-The meal protein is calculated by a formula that takes both seed protein
-and oil contents into account (reference from Pantalone). The meal
-protein contents of these lines with high protein and normal oil
-contents ranged from xx -- xx\% compared to the meal protein contents of
-the checks (Supplementary table XX).
+The meal protein is calculated by the following formula that takes both
+seed protein and oil contents into account:
 
-RILs were also evaluated for lodging and seed quality (data not shown?).
-All RILs had seed quality that was on par with that of the high-yielding
-checks however, however 11 genotypes had lodging scores that were
-statistically significantly greater than the checks on the basis of
-contrasts. These RILs were removed from consideration for recommendation
-on the basis of their relatively poor agronomic performance
+\[Meal\ protein = \frac{Pro13}{1-\frac{Oil13}{100}}/0.92 \]
+
+Where Pro13 and Oil13 are seed protein and oil contents on a 13\%
+moisture basis,
+respectively\citep{pantaloneRegistrationTN115102Soybean2018}.
+
+The meal protein contents of these lines with high protein and normal
+oil contents ranged from 103.8\% -- 108.5\% compared to the meal protein
+contents of the checks. Breeding line N18-1783 from test 2 had the
+maximum protein meal from among these lines. (Supplementary table 2).
+
+RILs were also evaluated for lodging and seed quality (Supplementary
+table 3). All RILs had seed quality that was on par with that of the
+high-yielding checks however, however 11 genotypes had lodging scores
+that were statistically significantly greater than the checks on the
+basis of contrasts (Supplementary table 4). These RILs were removed from
+consideration for recommendation on the basis of their relatively poor
+agronomic performance
 

### 2022-07-01 R/export_phenotype_plots.R

@@ -110,7 +110,7 @@ export_phenotype_plots <- function(BLUE_plots_two_years, phenotype_scatterplots,
   export_correlation_plots <- function(correlation_data, test_name, file_ext = "pdf"){
     
     # Get a filepath to save the plot to
-    current_filename <- paste0(export_dir, "/supplemental/", test_name, "correlation_plot.", file_ext)
+    current_filename <- paste0(export_dir, "/supplemental/", test_name, file_ext)
     
     current_plot <- pluck(correlation_data, "correlation_plot")
     
@@ -126,7 +126,10 @@ export_phenotype_plots <- function(BLUE_plots_two_years, phenotype_scatterplots,
     return(current_filename)
   }
   
-  all_correlation_plots <- map2_chr(correlation_plots, names(correlation_plots), export_correlation_plots)
+  # all_correlation_plots <- map2_chr(correlation_plots, names(correlation_plots), export_correlation_plots)
+  
+  Corr_plot_test1 <- export_correlation_plots(correlation_plots$`Jay Test 1`, test_name = "supplemental_figure_1.")
+  Corr_plot_test2 <- export_correlation_plots(correlation_plots$`Jay Test 2`, test_name = "supplemental_figure_2.")
   
   # Export all plots
   all_scatter_heatmaps <- map2_chr(scatter_heatmap_all, names(scatter_heatmap_all), export_scatter_heatmaps)
@@ -136,5 +139,6 @@ export_phenotype_plots <- function(BLUE_plots_two_years, phenotype_scatterplots,
            all_scatterplots, 
            all_histograms, 
            both_plots_scatter_filepath, 
-           all_correlation_plots))
+           Corr_plot_test1, 
+           Corr_plot_test2))
 }

### 2022-07-01 R/export_supplementary_tables.R

@@ -1,0 +1,46 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param genotype_contrasts_mixed
+#' @param supplementary_table_data
+#' @param util_tables
+#' @param exportdir
+export_supplementary_tables <- function(supplementary_table_data,
+                                        exportdir = here("exports", "data",
+                                        "supplementary")) {
+
+  
+  # File path for the contrasts table (supplementary table 1)
+  contrasts_path <- paste0(exportdir, "/", "supplementary_table_1.csv")
+  
+  # File path for the table of lsmeans for the genotypes that had high protein
+  # and yield, oil comparable to the checks for their tests
+  # (supplementary table 2)
+  meal_table_path <- paste0(exportdir, "/", "supplementary_table_2.csv")
+  
+  # File path for the lsmeans table (supplementary table 3)
+  lsmeans_path <- paste0(exportdir, "/", "supplementary_table_3.csv")
+  
+  # File path for the table of contrasts for the genotypes with lodging that
+  # as higher than the checks for their tests
+  high_lodging_path <- paste0(exportdir, "/", "supplementary_table_4.csv")
+  
+  # File path 
+  
+  # Combine all file paths into a list that can be returned by the function
+  all_paths <- c(contrasts_path, 
+                 meal_table_path,
+                 lsmeans_path, 
+                 high_lodging_path)
+  
+  # Export each dataframe to a csv file
+  write_csv(supplementary_table_data$contrasts_table, contrasts_path)
+  write_csv(supplementary_table_data$elite_genos_lsmeans, meal_table_path)
+  write_csv(supplementary_table_data$all_lsmeans, lsmeans_path)
+  write_csv(supplementary_table_data$high_lodging, high_lodging_path)
+  
+  # And return th paths to these files
+  return(all_paths)
+}

### 2022-07-01 R/make_elite_summary_tables.R

@@ -159,7 +159,6 @@ make_elite_summary_tables <- function(blue_data = genotype_BLUEs,
   # Agronomic comparison tables
   ag_comparison_tables <- full_comparison_table(blue_data = blue_data$BLUEs, lsd_data, keep_phenos = c("ht", "lod", "sdwt", "sq"))
   
-  # TODO:
   # Need to make a function that takes this data and converts it to a more 
   # reader-friendly format. I think that this will specifically involve writing
   # a function that can make hierarchical headings based on the current column 
@@ -169,7 +168,7 @@ make_elite_summary_tables <- function(blue_data = genotype_BLUEs,
   # genotype BLUE, genotype rank, overall test average, 
   # check average, and MSD.
   #
-  # Im imagining a table layout where each trait included in the table can have
+  # I'm imagining a table layout where each trait included in the table can have
   # a layout something like this: 
   #
   #     |                 Yield                    |
@@ -177,7 +176,7 @@ make_elite_summary_tables <- function(blue_data = genotype_BLUEs,
   #     | BLUE | Rank | Test Avg | Check Avg | MSD |
   #     
   # I can think this can be done in a fairly straightforward way by finding the 
-  # iundexes of the columns that match each phenotype name eg
+  # indexes of the columns that match each phenotype name eg
   # str_detect(colnames(x), "phenotype name") %>% which() and then use other
   # string processing functions to split the variable category (BLUE, rank, etc..)
   # from the phenotype, and then use lookup tables to clean up the names. 
@@ -292,6 +291,9 @@ make_elite_summary_tables <- function(blue_data = genotype_BLUEs,
         sort()
     }
     
+    
+    # TODO: This part needs to be fixed so that the footnote symbols can be 
+    # added to the column headings
     # names(current_table)[1] <- paste0(names(current_table)[1],
     #                                   footnote_marker_symbol(1, format = "latex"))
     # 
@@ -308,7 +310,7 @@ make_elite_summary_tables <- function(blue_data = genotype_BLUEs,
     #                                   footnote_marker_symbol(5, format = "latex"))
 
     
-    knitr::kable(current_table, "html", booktabs = TRUE, caption = table_caption) %>% 
+    knitr::kable(current_table, "latex", booktabs = TRUE, caption = table_caption) %>% 
       kable_styling(latex_options=c("scale_down", "HOLD_position")) %>%
       collapse_rows(columns = collapse_indices) %>%
       add_header_above(column_groups, escape = FALSE) %>% 

### 2022-07-01 R/make_supplementary_tables.R

@@ -1,0 +1,51 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param genotype_BLUEs
+make_supplementary_tables <- function(genotype_BLUEs, genotype_contrasts_mixed, util_tables) {
+
+  
+  # Unnest the contrasts
+  contrasts_wide <- genotype_contrasts_mixed %>% 
+    mutate(contrasts = map(contrasts, as_tibble)) %>% 
+    select(test_name, pheno, contrasts) %>% 
+    unnest(contrasts) 
+  
+  # Rename the variables in the pheno column
+  contrasts_wide <- convert_from_table(contrasts_wide, "pheno", util_tables$trait_lookup) %>% 
+    rename(`Test name` = test_name)
+  
+  # Get just the genotypes that had a lodging that was statistically higher than 
+  # the checks for its test
+  high_lodging <- contrasts_wide %>% 
+    dplyr::filter(pheno == "Lodging",
+                  p.value < 0.05, 
+                  estimate > 0)
+  
+  # Make a supplementary table with all the lsmeans 
+  lsmean_table <- genotype_BLUEs %>%
+    pluck("BLUEs") %>% 
+    reduce(bind_rows) %>% 
+    rename_with_lookup(util_tables$trait_lookup) %>% 
+    rename(Genotype = genotype, 
+           `Test name` = test_name) %>% 
+    arrange(`Test name`, Genotype) %>% 
+    mutate_if(is.numeric, round, 2)
+  
+  # Genotypes with similar oil and yield, high protein
+  elite_genos <- c("N18-1635", "N18-1627", "N18-1643", "N18-1783")
+  elite_genos_table <- lsmean_table %>% 
+    dplyr::filter(Genotype %in% elite_genos)
+  
+  # Table with just the protein, oil, and protein meal lsmeans for the 
+  # genotypes that had 
+  
+  res <- list("all_lsmeans"         = lsmean_table, 
+              "contrasts_table"     = contrasts_wide, 
+              "high_lodging"        = high_lodging, 
+              "elite_genos_lsmeans" = elite_genos_table)
+  
+  return(res)
+}

### 2022-07-01 R/merge_yield_data.R

@@ -105,16 +105,16 @@ merge_yield_data <- function(yield_2019_file, cas_maturity_file,
   all_merged <- map(all_yield, function(x) filter_fn(x, keep_cols)) %>% 
     reduce(bind_rows) %>% 
     mutate(across(any_of(num_cols), as.numeric), 
-           protein = ifelse(as.numeric(rep) > 2, NA, protein), 
-           oil     = ifelse(as.numeric(rep) > 2, NA, oil),
+           protein          = ifelse(as.numeric(rep) > 2, NA, protein), 
+           oil              = ifelse(as.numeric(rep) > 2, NA, oil),
            protein_plus_oil = protein + oil, 
-           yield = ifelse(year %in% c("2020"), yield*0.033, 
-                          ifelse(year == "2019", yield/67.2510693716674, 
-                            ifelse(loc %in% c("PLY", "SAN"), yield*0.0252, yield*0.0228))), 
-           ENV = paste(loc, year, sep = " - "), 
-           protein_13_pct = protein*0.87, 
-           oil_13_pct = oil*0.87, 
-           protein_meal = snfR::calc_protein_meal(oil_13_pct, protein_13_pct)) %>% 
+           yield            = ifelse(year %in% c("2020"), yield*0.033,                          # Adjust yield from kg/ha to bu/acre
+                               ifelse(year == "2019", yield/67.2510693716674,                   # Adjust yield from grams to bu/acre
+                                ifelse(loc %in% c("PLY", "SAN"), yield*0.0252, yield*0.0228))), # Adjust from grams to bu/acre
+           ENV              = paste(loc, year, sep = " - "), 
+           protein_13_pct   = protein*0.87, # Adjust protein/oil to a 13% moisture basis so that protein meal can be calculated
+           oil_13_pct       = oil*0.87, 
+           protein_meal     = snfR::calc_protein_meal(oil_13_pct, protein_13_pct)) %>% 
     distinct() %>% 
     select(-any_of(c("protein_13_pct", "oil_13_pct")))
   

### 2022-07-01 _targets.R

@@ -163,11 +163,16 @@ tar_plan(
                                       all_data   = all_yield_data$two_year, 
                                       util_tables)),
   
-  # A supplementary table with all the contrasts data
-  tar_target(contrast_export, 
-             export_contrasts(genotype_contrasts_mixed, 
-                              util_tables, 
-                              exportdir = here("exports", "data", "supplementary")), 
+  # Make supplementary tables 
+  tar_target(supplementary_table_data, 
+             make_supplementary_tables(genotype_BLUEs, 
+                                       genotype_contrasts_mixed, 
+                                       util_tables)),
+  
+  # A Export supplementary tables
+  tar_target(supplementary_tables_export, 
+             export_supplementary_tables(supplementary_table_data,
+                                         exportdir = here("exports", "data", "supplementary")), 
              format = "file"),
   
 # A example latex table to use for testing targets with the manuscript template
@@ -193,7 +198,7 @@ tar_plan(
   # Correlation plots
   tar_target(correlation_plots, 
              make_correlation_plots(genotype_BLUEs, 
-                                    pheno = c("protein", "oil", "yield", "sdwt", "md", "ht"), 
+                                    pheno = c("protein", "oil", "yield", "sdwt", "md", "ht", "protein_meal"), 
                                     util_tables)),
 
   # Latex tables of summary data for the yield marginal means

### 2022-07-12 doc/manuscript_docx_copy.Rmd
Added steps to make a .docx copy of the manuscript document. Also added to the supplementary table export step to export .docx copies of the supplementary data with some added formatting.

--- 2022-07-01 doc/manuscript/manuscript.Rmd
@@
 ---
-title: Identification of high-yielding soybean lines with exceptional seed composition qualities
-author:
-  - name: Jay Gillenwater
-    affil: 1,\ddagger,*
-    orcid: 0000-0002-3477-6291
-affiliation:
-  - num: 1
-    address: |
-      Department of Crop and Soil Sciences, NCSU, Raleigh, NC, USA
-    email: jhgille2@ncsu.edu
-# firstnote to eighthnote
-firstnote: |
-  Current address: Updated affiliation
-secondnote: |
-  These authors contributed equally to this work.
-journal: Agronomy
-type: article
-status: submit
-bibliography: mybibfile.bib
-appendix: appendix.tex
-simplesummary: |
-  A Simple summary goes here.
-abstract: |
- In current markets, the primary uses for soybean seed are in products derived from it’s oil or protein content.
-However, growers are compensated based on seed yield  so a more valuable crop is the one that is high yielding with an optimum combination of protein and oil.
-A negative correlation of seed protein with seed yield and oil makes simultaneous improvement of  these traits difficult but not impossible through conventional breeding.
-A selection of lines with exceptional yield and seed composition qualities was made from two recombinant inbred line (RIL) soybean mapping populations to identify high protein and/or high oil lines with yield comparable to elite cultivars.
-The performance of these RILs were evaluated in multiple environments and several genotypes were identified with yield comparable to that of high yielding check cultivars with seed protein and/or oil superior to the checks.
-These genotypes will provide breeders with additional sources of germplasm for continuing efforts to improve seed composition traits without compromising seed yield, and provide growers with more profitable varieties.
-keywords: |
-  yield; protein; oil;soybean; protein meal
-acknowledgement: |
-  All sources of funding of the study should be disclosed. Please clearly 
-  indicate grants that you have received in support of your research work. 
-  Clearly state if you received funds for covering the costs to publish in open 
-  access.
-authorcontributions: |
-  For research articles with several authors, a short paragraph specifying their 
-  individual contributions must be provided. The following statements should be 
-  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
-  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
-  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
-  limited to those who have contributed substantially to the work reported.
-conflictsofinterest: |
-  The authors declare no conflict of 
-  interest.
-sampleavailability: |
-  Samples of the compounds ...... are available from the authors.
-abbreviations:
-  - short: RIL
-    long: Recombinant inbred line
-  - short: RCBD
-    long: Randomized complete block design
-  - short: CLA
-    long: Central crops research station
-  - short: CAS
-    long: Caswell research farm
-  - short: PLY  
-    long: Tidewater research station
-output: rticles::mdpi_article
+title: "Identification of high-yielding soybean lines with exceptional seed composition qualities"
+author: "Jay Gillenwater"
+date: "`r format(Sys.time(), '%d %B, %Y')`"
+output: word_document
+bibliography: ./manuscript/mybibfile.bib  
 ---
@@
 ```
+
+# Abstract
+
+ In current markets, the primary uses for soybean seed are in products derived from it’s oil or protein content.
+However, growers are compensated based on seed yield  so a more valuable crop is the one that is high yielding with an optimum combination of protein and oil.
+A negative correlation of seed protein with seed yield and oil makes simultaneous improvement of  these traits difficult but not impossible through conventional breeding.
+A selection of lines with exceptional yield and seed composition qualities was made from two recombinant inbred line (RIL) soybean mapping populations to identify high protein and/or high oil lines with yield comparable to elite cultivars.
+The performance of these RILs were evaluated in multiple environments and several genotypes were identified with yield comparable to that of high yielding check cultivars with seed protein and/or oil superior to the checks.
+These genotypes will provide breeders with additional sources of germplasm for continuing efforts to improve seed composition traits without compromising seed yield, and provide growers with more profitable varieties.
 
@@
 ## Phenotypic correlations
+
 A strong negative correlation (r = -0.93) was observed in both tests between seed protein and seed oil content.
@@
 These correlation coefficients were not statistically significant in either population.
-The pairwise correlation coefficients for Tests 1 and 2 are presented in supplementary figures 2 and 3, respectively.
+The pairwise correlation coefficients for Tests 1 and 2 are presented in supplementary figures 1 and 2, respectively.
 
@@
 # Get the link to the lsmean scatterplot
-mean_plot_link <- phenotype_summary_plots[grepl("lsmean_scatterplot", phenotype_summary_plots)]
+mean_plot_link <- phenotype_summary_plots[grepl("lsmean_scatterplot.png", phenotype_summary_plots)]
 
@@
 
-```{=tex}
-\begin{figure}[H]
-\centering
-\includegraphics[width=15 cm]{`r mean_plot_link`}
-\caption{Genotype Least square means for seed oil, seed protein, and seed yield for soybean RILs in Test 1 (\textbf{A}) and Test 2 (\textbf{B}).
+![**Figure 1**: Genotype Least square means for seed oil, seed protein, and seed yield for soybean RILs in Test 1 (**A**) and Test 2 (**B**).
 Points indicate the least square means and error bars indicate the standard errors in the estimation of least square means.
 Blue dots indicate that a RIL has a least square mean above the average of the checks in the test and a color of red indicates that the RIL has a mean value below the check average.
-The check average is shown with the vertical dashed line.}
-\end{figure}
-```
+The check average is shown with the vertical dashed line.](`r mean_plot_link`)
 
@@
 ## Yield contrasts
+
 Several RILs in each of the tests had yield that was comparable to that of their check cultivars as per contrasts between RIL means and the average of the check cultivars for each test.
@@
 
-The meal protein contents of these lines with high protein and normal oil contents ranged from 103.8% – 108.5% compared to the meal protein contents of the checks.
+The meal protein contents of these lines with high protein and normal oil contents ranged from 103.8% -- 108.5% compared to the meal protein contents of the checks.
 Breeding line N18-1783 from test 2 had the maximum protein meal from among these lines.
@@
 ## Genotypes with comparable seed yield and seed oil and superior seed protein content
+
 Four genotypes had yield and oil that was similar to that of the yield checks, and seed protein that was greater than the average of the checks.
@@
 
-```{r elite_geno_table, results = "asis", echo = FALSE}
+```{r elite_geno_table, echo = FALSE}
 
-print(elite_genotype_tables$elite_genos)
+knitr::knit_print(elite_genotype_tables$elite_genos$word_table)
 
@@
 ## Genotypes with comparable yield and superior protein
+
 Seventeen RILs had a similar yield and superior protein content to the check cultivars.
@@
 
-```{r high_po_table, results = "asis", echo = FALSE}
+```{r high_po_table, echo = FALSE}
 
-print(elite_genotype_tables$hp_sy_table)
+knitr::knit_print(elite_genotype_tables$hp_sy_table$word_table)
 

### 2022-07-12 R/export_elite_genotype_tables.R

@@ -1,0 +1,44 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param elite_genotype_tables
+#' @param dir
+export_elite_genotype_tables <- function(elite_genotype_tables, dir =
+                                         here("exports", "tables",
+                                         "elite_genos")) {
+
+  # Make a vector of filepath names
+  all_filepaths <- paste0(dir, "/", names(elite_genotype_tables), ".docx")
+  
+  export_fn <- function(table_list, file_path){
+    
+    # Section properties as provided by the officer package. 
+    # Basically, I want the tables to be landscape
+    sect_properties <- prop_section(
+      page_size = page_size(orient = "landscape",
+                            width = 8.3, height = 11.7),
+      type = "continuous",
+      page_margins = page_mar()
+    )
+    
+    FitFlextableToPage <- function(ft, pgwidth = 11){
+      
+      ft_out <- ft %>% autofit()
+      
+      ft_out <- width(ft_out, width = dim(ft_out)$widths*pgwidth /(flextable_dim(ft_out)$widths))
+      return(ft_out)
+    }
+    
+    table_list %>% 
+      pluck("word_table") %>% 
+      FitFlextableToPage() %>%
+      fontsize(part = "all", size = 8) %>%
+      save_as_docx(path = file_path, pr_section = sect_properties)
+  }
+  
+  walk2(elite_genotype_tables, all_filepaths, export_fn)
+  
+  return(all_filepaths)
+}

### 2022-07-12 R/export_phenotype_plots.R

@@ -38,7 +38,8 @@ export_phenotype_plots <- function(BLUE_plots_two_years, phenotype_scatterplots,
   # All filepaths to the saved scatterplots
   all_scatterplots <- export_scatterplots(phenotype_scatterplots$side_by_side)
   
-  both_plots_scatter_filepath <- paste0(export_dir, "/", "lsmean_scatterplot.pdf")
+  both_plots_scatter_filepath     <- paste0(export_dir, "/", "lsmean_scatterplot.pdf")
+  both_plots_scatter_filepath_png <- paste0(export_dir, "/", "lsmean_scatterplot.png")
   
   ggsave(filename = both_plots_scatter_filepath, 
          plot = phenotype_scatterplots$combined, 
@@ -47,6 +48,14 @@ export_phenotype_plots <- function(BLUE_plots_two_years, phenotype_scatterplots,
          height = 10, 
          units = "in", 
          dpi = 800)
+  
+  ggsave(filename = both_plots_scatter_filepath_png, 
+         plot = phenotype_scatterplots$combined, 
+         device = "png", 
+         width = 12, 
+         height = 10, 
+         units = "in", 
+         dpi = 1800)
   
   
   ## Section: Labelled histograms
@@ -116,11 +125,11 @@ export_phenotype_plots <- function(BLUE_plots_two_years, phenotype_scatterplots,
     
     # Save the plot to the filepath
     ggsave(filename = current_filename, 
-           plot = current_plot, 
-           device = file_ext, 
-           width = 8, 
-           height = 8, 
-           units = "in")
+           plot     = current_plot, 
+           device   = file_ext, 
+           width    = 8, 
+           height   = 8, 
+           units    = "in")
     
     # And return the path
     return(current_filename)
@@ -138,7 +147,8 @@ export_phenotype_plots <- function(BLUE_plots_two_years, phenotype_scatterplots,
   return(c(all_scatter_heatmaps, 
            all_scatterplots, 
            all_histograms, 
-           both_plots_scatter_filepath, 
+           both_plots_scatter_filepath,
+           both_plots_scatter_filepath_png,
            Corr_plot_test1, 
            Corr_plot_test2))
 }

### 2022-07-12 R/export_supplementary_tables.R

@@ -8,38 +8,99 @@
 #' @param util_tables
 #' @param exportdir
 export_supplementary_tables <- function(supplementary_table_data,
+                                        elite_genotype_tables,
                                         exportdir = here("exports", "data",
                                         "supplementary")) {
 
   
   # File path for the contrasts table (supplementary table 1)
-  contrasts_path <- paste0(exportdir, "/", "supplementary_table_1.csv")
+  contrasts_path      <- paste0(exportdir, "/", "supplementary_data_1.csv")
+  contrasts_path_docx <- paste0(exportdir, "/", "supplementary_table_1.docx")
   
   # File path for the table of lsmeans for the genotypes that had high protein
   # and yield, oil comparable to the checks for their tests
   # (supplementary table 2)
-  meal_table_path <- paste0(exportdir, "/", "supplementary_table_2.csv")
+  meal_table_path      <- paste0(exportdir, "/", "supplementary_data_2.csv")
+  meal_table_path_docx <- paste0(exportdir, "/", "supplementary_table_2.docx")
   
   # File path for the lsmeans table (supplementary table 3)
-  lsmeans_path <- paste0(exportdir, "/", "supplementary_table_3.csv")
+  lsmeans_path      <- paste0(exportdir, "/", "supplementary_data_3.csv")
+  lsmeans_path_docx <- paste0(exportdir, "/", "supplementary_table_3.docx")
   
   # File path for the table of contrasts for the genotypes with lodging that
   # as higher than the checks for their tests
-  high_lodging_path <- paste0(exportdir, "/", "supplementary_table_4.csv")
+  high_lodging_path      <- paste0(exportdir, "/", "supplementary_data_4.csv")
+  high_lodging_path_docx <- paste0(exportdir, "/", "supplementary_table_4.docx")
   
-  # File path 
+  # File paths
   
   # Combine all file paths into a list that can be returned by the function
   all_paths <- c(contrasts_path, 
+                 contrasts_path_docx,
                  meal_table_path,
+                 meal_table_path_docx,
                  lsmeans_path, 
-                 high_lodging_path)
+                 lsmeans_path_docx,
+                 high_lodging_path, 
+                 high_lodging_path_docx)
+  
+  # Section properties as provided by the officer package. 
+  # Basically, I want the tables to be landscape
+  sect_properties <- prop_section(
+    page_size = page_size(orient = "landscape",
+                          width = 8.3, height = 11.7),
+    type = "continuous",
[…]

### 2022-07-12 R/make_elite_summary_tables.R

@@ -159,6 +159,9 @@ make_elite_summary_tables <- function(blue_data = genotype_BLUEs,
   # Agronomic comparison tables
   ag_comparison_tables <- full_comparison_table(blue_data = blue_data$BLUEs, lsd_data, keep_phenos = c("ht", "lod", "sdwt", "sq"))
   
+  # Lodging comparison tales
+  lodging_comparison_tables <- full_comparison_table(blue_data = blue_data$BLUEs, lsd_data, keep_phenos = c("lod"))
+  
   # Need to make a function that takes this data and converts it to a more 
   # reader-friendly format. I think that this will specifically involve writing
   # a function that can make hierarchical headings based on the current column 
@@ -308,18 +311,63 @@ make_elite_summary_tables <- function(blue_data = genotype_BLUEs,
     # 
     # names(current_table)[5] <- paste0(names(current_table)[5],
     #                                   footnote_marker_symbol(5, format = "latex"))
-
     
-    knitr::kable(current_table, "latex", booktabs = TRUE, caption = table_caption) %>% 
-      kable_styling(latex_options=c("scale_down", "HOLD_position")) %>%
-      collapse_rows(columns = collapse_indices) %>%
-      add_header_above(column_groups, escape = FALSE) %>% 
-      footnote(symbol = c("The genotype name.", 
+    table_footnotes <-  c("The genotype name.", 
+                          "The test name",
                           "The genotype marginal mean for the phenotype (value divided by check average).", 
                           "The ranking of this genotype for the phenotype within its test.", 
                           "The average phenotype value for all genotypes in the test.",
-                          "The average value of the checks in the test."))
+                          "The average value of the checks in the test.")
+
     
+    # Export two copies of the table, one that uses the kable package to make a latex table, and another that
+    # uses the flextable package to make tables that can be exported to word. 
+    kable_table <- knitr::kable(current_table, "latex", booktabs = TRUE, caption = table_caption) %>% 
+      kable_styling(latex_options=c("scale_down", "HOLD_position")) %>%
+      collapse_rows(columns = collapse_indices) %>%
+      add_header_above(column_groups, escape = FALSE) %>% 
+      kableExtra::footnote(symbol = table_footnotes)
+    
+    
+    # Flextable doesn't like it if column names are repeated. I'll first
+    # remove them and then put them back later as a header row. 
[…]

### 2022-07-12 _targets.R

@@ -169,12 +169,6 @@ tar_plan(
                                        genotype_contrasts_mixed, 
                                        util_tables)),
   
-  # A Export supplementary tables
-  tar_target(supplementary_tables_export, 
-             export_supplementary_tables(supplementary_table_data,
-                                         exportdir = here("exports", "data", "supplementary")), 
-             format = "file"),
-  
 # A example latex table to use for testing targets with the manuscript template
   tar_target(example_table, 
              make_example_table()),
@@ -214,9 +208,12 @@ tar_target(elite_genotype_tables,
            make_elite_summary_tables(blue_data      = genotype_BLUEs,
                                      utility_tables = util_tables, 
                                      lsd_data       = least_sig_differences)),
-             
-             
-  
+
+# Export all of these tables as word documents
+tar_target(elite_genotype_table_exports, 
+           export_elite_genotype_tables(elite_genotype_tables, dir = here("exports", "tables", "elite_genos")), 
+           format = "file"),
+            
   # Histograms for each test with a selection of genotypes labelled for each test
   tar_target(labelled_test_histograms, 
              make_test_histograms(geno_means = genotype_BLUEs$BLUEs, 
@@ -234,6 +231,13 @@ tar_target(elite_genotype_tables,
                                     export_dir = here("exports", "plots")), 
              format = "file"),
 
+# A Export supplementary tables
+tar_target(supplementary_tables_export, 
+           export_supplementary_tables(supplementary_table_data,
+                                       elite_genotype_tables,
+                                       exportdir = here("exports", "data", "supplementary")), 
+           format = "file"),
+
 
 
 
@@ -244,6 +248,7 @@ tar_target(elite_genotype_tables,
 
   # tar_render(overview_document, here("doc", "overview_document.Rmd")),
   
-  tar_render(manuscript_document, here("doc", "manuscript", "manuscript.Rmd"))
-  
+  tar_render(manuscript_document, here("doc", "manuscript", "manuscript.Rmd")), 
+
+  tar_render(manuscript_docx_copy, here("doc", "manuscript_docx_copy.Rmd"))
 )

### 2022-07-12 packages.R

@@ -50,10 +50,13 @@ pacman::p_load(metan,
 pacman::p_load(rmdformats, 
                kableExtra, 
                pander, 
+               flextable,
                kableExtra, 
                rmarkdown, 
-               rticles)
+               rticles, 
+               officer)
 
 # Function conflict preferences
 conflicted::conflict_prefer("filter", "dplyr", "base")
 
+library(rmarkdown)

### 2022-07-12 sandbox/contrast exploring.R

@@ -1,0 +1,34 @@
+##################################################
+## Project: Jay Yield
+## Script purpose: Explore the output of the contrast step to identify
+## genotypes with yield and seed composition traits similar to, or superior
+## to check cultivars
+## Date: 2022-05-02
+## Author: Jay Gillenwater
+##################################################
+
+# Run pipeline and load in the contrasts data
+source("./packages.R")
+tar_make()
+tar_load(c(contrasts_linear, contrasts_mixed))
+
+# The "main" phenotypes I'm interested in
+main_pheno <- c("yield", "oil", "protein")
+
+mixed_tbl <- contrasts_mixed %>% 
+  dplyr::filter(pheno %in% main_pheno) %>% 
+  select(test_name, pheno, contrasts) %>% 
+  unnest(contrasts) %>% 
+  group_by(test_name, pheno) %>% 
+  mutate(contrast = str_remove(contrast, " - Checks")) %>% 
+  dplyr::filter((p.value <= 0.05 & estimate > 0 )| p.value > 0.05) %>%
+  arrange(test_name, pheno, desc(estimate))
+
+linear_tbl <- contrasts_linear %>% 
+  dplyr::filter(pheno %in% main_pheno) %>% 
+  select(test_name, pheno, contrasts) %>% 
+  unnest(contrasts) %>% 
+  group_by(test_name, pheno) %>% 
+  mutate(contrast = str_remove(contrast, " - Checks")) %>% 
+  dplyr::filter((p.value <= 0.05 & estimate > 0 )| p.value > 0.05) %>%
+  arrange(test_name, pheno, desc(estimate))

### 2022-07-12 doc/manuscript/manuscript.tex
Small changed to the manuscript.docx document

@@
 population. The pairwise correlation coefficients for Tests 1 and 2 are
-presented in supplementary figures 2 and 3, respectively.
+presented in supplementary figures 1 and 2, respectively.
 
@@
 \centering
-\includegraphics[width=15 cm]{C:/Users/jhgille2/Documents/R/projects/Jay_yield/exports/plots/lsmean_scatterplot.pdf}
+\includegraphics[width=15 cm]{C:/Users/jhgille2/Documents/R/projects/Jay_yield/exports/plots/lsmean_scatterplot.pdf, C:/Users/jhgille2/Documents/R/projects/Jay_yield/exports/plots/lsmean_scatterplot.png}
 \caption{Genotype Least square means for seed oil, seed protein, and seed yield for soybean RILs in Test 1 (\textbf{A}) and Test 2 (\textbf{B}).
@@
 \multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{*} The genotype name.}\\
-\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\dag} The genotype marginal mean for the phenotype (value divided by check average).}\\
-\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\ddag} The ranking of this genotype for the phenotype within its test.}\\
-\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\S} The average phenotype value for all genotypes in the test.}\\
-\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\P} The average value of the checks in the test.}\\
+\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\dag} The test name}\\
+\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\ddag} The genotype marginal mean for the phenotype (value divided by check average).}\\
+\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\S} The ranking of this genotype for the phenotype within its test.}\\
+\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\P} The average phenotype value for all genotypes in the test.}\\
+\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{**} The average value of the checks in the test.}\\
 \end{tabular}}
@@
 \multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{*} The genotype name.}\\
-\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\dag} The genotype marginal mean for the phenotype (value divided by check average).}\\
-\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\ddag} The ranking of this genotype for the phenotype within its test.}\\
-\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\S} The average phenotype value for all genotypes in the test.}\\
-\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\P} The average value of the checks in the test.}\\
+\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\dag} The test name}\\
+\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\ddag} The genotype marginal mean for the phenotype (value divided by check average).}\\
+\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\S} The ranking of this genotype for the phenotype within its test.}\\
+\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\P} The average phenotype value for all genotypes in the test.}\\
+\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{**} The average value of the checks in the test.}\\
 \end{tabular}}
